### 2021-09-09 manuscript/manuscript.Rmd
set up gitignore file, first go at manuscript (long version)

---
title             : "Uncertain Science is Bad Science: Lay Perceptions of Crowd-Scientific Findings"
shorttitle        : "The Sway and Credibility of Multi-Analyst Studies"

author: 
  - name          : "Shilaan Alzahawi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "655 Knight Way, Stanford, CA 94305"
    email         : "shilaan@stanford.edu"
  - name          : "Benoît Monin"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Stanford University, Graduate School of Business"

abstract: |
  A recent movement towards crowd science has emerged in the behavioral sciences. Crowd science aims to increase the rigor, reliability, and credibility of scientific research. Does it meet its promises in reality? We report the results of an experiment in which we explore whether scientific findings emerging from a crowd of researchers (vs. a typical research collaboration) are more likely to sway the prior beliefs of research consumers, increase ratings of credibility and confidence, and decrease ratings of bias and error. We focus on crowdsourced data analysis (also known as the 'many analysts' or 'multi-analyst' approach): giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.  
  In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) are less likely to be swayed, have less confidence in the average effect size estimate, find the results less credible, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific research.

keywords          : "Meta-science, Crowd science, Many analysts, Multi-analyst, Research credibility"
wordcount         : "X"

bibliography      : ["r-references.bib", "library.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
# devtools::install_github("crsh/papaja@devel")
library(papaja)
library(tidyverse)
library(rmarkdown)
library(here)
r_refs("r-references.bib")
```

The credibility of scientific research is in doubt, among lay consumer and scientist alike. From man-made climate change to the safety and effectiveness of Covid-19 vaccinations, important scientific findings are rejected at large [@hornsey2017]. In addition to widespread science skepticism among the general public, doubts about the credibility of scientific research have emerged from within the scientific community itself. Reliance on widely followed research practices, some scientists have come to realize, can generate impossible results, such as the ability of humans to feel what’s in the future [@bem2011] or to become younger in age from listening to certain music [@simmons2011: p. 1360].  
What can be done about this "crisis of confidence" [@pashler2012: p. 528]? Several tools have been proposed to improve the rigor and reliability of scientific research and, consequently, combat the crisis of confidence. One such tool is the crowd or big team science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].   
Crowd science aims to improve the rigor, reliability, and credibility of scientific research. Does it meet its promises in reality? In this commentary, we focus on crowdsourced data analysis (also known as the 'many analysts' or 'multi-analyst' approach): giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question. We explore whether multi-analyst studies increase the sway and credibility of scientific research. That is, are scientific findings emerging from a crowd of researchers (vs. a typical science collaboration) more likely to sway the prior beliefs of research consumers, increase ratings of credibility and confidence, and decrease ratings of bias and error?

# Methods
The preregistration of our experiment can be found in the Open Science Foundation (OSF) Registries at https://osf.io/rpu98. All data and code needed to reproduce this article can be found on GitHub at https://github.com/shilaan/many-analysts and the OSF at https://osf.io/vedb4/. We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

## Participants
We sampled participants from the Prolific participant pool. We included participants from the United States or the United Kingdom who were at least 18 years old and spoke English as a first language. Participants were paid $2 for 8-12 minutes of their time.   
Our target sample size was 1500 participants after exclusions due to failing the attention check, not completing the attention check, or attempting to take the survey more than once. We aimed to sample until reaching the desired number of valid participants or until 2 weeks passed (whichever came first). We expected relatively small effect sizes and decided on an upper limit on the number of participants based on monetary constraints.

## Procedure and materials
The Survey Materials can be found on the OSF at https://osf.io/md9z5/. After a brief introduction to a research question ("Do religious people report higher well-being?"), participants were first asked to report their prior beliefs ("How likely do you think it is that people who are more religious generally report higher well-being?") on a slider from 0% (not likely at all) to 100% (extremely likely).  
After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a single-analyst study (the "single-analyst" condition); a multi-analyst study with consistent results (the "multi-analyst: consistent" condition); or a multi-analyst study with inconsistent results (the "multi-analyst: inconsistent" condition).  
Afterwards, participants rated (1) their final beliefs about the research question, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) degrees of freedom. All questions were answered on a slider from 0% (not likely/credible/confident at all) to 100% (extremely likely/credible/confident).

## Data analysis
For all six dependent variables, we ran linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate. All statistical models and code were preregistered at https://osf.io/rpu98. An overview of our preregistered, directional hypotheses can be found in Table 1. We did not preregister any hypotheses for the last measure ("degrees of freedom"). Thus, the findingds concerning the impact of experimental condition on ratings of degrees of freedom are exploratory, and should be treated as such.

```{r, echo = FALSE}
table1 <- data.frame(
  Measure = c("1. Final beliefs",
              "2. Credibility", 
              "3. Confidence",
              "4. Bias",
              "5. Error"),
  Multi_Consistent = c("+", "+", "-", "-", "-"),
  Multi_Inconsistent = c("-", "-", "-", "+", "+"))

knitr::kable(table1,
             col.names = c("Measure", 
                           "Many-analysts: Consistent", 
                           "Many-analysts: Inconsistent"),
             align = "lcc",
             caption = "Table 1")
```

# Results

## Participants

# Discussion

## Acknowledgement
This manuscript was created using `r cite_r("r-references.bib")`.

## Data availability statement
The data that support the findings of this study are openly available on GitHub at https://github.com/shilaan/many-analysts and the OSF at https://osf.io/vedb4/.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-09-09 manuscript/manuscript.Rmd
major edits to manuscript

@@
 a typical research collaboration) are more likely to sway the prior beliefs of research consumers, increase ratings of credibility and confidence, and decrease ratings of bias and error.
-We focus on crowdsourced data analysis (also known as the 'many analysts' or 'multi-analyst' approach): giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.
-  In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) are less likely to be swayed, have less confidence in the average effect size estimate, find the results less credible, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific research.
+We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.
+  In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) are less likely to be swayed, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
+Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific research to lay consumer.
 
-keywords          : "Meta-science, Crowd science, Many analysts, Multi-analyst, Research credibility"
+keywords          : "Meta-science, Crowd science, Many analysts, Multi-analyst, Research credibility, Science skepticism"
 wordcount         : "X"
@@
 library(papaja)
-library(tidyverse)
+library(raincloudplots)
+library(ggplot2)
+library(broom)
+library(purrr)
+library(glue)
+library(readr)
+library(dplyr)
 library(rmarkdown)
@@
 The credibility of scientific research is in doubt, among lay consumer and scientist alike.
-From man-made climate change to the safety and effectiveness of Covid-19 vaccinations, important scientific findings are rejected at large [@hornsey2017].
-In addition to widespread science skepticism among the general public, doubts about the credibility of scientific research have emerged from within the scientific community itself.
-Reliance on widely followed research practices, some scientists have come to realize, can generate impossible results, such as the ability of humans to feel what’s in the future [@bem2011] or to become younger in age from listening to certain music [@simmons2011: p.
-1360].
 What can be done about this "crisis of confidence" [@pashler2012: p.
 528]?
-Several tools have been proposed to improve the rigor and reliability of scientific research and, consequently, combat the crisis of confidence.
-One such tool is the crowd or big team science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
+Several tools have been proposed to improve the reliability of scientific research and combat the crisis of confidence.
+One such tool is the crowd science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
 Crowd science aims to improve the rigor, reliability, and credibility of scientific research.
 Does it meet its promises in reality?
-In this commentary, we focus on crowdsourced data analysis (also known as the 'many analysts' or 'multi-analyst' approach): giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.
-We explore whether multi-analyst studies increase the sway and credibility of scientific research.
+Here, we focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.
+We explore whether multi-analyst studies increase the sway and credibility of scientific research to lay consumers.
 That is, are scientific findings emerging from a crowd of researchers (vs.
@@
 We included participants from the United States or the United Kingdom who were at least 18 years old and spoke English as a first language.
-Participants were paid $2 for 8-12 minutes of their time.
-Our target sample size was 1500 participants after exclusions due to failing the attention check, not completing the attention check, or attempting to take the survey more than once.
-We aimed to sample until reaching the desired number of valid participants or until 2 weeks passed (whichever came first).
+We excluded participants who failed the attention check or attempted to take the survey more than once.
+Our target sample size was 1500 participants after exclusions.
+We aimed to keep sampling until reaching the desired number of valid participants or until 2 weeks passed (whichever came first).
 We expected relatively small effect sizes and decided on an upper limit on the number of participants based on monetary constraints.
@@
 ## Procedure and materials
-The Survey Materials can be found on the OSF at https://osf.io/md9z5/.
-After a brief introduction to a research question ("Do religious people report higher well-being?"), participants were first asked to report their prior beliefs ("How likely do you think it is that people who are more religious generally report higher well-being?") on a slider from 0% (not likely at all) to 100% (extremely likely).
-After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a single-analyst study (the "single-analyst" condition); a multi-analyst study with consistent results (the "multi-analyst: consistent" condition); or a multi-analyst study with inconsistent results (the "multi-analyst: inconsistent" condition).
+All survey materials can be found on the OSF at https://osf.io/md9z5/.
+After a brief introduction to a research question ("Do religious people report higher well-being?"), participants were asked to report their prior beliefs ("How likely do you think it is that people who are more religious generally report higher well-being?") on a slider from 0% (not likely at all) to 100% (extremely likely).
+After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a scientific study.
+In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, and 6%, respectively) that average to 5%; and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5%.
 Afterwards, participants rated (1) their final beliefs about the research question, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) degrees of freedom.
@@
 ## Data analysis
-For all six dependent variables, we ran linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate.
-All statistical models and code were preregistered at https://osf.io/rpu98.
+For all six measures, we run linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate.
+All hypotheses, statistical models, and code were preregistered at https://osf.io/rpu98.
 An overview of our preregistered, directional hypotheses can be found in Table 1.
-We did not preregister any hypotheses for the last measure ("degrees of freedom").
-Thus, the findingds concerning the impact of experimental condition on ratings of degrees of freedom are exploratory, and should be treated as such.
-
-```{r, echo = FALSE}
-table1 <- data.frame(
-  Measure = c("1. Final beliefs",
-              "2. Credibility", 
-              "3. Confidence",
-              "4. Bias",
-              "5. Error"),
-  Multi_Consistent = c("+", "+", "-", "-", "-"),
-  Multi_Inconsistent = c("-", "-", "-", "+", "+"))
-
-knitr::kable(table1,
-             col.names = c("Measure", 
-                           "Many-analysts: Consistent", 
-                           "Many-analysts: Inconsistent"),
-             align = "lcc",
-             caption = "Table 1")
-```
+We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of degrees of freedom are exploratory, and should be treated as such.
+Because we test five separate hypotheses using two comparisons each (one comparison of the single-analyst vs.
+the multi-consistent condition, and one comparison of the single-analyst vs.
+the multi-inconsistent condition), we use the Bonferroni method to correct for multiple comparisons.
+Thus, our preregistered threshold for statistical significance is $\displaystyle \alpha = \frac{.05}{2} = .025$.
 
@@
 
-## Participants
+```{r data-cleaning, include = FALSE}
+df <- read.csv(paste0(here(), "/data/data.csv"))
+df <- df[3:nrow(df),]
+n_recorded <- nrow(df)
+
+df <- df %>% #take out participants who attempted to take the survey more than once
+  filter(!PROLIFIC_PID %in% df$PROLIFIC_PID[duplicated(df$PROLIFIC_PID)])
+n_more_than_once <- n_recorded - nrow(df)
+
+df <- df %>% #take out participants who were screened out or did not consent
+  filter(Consent == "I agree to participate in this research project")
+n_screened_out <- n_recorded - n_more_than_once - nrow(df)
+
+df <- df %>% #take out participants who failed or did not complete the attention check
+  filter(Condition == Attention_check & Attention_check != "") 
+n_failed_attention <- n_recorded - n_more_than_once - n_screened_out - nrow(df)
+
+df <- df %>% 
+  mutate(
+    ID = 1:nrow(df),
+    Condition = factor(Condition, #set reference category
+                       levels = c("Single",           
+                                  "Multi-consistent", 
+                                  "Multi-inconsistent"))
+  ) %>% 
+  rename(
+    Prior_beliefs = Prior.beliefs_1,
+    Final_beliefs = Final.beliefs_1,
+    Credibility = Credibility_1,
+    Confidence = Confidence_1,
+    Bias = Sources.Variability_1,
+    Error = Sources.Variability_4,
+    Discretion = Sources.Variability_5
+  ) %>% 
+  select(ID, Condition, Attention_check, Prior_beliefs:Discretion)
+
+df[,4:ncol(df)] <- sapply(df[,4:ncol(df)], as.numeric) #recode variables to numeric
+```
+
+We recorded `r n_recorded` responses in Qualtrics.
+We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check.
+This left us with a total sample of `r nrow(df)` participants (500 per condition).
+```{r, include = FALSE}
+results <- function(Predictor, Multi_Condition = "Consistent") {
+  linear_mod <- lm(
+    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
+
+  apa_results <- apa_print(linear_mod)
+
+  ifelse(Multi_Condition == "Consistent",
+         paste(apa_results$estimate$ConditionMulti_consistent,
+               apa_results$statistic$ConditionMulti_consistent,
+               sep = ", "),
+         paste(apa_results$estimate$ConditionMulti_inconsistent,
+               apa_results$statistic$ConditionMulti_inconsistent,
+               sep = ", ")
+         )
+}
+```
+Our main findings are displayed in Figure 1.
+Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported final beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`.
+For our exploratory measure of discretion, we found that ratings of degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
+In sum, all preregistered hypotheses (see Table 1) related to the multi-consistent condition were not corroborated; all preregistered hypotheses related to the multi-inconsistent condition were corroborated.
+In line with our hypotheses, multi-analyst studies with inconsistent results decrease the sway and credibility of scientific research to lay consumers.
+Contrary to our hypotheses, multi-analyst studies with consistent result do not increase the sway and credibility of scientific research to lay consumers.
+Figure 2 further clarifies the sway of multi-analyst vs.
+single-analyst studies, by displaying the distribution of prior and final beliefs across the three conditions.
 
@@
 
-## Acknowledgement
-This manuscript was created using `r cite_r("r-references.bib")`.
+From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the rigor and reliability of scientific research.
+However, as with any real-world intervention, scientific reform can have unintended consequences.
+Here, we focused on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
+While instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent uncertainty that comes with inconsistent estimates.
+As a result, they are less likely to believe in the reported phenomenon, rate the scientific finding as less credible, have less confidence in the reported effect size estimate, and are more likely to think that the findings stem from bias and error.
+
+## Acknowledgements
+This manuscript was created using `r cite_r("r-references.bib")`. We thank Nicole Clare Kolmstetter for valuable assistance in the data collection.
 
@@
 \endgroup
+
+\newpage
+
+# Tables and Figures
+
+## Table 1
+```{r, echo = FALSE}
+table1 <- data.frame(
+  Measure = c("1. Final beliefs",
+              "2. Credibility", 
+              "3. Confidence",
+              "4. Bias",
+              "5. Error"),
+  Multi_Consistent = c("+", "+", "-", "-", "-"),
+  Multi_Inconsistent = c("-", "-", "-", "+", "+"))
+
+knitr::kable(table1,
+             col.names = c("Measure", 
+                           "Many-analyst: Consistent", 
+                           "Many-analyst: Inconsistent"),
+             align = "lcc",
+             label = NA,
+             caption = "Predicted direction of effects for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs")
+```
+*Note*.
+Table 1 indicates the predicted direction of the effect for each of the five dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+## Figure 1
+*Ratings of Bias, Confidence, Credibility, Discretion, Error, and Final Beliefs*
+\noindent
+```{r fig-1, echo=FALSE}
+tidy_df <- function(Predictor) {
+  linear_mod <- lm(
+    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
+
+  tidy_lm <- tidy(linear_mod, conf.int = TRUE) %>% 
+    mutate(Measure = glue("{Predictor}")) %>% 
+    filter(term != "Prior_beliefs" & term != "(Intercept)")
+  tidy_lm
+}
+
+Predictors <- list("Final_beliefs", 
+                  "Credibility", 
+                  "Confidence", 
+                  "Bias", 
+                  "Error", 
+                  "Discretion")
+
+tidy_results <- Predictors %>% 
+  map(~ tidy_df(.x)) %>% 
+  bind_rows() %>% 
+  mutate(term = gsub("Condition", "", term))
+
+Measure.label = c("Final beliefs", Predictors %>% unlist() %>% tail(5))
+names(Measure.label) <- Predictors %>% unlist()
+
+p1 <- ggplot(mapping = aes(x = term, y = estimate), 
+             data = tidy_results) +
+  geom_point(size = 2) +
+  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), 
+                size = 0.8, width = 0.2) +
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray34", alpha = 0.7) +
+  facet_wrap(~ Measure, 
+             labeller = labeller(Measure = Measure.label)) + 
+  theme_bw() + 
+  theme(strip.background = element_rect(fill = "white"),
+        legend.position = "") +
+  labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
+   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))
+
+ggsave("Figure1.jpg", p1, 
+       width = 7, height = 5, units = "in")
+
+knitr::include_graphics("Figure1.jpg", dpi = 1200)
+```
+*Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of bias, confidence, credibility, discretion, error, and final beliefs in the two multi-analyst conditions, compared to the single-analyst condition (and controlling for prior beliefs).
+
+\newpage
+
+## Figure 2
+
+*Individual data points, quartiles, and distributions of prior and final beliefs in the single-analyst, multi-consistent, and multi-inconsistent conditions*  
+\noindent
+```{r raincloud, echo=FALSE}
+df_2x3 <- data_2x2(
+  array_1 = df %>% filter(Condition == "Multi-inconsistent") %>% pull(Prior_beliefs),
+  array_2 = df %>% filter(Condition == "Multi-inconsistent") %>% pull(Final_beliefs),
+  array_3 = df %>% filter(Condition == "Multi-consistent") %>% pull(Prior_beliefs),
+  array_4 = df %>% filter(Condition == "Multi-consistent") %>% pull(Final_beliefs),
+  array_5 = df %>% filter(Condition == "Single") %>% pull(Prior_beliefs),
+  array_6 = df %>% filter(Condition == "Single") %>% pull(Final_beliefs),
+  labels = (c('Prior Beliefs','Final Beliefs')),
+  jit_distance = .09,
+  jit_seed = 321)
+
+colors <- rep(c("dodgerblue", "darkorange"), 3) #choose colors
+
+p2 <- raincloud_2x3_repmes(
+  data = df_2x3,
+  colors = colors,
+  fills = colors,
+  size = 1,
+  alpha = .6,
+  ort = "h") + #set to v for vertical plot
+
+  scale_x_continuous(
+    breaks = c(1,2,3), 
+    limits = c(0.8, 4.3), 
+    labels = rep("", 3)) +
+  ylab("Rated Beliefs") +
+
+  annotate(geom = "text", 
+           label = "Single-Analyst", 
+           x = 3.9, y = 13, hjust = 1) + 
+  annotate(geom = "text", 
+           label = "Multi-Analyst: Consistent", 
+           x = 2.7, y = 11) + 
+  annotate(geom = "text", 
+           label = "Multi-Analyst: Inconsistent",
+           x = 1.75, y = 12) + 
+  annotate(geom = "text", 
+           label = "Prior Beliefs", 
+           x = 4.2, y = 37, size = 5, 
+           color = "dodgerblue") + 
+  annotate(geom = "text", 
+           label = "vs.", 
+           x = 4.2, y = 50, size = 5) + 
+  annotate(geom = "text", 
+           label = "Final Beliefs", 
+           x = 4.2, y = 63, size = 5, 
+           color = "darkorange") +
+
+  theme_classic() +
+  theme(axis.ticks.y = element_blank(),
+        axis.text = element_text(size = 9),
+        axis.title.y = element_blank())
+
+ggsave("Figure2.jpg", p2, 
+       width = 7, height = 5, units = "in")
+
+knitr::include_graphics("Figure2.jpg", dpi = 1200)
+```
+*Note.
+* Prior beliefs are displayed in blue; final beliefs are displayed in orange.
+The respective boxes display the lower quartiles, medians, and upper quartiles of prior and final beliefs by condition.

### 2021-09-21 manuscript/manuscript.Rmd
incorporated feedback Benoît

@@
 ---
-title             : "Uncertain Science is Bad Science: Lay Perceptions of Crowd-Scientific Findings"
-shorttitle        : "The Sway and Credibility of Multi-Analyst Studies"
+title             : "Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus"
+shorttitle        : "Lay Perceptions of Multi-Analyst Studies"
 
@@
   A recent movement towards crowd science has emerged in the behavioral sciences.
-Crowd science aims to increase the rigor, reliability, and credibility of scientific research.
-Does it meet its promises in reality?
-We report the results of an experiment in which we explore whether scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) are more likely to sway the prior beliefs of research consumers, increase ratings of credibility and confidence, and decrease ratings of bias and error.
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.
-  In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) are less likely to be swayed, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific research to lay consumer.
+One of the aims of crowd science is to increase the credibility of scientific research.
+Does it meet this promise in reality?
+We run an experiment to study the effects of scientific findings emerging from a crowd of researchers (vs.
+a typical research collaboration) on lay consumers's posterior beliefs and ratings of credibility, confidence in an aggregate effect size estimate, bias, and error.
+We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to answer a research question and/or estimate a parameter of interest.
+We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) to (a) providing multiple -- slightly varying -- parameter estimates in the same direction, leading to the same qualitative conclusion (the "multi-consistent" condition) and (b) providing multiple -- widely varying -- parameter estimates in different directions, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
+Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific findings to lay consumers: instead, to our surprise, they lead to lower posterior beliefs and higher ratings of error.
 
-keywords          : "Meta-science, Crowd science, Many analysts, Multi-analyst, Research credibility, Science skepticism"
-wordcount         : "X"
+keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
+wordcount         : "1,634"
 
@@
 
-The credibility of scientific research is in doubt, among lay consumer and scientist alike.
-What can be done about this "crisis of confidence" [@pashler2012: p.
-528]?
-Several tools have been proposed to improve the reliability of scientific research and combat the crisis of confidence.
+The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
+Several tools have been proposed to combat this "crisis of confidence" (Ibid.: p.
+528).
 One such tool is the crowd science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
-Crowd science aims to improve the rigor, reliability, and credibility of scientific research.
-Does it meet its promises in reality?
-Here, we focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question.
-We explore whether multi-analyst studies increase the sway and credibility of scientific research to lay consumers.
-That is, are scientific findings emerging from a crowd of researchers (vs.
-a typical science collaboration) more likely to sway the prior beliefs of research consumers, increase ratings of credibility and confidence, and decrease ratings of bias and error?
+Does crowd science meet its promise -- to improve the credibility of scientific research -- in reality?
+We explore the effects of scientific findings emerging from a crowd of researchers (vs.
+a typical research collaboration) on lay consumers's posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
+We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
+We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) to (a) providing multiple  -- slightly varying -- parameter estimates in the same direction, leading to the same qualitative conclusion (the "multi-consistent" condition) and (b) providing multiple  -- widely varying -- parameter estimates in different directions, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+Normatively, we expect laypeople who observe several individual (teams of) scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings.
+Although lay observers, in such cases, may be less certain that the aggregate parameter estimate is exactly correct (because they  observed several slightly varying estimates), they may be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
+Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
+However, when laypeople observe several individual (teams of) scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
+Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 1: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
+For the multi-inconsistent condition, we hypothesized that lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
+In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both multi-analyst conditions.
 
@@
 After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a scientific study.
-In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, and 6%, respectively) that average to 5%; and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5%.
-Afterwards, participants rated (1) their final beliefs about the research question, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) degrees of freedom.
+In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% (SD = 2); and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% (SD = 8.25).
+Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) experimenter degrees of freedom.
 All questions were answered on a slider from 0% (not likely/credible/confident at all) to 100% (extremely likely/credible/confident).
@@
 An overview of our preregistered, directional hypotheses can be found in Table 1.
-We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of degrees of freedom are exploratory, and should be treated as such.
+We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of experimenter degrees of freedom are exploratory, and should be treated as such.
 Because we test five separate hypotheses using two comparisons each (one comparison of the single-analyst vs.
@@
 n_failed_attention <- n_recorded - n_more_than_once - n_screened_out - nrow(df)
+ns_bycondition <- table(df$Condition)
 
@@
 df[,4:ncol(df)] <- sapply(df[,4:ncol(df)], as.numeric) #recode variables to numeric
-```
 
-We recorded `r n_recorded` responses in Qualtrics.
-We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check.
-This left us with a total sample of `r nrow(df)` participants (500 per condition).
-```{r, include = FALSE}
+# Function to show inline results
 results <- function(Predictor, Multi_Condition = "Consistent") {
@@
 }
+
+# Post-hoc t-test
+df_multiconsistent <- df %>% 
+  filter(Condition == "Multi-consistent")
+
+t_test <- t.test(df_multiconsistent$Final_beliefs, df_multiconsistent$Prior_beliefs, paired = TRUE)
+t_apa <- apa_print(t_test)
 ```
+
+After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics.
+We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check.
+This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).
 Our main findings are displayed in Figure 1.
-Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported final beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`.
-For our exploratory measure of discretion, we found that ratings of degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
-In sum, all preregistered hypotheses (see Table 1) related to the multi-consistent condition were not corroborated; all preregistered hypotheses related to the multi-inconsistent condition were corroborated.
-In line with our hypotheses, multi-analyst studies with inconsistent results decrease the sway and credibility of scientific research to lay consumers.
-Contrary to our hypotheses, multi-analyst studies with consistent result do not increase the sway and credibility of scientific research to lay consumers.
+Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`.
+For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
+In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
+Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
 Figure 2 further clarifies the sway of multi-analyst vs.
-single-analyst studies, by displaying the distribution of prior and final beliefs across the three conditions.
+single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.
+It is worth noting on the basis of Figure 2 and a post-hoc one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs within the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
 
@@
 
-From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the rigor and reliability of scientific research.
+From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
+The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
 However, as with any real-world intervention, scientific reform can have unintended consequences.
-Here, we focused on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent uncertainty that comes with inconsistent estimates.
-As a result, they are less likely to believe in the reported phenomenon, rate the scientific finding as less credible, have less confidence in the reported effect size estimate, and are more likely to think that the findings stem from bias and error.
+Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
+While instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
+To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.
 
 ## Acknowledgements
-This manuscript was created using `r cite_r("r-references.bib")`. We thank Nicole Clare Kolmstetter for valuable assistance in the data collection.
+We thank Nicole Clare Kolmstetter for valuable assistance in the data collection. This manuscript was created using `r cite_r("r-references.bib")`.
 
@@
               "4. Bias",
-              "5. Error"),
-  Multi_Consistent = c("+", "+", "-", "-", "-"),
-  Multi_Inconsistent = c("-", "-", "-", "+", "+"))
+              "5. Error",
+              "6. Discretion"),
+  Multi_Consistent = c("+", "+", "-", "-", "-", "No prediction"),
+  Multi_Inconsistent = c("-", "-", "-", "+", "+", "No prediction"))
 
@@
 ## Figure 1
-*Ratings of Bias, Confidence, Credibility, Discretion, Error, and Final Beliefs*
+*Ratings of Bias, Confidence, Credibility, Discretion, Error, and Posterior Beliefs*
 \noindent
@@
   bind_rows() %>% 
-  mutate(term = gsub("Condition", "", term))
+  mutate(term = gsub("Condition", "", term),
+         Measure = factor(Measure,
+                          levels = c("Final_beliefs",
+                                     "Credibility",
+                                     "Confidence",
+                                     "Bias",
+                                     "Error",
+                                     "Discretion")))
 
-Measure.label = c("Final beliefs", Predictors %>% unlist() %>% tail(5))
+Measure.label = c("Posterior beliefs", Predictors %>% unlist() %>% tail(5))
 names(Measure.label) <- Predictors %>% unlist()
@@
 ```
-*Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of bias, confidence, credibility, discretion, error, and final beliefs in the two multi-analyst conditions, compared to the single-analyst condition (and controlling for prior beliefs).
+*Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of posterior beliefs, credibility, confidence, bias, error, and discretion in the two multi-analyst conditions, compared to the single-analyst condition (and controlling for prior beliefs).
 
@@
 
-*Individual data points, quartiles, and distributions of prior and final beliefs in the single-analyst, multi-consistent, and multi-inconsistent conditions*  
+*Individual data points, quartiles, and distributions of prior and posterior beliefs in the single-analyst, multi-consistent, and multi-inconsistent conditions*  
 \noindent
 ```{r raincloud, echo=FALSE}
+df <- df %>% 
+  group_by(Condition) %>% 
+  slice_sample(n = 499)
+
 df_2x3 <- data_2x2(
@@
   annotate(geom = "text", 
-           label = "Final Beliefs", 
-           x = 4.2, y = 63, size = 5, 
+           label = "Posterior Beliefs", 
+           x = 4.2, y = 66, size = 5, 
            color = "darkorange") +
@@
 *Note.
-* Prior beliefs are displayed in blue; final beliefs are displayed in orange.
-The respective boxes display the lower quartiles, medians, and upper quartiles of prior and final beliefs by condition.
+* Prior beliefs are displayed in blue; posterior beliefs are displayed in orange.
+The respective boxes display the lower quartiles, medians, and upper quartiles of prior and posterior beliefs by condition.

### 2021-09-21 manuscript/manuscript.Rmd
minor edits

@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "1,634"
+wordcount         : "1,702"
 
@@
 single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.
-It is worth noting on the basis of Figure 2 and a post-hoc one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs within the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
+It is worth noting on the basis of Figure 2 and a post-hoc, one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
 

### 2021-09-21 manuscript/manuscript.Rmd
typo + README

@@
 We run an experiment to study the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers's posterior beliefs and ratings of credibility, confidence in an aggregate effect size estimate, bias, and error.
+a typical research collaboration) on lay consumers' posterior beliefs and ratings of credibility, confidence in an aggregate effect size estimate, bias, and error.
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to answer a research question and/or estimate a parameter of interest.
@@
 We explore the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers's posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
+a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.

### 2021-09-21 manuscript/manuscript.Rmd
clarified multi-consistent findings

@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "1,702"
+wordcount         : "1,744"
 
@@
 It is worth noting on the basis of Figure 2 and a post-hoc, one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
+This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.
 

### 2021-09-24 manuscript/manuscript.Rmd
incorporated round two of feedback

@@
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to answer a research question and/or estimate a parameter of interest.
-We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) to (a) providing multiple -- slightly varying -- parameter estimates in the same direction, leading to the same qualitative conclusion (the "multi-consistent" condition) and (b) providing multiple -- widely varying -- parameter estimates in different directions, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+We compare the effects of providing (a) a single, aggregate parameter estimate (the single-analyst condition) vs.
+multiple parameter estimates that (b) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (c) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
 In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "1,744"
+wordcount         : "1,890"
 
-bibliography      : ["r-references.bib", "library.bib"]
+bibliography      : ["r-references.bib", "references.bib"]
 
@@
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
-We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) to (a) providing multiple  -- slightly varying -- parameter estimates in the same direction, leading to the same qualitative conclusion (the "multi-consistent" condition) and (b) providing multiple  -- widely varying -- parameter estimates in different directions, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
-Normatively, we expect laypeople who observe several individual (teams of) scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings.
-Although lay observers, in such cases, may be less certain that the aggregate parameter estimate is exactly correct (because they  observed several slightly varying estimates), they may be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
+We compare the effects of providing (a) a single, aggregate parameter estimate (the single-analyst condition) vs.
+multiple parameter estimates that (b) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (c) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings, as it seems to reflect consensus between various approaches.
+After all, it's a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence [@jick1979; @turner2017], and to provide a "sensitivity analysis" or "robustness checks" to examine whether and how the findings change as a result of alternative analytic specifications [@munoz2018; @steegen2016].
+As argued in Aczel et al.
+[-@aczel2020: p.
+562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher's idiosyncratic choice (…) when reasonable alternatives exist." The same argument has been made for triangulation, which, according to Jick [-@jick1979: p.
+608], "allows researchers to be more confident of their results." We would similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
+Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
 Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
-However, when laypeople observe several individual (teams of) scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
+However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
 Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 1: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
@@
 We excluded participants who failed the attention check or attempted to take the survey more than once.
-Our target sample size was 1500 participants after exclusions.
+Our target sample size was 1,500 participants after exclusions.
 We aimed to keep sampling until reaching the desired number of valid participants or until 2 weeks passed (whichever came first).

### 2021-09-27 manuscript/manuscript.Rmd
minor edit

@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "1,890"
+wordcount         : "1,891"
 
@@
 single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.
-It is worth noting on the basis of Figure 2 and a post-hoc, one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
+It is worth noting on the basis of Figure 2 and a post-hoc, one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa$full_result`.
 This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.

### 2021-10-05 manuscript/manuscript.Rmd
added table with proposed benefits, disclosure statement

--- 2021-09-24 manuscript/manuscript.Rmd
@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "1,890"
+wordcount         : "3,627"
 
@@
 The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
-Several tools have been proposed to combat this "crisis of confidence" (Ibid.: p.
+Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
 528).
@@
 multiple parameter estimates that (b) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (c) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+According to previous work, crowdsourced data analysis should increase the credibility of scientific findings; Table 1 provides an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
 Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings, as it seems to reflect consensus between various approaches.
@@
 As argued in Aczel et al.
-[-@aczel2020: p.
-562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher's idiosyncratic choice (…) when reasonable alternatives exist." The same argument has been made for triangulation, which, according to Jick [-@jick1979: p.
+[-@aczel2020, p.
+562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher's idiosyncratic choice (…) when reasonable alternatives exist." The same argument has been made for triangulation, which, according to Jick [-@jick1979, p.
 608], "allows researchers to be more confident of their results." We would similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
@@
 However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
-Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 1: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
+**[Insert Table 1 here]**  
+Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 2: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
 For the multi-inconsistent condition, we hypothesized that lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
 In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both multi-analyst conditions.
+**[Insert Table 2 here]**
+
+<!-- "Following the logic of the wisdom of the crowds, in which aggregating estimates reduces individual level biases (Galton, 1907; Lorge, Fox, Davitz, & Brenner, 1958; Surowiecki, 2004), the central tendency of the effect size estimates calculated by many different analysts may provide a less subjective and error-prone estimate of the effect."  (Schweinsberg et al., 2021: p.
+246-7) -->
 
@@
 All hypotheses, statistical models, and code were preregistered at https://osf.io/rpu98.
-An overview of our preregistered, directional hypotheses can be found in Table 1.
+An overview of our preregistered, directional hypotheses can be found in Table 2.
 We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of experimenter degrees of freedom are exploratory, and should be treated as such.
@@
 For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
+**[Insert Figure 1 here]**  
 In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
@@
 single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.
-It is worth noting on the basis of Figure 2 and a post-hoc, one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
+**[Insert Figure 2 here]**  
+It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa$full_result`.
 This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.
@@
 Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
+While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
 To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.
@@
 We thank Nicole Clare Kolmstetter for valuable assistance in the data collection. This manuscript was created using `r cite_r("r-references.bib")`.
+
+## Disclosure statement
+There are no relevant financial or non-financial competing interests to report.
 
@@
 
-# Tables and Figures
+# Tables
 
 ## Table 1
+## *Proposed credibility- and confidence-related benefits of crowdsourced data analysis*
+
+| Citation | Description of credibility- or confidence-related benefits | 
+| ------------- | ------------- | 
+| [@aczel2021, pp.
+3-4] | "When the results of independent data analyses converge, more confidence in the conclusions is warranted.
+When the results diverge, confidence appropriately falters, and scientists can examine the reasons for these discrepancies."|
+|[@arbon2019] | "For the public to have faith in the conclusions of scientists it is important that the methods they employ are robust and transparent.
+This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis." |
+| [@auspurg2021, pp. 1, 10]  | "Several researchers analyze the same research question with the same data (...) Science is credible if different researchers come up with a similar answer"  | 
+| [@breznau2021, p.
+3] | "Organized scientific knowledge production (...) should generate inter-researcher reliability, offering consumers of scientific findings assurance that they are not arbitrary flukes but that other researchers would generate similar findings given the same data." |
+| [@breznau2021a, p.
+311] | "crowdsourcing provides a new way to increase credibility for political and social research---in both sample populations and among the researchers themselves (...) It is hoped that these developments are tangible outcomes that increase public, private, and government views of social science." |
+|[@silberzahn2015, pp. 190-1]|"the results are more credible (...) greater certainty comes from having an independent check."|
+|[@silberzahn2018, p.
+352]|"Scientists can have comparatively more faith in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
+(...) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have no faith that the hypothesis is true"|
+|[@uhlmann2019, p.
+713]|"crowdsourced teams can conduct high-powered, precise studies and draw confident conclusions.
+(...) Crowdsourcing research is a part of a changing landscape of science that seeks to improve research reliability and advance the credibility of academic research"|
+
+\newpage
+
+## Table 2
 ```{r, echo = FALSE}
-table1 <- data.frame(
+table2 <- data.frame(
   Measure = c("1. Final beliefs",
@@
 
-knitr::kable(table1,
+knitr::kable(table2,
              col.names = c("Measure", 
@@
 *Note*.
-Table 1 indicates the predicted direction of the effect for each of the five dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+Table 2 indicates the predicted direction of the effect for each of the five dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
 For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+\newpage
+
+# Figures
 
@@
 ```{r raincloud, echo=FALSE}
+set.seed(341990)
+
 df <- df %>% 
@@
 The respective boxes display the lower quartiles, medians, and upper quartiles of prior and posterior beliefs by condition.
+
+<!-- Given the existing huge inefficiencies, substantial improvements are almost certainly feasible...but neither presence nor absence of revolutionary intent should be taken as a reliable surrogate for actual impact…  -->
+
+<!-- Interventions to change the current system should not be accepted without proper scrutiny, even when they are reasonable and well-intended.” -->
+
+<!-- John Ioannidis -->

### 2021-10-06 talk/index.Rmd
first rough draft talk (incomplete)

---
title: "Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus"
# subtitle: ""  
author: 
  - "Shilaan Alzahawi & Benoît Monin"
date: "October 11, 2021"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanthemer)
library(xaringanExtra)
library(icons)

style_duo(primary_color = "#ffffff", 
          secondary_color = "#035AA6")
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r echo=FALSE}
xaringanExtra::style_panelset_tabs(
  active_foreground = "#035AA6",
  hover_foreground = "#d22"
 )
```

```{r xaringanExtra, echo = FALSE}
xaringanExtra::use_progress_bar(color = "#035AA6", location = "top")
```

```{r, echo = FALSE}
set.seed(1808)

estimates <- data.frame(
  Estimate = sample(
    x = seq(-0.3, 0.3, .001), 
    size = 100
    ),
  se = sample(
    x = seq(0.006, 0.05, .001),
    replace = TRUE,
    size = 100
  )) %>% 
  arrange(Estimate) %>% 
  mutate(Team = 1:100,
         Conclusion = case_when(
           Estimate - 1.96 * se < 0 & Estimate + 1.96 * se < 0 ~ "Negative Evidence",
           Estimate - 1.96 * se < 0 & Estimate + 1.96 * se > 0 ~ "Inconclusive Evidence",
           Estimate - 1.96 * se > 0 & Estimate + 1.96 * se > 0 ~ "Positive Evidence"
         )) %>% 
  mutate(Conclusion = factor(Conclusion,
                             levels = c("Negative Evidence",
                                        "Inconclusive Evidence",
                                        "Positive Evidence")))

title_plot <- ggplot(data = estimates, 
                     mapping = aes(x = Team, y = Estimate, color = Conclusion)) +
  geom_point(size = 2) +
  geom_errorbar(mapping = aes(ymin = Estimate - 1.96 * se, 
                              ymax = Estimate + 1.96 * se),
                width = 3) + 
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  labs(y = "Standardized Effect Size") +
  scale_color_discrete(type = c("red", "orange", "green4")) +
  theme(legend.position = c(0.3, 0.8),
        text = element_text(size = 19))

ggsave("title_plot.jpg", title_plot, 
       width = 7, height = 5, units = "in")
```

# Lay Perceptions of Crowd-Scientific Findings

**The Risks of Variability and Lack of Consensus**  
[Shilaan Alzahawi](http://shilaan.rbind.io) & [Benoît Monin](https://www.gsb.stanford.edu/faculty-research/faculty/benoit-monin)

.pull-left[
![](title_plot.jpg)
]

.pull-right[
[`r icon_style(icons::fontawesome("twitter"), scale = 2, fill = "#035AA6")` $~~$ twitter.com/shilaan01](https://twitter.com/shilaan01)    
[`r icon_style(icons::fontawesome("globe"), scale = 2, fill = "#035AA6")` $~~$ shilaan.rbind.io](https://shilaan.rbind.io)     
[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan](https://github.com/shilaan)  
[`r icon_style(icons::fontawesome("paper-plane"), scale = 2, fill = "#035AA6")` $~~$ shilaan@stanford.edu](mailto:shilaan@stanford.edu)

]
---
# Outline

---
# Open Science Statement

[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~$ Preregistration](https://osf.io/rpu98)

[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~$ Open materials](https://osf.io/6vze3)

[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~$ Open data](https://osf.io/b527v/)

[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)

[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~$ osf.io/vedb4](https://osf.io/vedb4)

[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)

---
# Crowdsourced Data Analysis

---
# Methods

---
.panelset.sideways[
.panel[.panel-name[Introduction]
```{r, echo = FALSE, out.width='90%'}
knitr::include_graphics("images/introduction.png")
```
]

.panel[.panel-name[Prior Beliefs]

![](images/prior_beliefs.png)
]

.panel[.panel-name[Thanks!]

![](images/thanks.png)
]
]

???

Participants had to wait 30 seconds before proceeding to the next slide. 
---
.panelset.sideways[
.panel[.panel-name[Study design & research approach (Single-analyst)]
```{r, echo = FALSE, out.width='93%'}
knitr::include_graphics("images/design_single.png")
```
]

.panel[.panel-name[Study design & research approach (Multi-analyst)]
```{r, echo = FALSE, out.width='91%'}
knitr::include_graphics("images/design_multi.png")
```
]
]

---

.panelset[
.panel[.panel-name[Results (Single-analyst)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("images/results_single.png")
```
]

.panel[.panel-name[Results (Multi-consistent)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("images/results_multi-consistent.png")
```
]

.panel[.panel-name[Results (Multi-inconsistent)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("images/results_multi-inconsistent.png")
```
]
]

---

.panelset.sideways[
.panel[.panel-name[Posterior beliefs]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/posterior_beliefs.png")
```
]

.panel[.panel-name[Credibility]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/credibility.png")
```
]

.panel[.panel-name[Confidence]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/confidence.png")
```
]

.panel[.panel-name[Bias]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/bias.png")
```
]
.panel[.panel-name[Error]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/bias.png")
```
]
.panel[.panel-name[Discretion]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/bias.png")
```
]

.panel[.panel-name[Attention check]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/attention.png")
```
]

]
---
exclude: true

```{r}
knitr::kable(head(mtcars), format = 'html')
```

---
exclude: true

```{r eval=requireNamespace("DT", quietly=TRUE)}
DT::datatable(head(mtcars), fillContainer = FALSE, options = list(pageLength = 4))
```

---
exclude: true

## Square image

<center><img src="https://octodex.github.com/images/labtocat.png" height="400px" /></center>

.footnote[GitHub Octocat]

### 2021-10-07 manuscript/manuscript.Rmd
edited manuscript intro to crowd science, edited talk (title plot, outline, intro to crowd science)

@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "3,627"
+wordcount         : "3,710"
 
@@
 One such tool is the crowd science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
-Does crowd science meet its promise -- to improve the credibility of scientific research -- in reality?
+Crowd science is defined as "the organization of scientific research in open collaborative projects"  [@franzoni2014, p.
+1].
+Crowd-scientific projects vary in their degree of selectivity: some are open to the general public (such projects are often referred to as "citizen science"), while others require the expertise of specialists [e.g., scientists\; @uhlmann2019, p.
+714].
+Here, we focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
 We explore the effects of scientific findings emerging from a crowd of researchers (vs.
 a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
 We compare the effects of providing (a) a single, aggregate parameter estimate (the single-analyst condition) vs.
@@
 According to previous work, crowdsourced data analysis should increase the credibility of scientific findings; Table 1 provides an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
+Does crowd science meet its promise -- to improve the credibility of scientific research -- in reality?
 Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings, as it seems to reflect consensus between various approaches.

### 2021-10-07 talk/index.Rmd
edited manuscript intro to crowd science, edited talk (title plot, outline, intro to crowd science)

@@
   Estimate = sample(
-    x = seq(-0.3, 0.3, .001), 
+    x = c(seq(-0.3, 0.3, .001), seq(-0.1, 0.1, .0001)), 
     size = 100
@@
   se = sample(
-    x = seq(0.006, 0.05, .001),
+    x = seq(0.003, 0.04, .001),
     replace = TRUE,
@@
   geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
-  labs(y = "Standardized Effect Size") +
+  labs(x = "Science Team", 
+       y = "Obtained Effect Size",
+       color = "Conclusion of Science Team") +
   scale_color_discrete(type = c("red", "orange", "green4")) +
-  theme(legend.position = c(0.3, 0.8),
+  theme(legend.position = c(0.35, 0.8),
         text = element_text(size = 19))
@@
 .pull-right[
+$~~$
+
 [`r icon_style(icons::fontawesome("twitter"), scale = 2, fill = "#035AA6")` $~~$ twitter.com/shilaan01](https://twitter.com/shilaan01)    
@@
 # Outline
+
+`r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ **Crowdsourcing Science** 
+`r icon_style(icons::fontawesome("chart-bar"), scale = 2, fill = "#035AA6")` $~~~$ **Crowdsourced Data Analysis**  
+`r icon_style(icons::fontawesome("question-circle"), scale = 2, fill = "#035AA6")` $~~~$ **Lay Perceptions: Are Crowd-Scientific Findings More Credible?**   
+`r icon_style(icons::fontawesome("tools"), scale = 2, fill = "#035AA6")` $~~~$ **Method**
+`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~$ **Results**
+`r icon_style(icons::fontawesome("comment"), scale = 2, fill = "#035AA6")` $~~~$ **Discussion**
+
+---
+.center[
+# Crowd Science
+]
+
+### The organization of scientific research in open and collaborative projects
+
+Highly **inclusive** (sourcing citizens) or highly **selective** (sourcing specialists)
+
+Used at different **stages** of the research process
+
+.pull-left[
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("coins"), scale = 1, fill = "#035AA6")` $~~~$ **Funding**
+`r icon_style(icons::fontawesome("lightbulb"), scale = 1, fill = "#035AA6")`  $~~~~$ **Ideation**
+`r icon_style(icons::fontawesome("project-diagram"), scale = 1, fill = "#035AA6")`  $~~$  **Study design**
+`r icon_style(icons::fontawesome("folder-open"), scale = 1, fill = "#035AA6")`  $~~$  **Data collection**
+
+]
+
+.pull-right[
+
+`r icon_style(icons::fontawesome("laptop-code"), scale = 1, fill = "#035AA6")`  $~~$   **Data analysis**
+`r icon_style(icons::fontawesome("feather-alt"), scale = 1, fill = "#035AA6")`  $~~~$    **Writing**
+`r icon_style(icons::fontawesome("file-pdf"), scale = 1, fill = "#035AA6")`  $~~~$    **Peer review**
+`r icon_style(icons::fontawesome("check-double"), scale = 1, fill = "#035AA6")`  $~~$   **Replication**
+
+]
+
+]
+
+.pull-right[
+
+]
+
+---
+background-image: url("images/meteor.jpeg")
+background-position: 90% 73%
+background-size: 42%
+
+.center[
+# Crowd Science
+]
+
+### The organization of scientific research in open and collaborative projects
+
+Highly **inclusive** (sourcing citizens) or highly **selective** (sourcing specialists)
+
+Used at different **stages** of the research process
+
+.pull-left[
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("coins"), scale = 1, fill = "#035AA6")` $~~~$ **Funding**
+`r icon_style(icons::fontawesome("lightbulb"), scale = 1, fill = "#035AA6")`  $~~~~$ **Ideation**
+`r icon_style(icons::fontawesome("project-diagram"), scale = 1, fill = "#035AA6")`  $~~$  **Study design**
+`r icon_style(icons::fontawesome("folder-open"), scale = 1, fill = "#035AA6")`  $~~$  **Data collection**
+
+]
+
+.pull-right[
+
+`r icon_style(icons::fontawesome("laptop-code"), scale = 1, fill = "#035AA6")`  $~~$   **Data analysis**
+`r icon_style(icons::fontawesome("feather-alt"), scale = 1, fill = "#035AA6")`  $~~~$    **Writing**
+`r icon_style(icons::fontawesome("file-pdf"), scale = 1, fill = "#035AA6")`  $~~~$    **Peer review**
+`r icon_style(icons::fontawesome("check-double"), scale = 1, fill = "#035AA6")`  $~~$   **Replication**
+
+]
+
+]
+
+.pull-right[
+
+]
+
+.right[
+
+$~~$  
+$~~$  
+The great meteor storm of 1833: birth of *Citizen Science*
+
+]
+---
+.center[
+# Crowdsourced data analysis
+
+]
+
+### Different teams of scientists independently analyze the same dataset
+
+Also known as the **many-analysts** or **multi-analyst** approach
 
@@
 [`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)
-
----
-# Crowdsourced Data Analysis
 

### 2021-10-07 manuscript/manuscript.Rmd
manuscript: fixed typo, talk: started table many-analysts studies

@@
 One such tool is the crowd science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
-Crowd science is defined as "the organization of scientific research in open collaborative projects"  [@franzoni2014, p.
+Crowd science is defined as "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p.
 1].
@@
 562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher's idiosyncratic choice (…) when reasonable alternatives exist." The same argument has been made for triangulation, which, according to Jick [-@jick1979, p.
-608], "allows researchers to be more confident of their results." We would similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
+608], "allows researchers to be more confident of their results."
+We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
 Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.

### 2021-10-07 talk/index.Rmd
manuscript: fixed typo, talk: started table many-analysts studies

@@
 `r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ **Crowdsourcing Science** 
-`r icon_style(icons::fontawesome("chart-bar"), scale = 2, fill = "#035AA6")` $~~~$ **Crowdsourced Data Analysis**  
+`r icon_style(icons::fontawesome("chart-bar"), scale = 2, fill = "#035AA6")` $~~~$ **Crowdsourcing Data Analysis**  
 `r icon_style(icons::fontawesome("question-circle"), scale = 2, fill = "#035AA6")` $~~~$ **Lay Perceptions: Are Crowd-Scientific Findings More Credible?**   
@@
 
-Highly **inclusive** (sourcing citizens) or highly **selective** (sourcing specialists)
+From highly **inclusive** (sourcing citizens) to highly **selective** (sourcing specialists)
 
@@
 ]
+
+???
+
+In 1833, Denison Olmsted used letter correspondence to recruit citizen scientists to help document a meteor shower.
+This led to a detailed documentation of the great meteor shower and the birth of the citizen-science movement (highly inclusive, used for data collection.
 ---
@@
 
-Also known as the **many-analysts** or **multi-analyst** approach
+`r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ Also known as the **many-analysts** or **multi-analyst** approach
+`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~~$ On the **rise** in behavioral science
+
+--
+
+```{r, echo = FALSE}
+t1 <- data.frame(
+  Authors = c(
+    "Botvinik-Nezer et al.",
+    "Schweinsberg et al.",
+    "Silberzahn et al."
+  ),
+  Year = c(
+    2020,
+    2018,
+    2018
+  ),
+  Title = c(
+    "Variability in the analysis of a single neuroimaging dataset by many teams",
+    "Same data, different conclusions: Radical dispersion in empirical results when independent analysts operationalize and test the same hypothesis",
+    "Many Analysts, One Data Set: Making Transparent How Variations in Analytic Choices Affect Results"
+  )
+)
+DT::datatable(t1, fillContainer = FALSE, options = list(pageLength = 2))
+```
 
@@
 ]
----
-exclude: true
-
-```{r}
-knitr::kable(head(mtcars), format = 'html')
-```
-
----
-exclude: true
-
-```{r eval=requireNamespace("DT", quietly=TRUE)}
-DT::datatable(head(mtcars), fillContainer = FALSE, options = list(pageLength = 4))
-```
-
----
-exclude: true
-
-## Square image
-
-<center><img src="https://octodex.github.com/images/labtocat.png" height="400px" /></center>
-
-.footnote[GitHub Octocat]

### 2021-10-07 talk/index.Rmd
further edits studies table

@@
 `r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ Also known as the **many-analysts** or **multi-analyst** approach
-`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~~$ On the **rise** in behavioral science
+`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~~$ On the **rise** in the social and behavioral sciences
 
@@
   Authors = c(
+    "Bastiaansen et al.",
     "Botvinik-Nezer et al.",
+    "Breznau et al.",
+    "Breznau et al.",
+    "Huntington-Klein et al.",
     "Schweinsberg et al.",
@@
   Year = c(
+    2019,
+    2020,
+    2021,
+    2021,
     2020,
@@
   Title = c(
+    "Time to get personal? The impact of researchers choices on the selection of
+treatment targets using the experience sampling methodology",
+
     "Variability in the analysis of a single neuroimaging dataset by many teams",
+
+    "How many replicators does it take to achieve reliability? Investigating researcher variability in a crowdsourced replication",
+
+    "Observing many researchers using the same data and hypothesis
+reveals a hidden universe of uncertainty",
+
+    "The influence of hidden researcher decisions in applied microeconomics",
+
     "Same data, different conclusions: Radical dispersion in empirical results when independent analysts operationalize and test the same hypothesis",
-    "Many Analysts, One Data Set: Making Transparent How Variations in Analytic Choices Affect Results"
+
+    "Many analysts, one data set: Making transparent how variations in analytic choices affect results"
   ) 
-)
+) %>% 
+  arrange(desc(Year))
+
 DT::datatable(t1, fillContainer = FALSE, options = list(pageLength = 2))
@@
 ---
+
 # Open Science Statement

### 2021-10-07 talk/index.Rmd
restructured talk w hyperlinks to slides, added credibility table, started methods section

@@
 
-`r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ **Crowdsourcing Science** 
-`r icon_style(icons::fontawesome("chart-bar"), scale = 2, fill = "#035AA6")` $~~~$ **Crowdsourcing Data Analysis**  
-`r icon_style(icons::fontawesome("question-circle"), scale = 2, fill = "#035AA6")` $~~~$ **Lay Perceptions: Are Crowd-Scientific Findings More Credible?**   
-`r icon_style(icons::fontawesome("tools"), scale = 2, fill = "#035AA6")` $~~~$ **Method**
-`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~$ **Results**
-`r icon_style(icons::fontawesome("comment"), scale = 2, fill = "#035AA6")` $~~~$ **Discussion**
+--
+`r icon_style(icons::fontawesome("lock-open"), scale = 2, fill = "#035AA6")` $~~$ [**Open Science Statement**](#openscience)   
+--
+
+`r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~$ [**Crowdsourcing Science**](#crowdscience)  
+--
+
+`r icon_style(icons::fontawesome("chart-bar"), scale = 2, fill = "#035AA6")` $~~~$ [**Crowdsourcing Data Analysis**](#crowddata)  
+--
+
+`r icon_style(icons::fontawesome("question-circle"), scale = 2, fill = "#035AA6")` $~~~$ [**Lay Perceptions: Are Crowd-Scientific Findings More Credible?**](#lay)   
+--
+
+`r icon_style(icons::fontawesome("tools"), scale = 2, fill = "#035AA6")` $~~~$ [**Method**](#method)  
+--
+
+`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~$ [**Results**](#results)  
+--
+
+`r icon_style(icons::fontawesome("comment"), scale = 2, fill = "#035AA6")` $~~~$ [**Discussion**](#discussion)
+
+---
+class: inverse, middle, center
+name: openscience
+
+# Open Science Statement
+
+---
+# Open Science Statement
+
+--
+[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~$ Preregistration](https://osf.io/rpu98)
+
+--
+
+[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~$ Open materials](https://osf.io/6vze3)
+
+--
+
+[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~$ Open data](https://osf.io/b527v/)
+
+--
+
+[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)
+
+--
+
+[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~$ osf.io/vedb4](https://osf.io/vedb4)
+
+--
+
+[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)
+
+---
+class: inverse, center, middle
+name: crowdscience
+
+# Crowdsourcing Science
 
@@
 
+--
+
 ### The organization of scientific research in open and collaborative projects
+
+--
 
@@
 
+--
+
 Used at different **stages** of the research process
+
+--
 
@@
 ---
+class: inverse, center, middle
+name: crowddata
+
+# Crowdsourcing Data Analysis
+
+---
 .center[
-# Crowdsourced data analysis
+# Crowdsourced Data Analysis
 
@@
 
+--
+
 ### Different teams of scientists independently analyze the same dataset
 
+--
+
 `r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ Also known as the **many-analysts** or **multi-analyst** approach
+
+--
+
 `r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~~$ On the **rise** in the social and behavioral sciences
@@
 t1 <- data.frame(
-  Authors = c(
+  Author = c(
     "Bastiaansen et al.",
@@
 ---
+class: inverse, center, middle
+name: lay
 
-# Open Science Statement
-
-[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~$ Preregistration](https://osf.io/rpu98)
-
-[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~$ Open materials](https://osf.io/6vze3)
-
-[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~$ Open data](https://osf.io/b527v/)
-
-[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)
-
-[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~$ osf.io/vedb4](https://osf.io/vedb4)
-
-[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)
+# Lay Perceptions
 
 ---
-# Methods
+# Credibility of Crowd-Scientific Findings
+
+According to science reformers, crowd-scientific findings should **increase the credibility of scientific research**
+--
+
+$~~$
+
+```{r, echo = FALSE}
+t2 <- data.frame(
+  Author = c(
+    "Aczel et al.",
+    "Arbon et al.",
+    "Auspurg & Brüderl",
+    "Breznau et al.",
+    "Breznau",
+    "Silberzahn & Uhlmann",
+    "Silberzahn et al.",
+    "Uhlmann et al."
+  ),
+
+  Year = c(
+    2021,
+    2019,
+    2021,
+    2021,
+    2021,
+    2015,
+    2018,
+    2019
+  ),
+  Quote = c(
+    "When the results of independent data analyses converge, more confidence in the conclusions is warranted.
+When the results diverge, confidence appropriately falters, and scientists can examine the reasons for these discrepancies.",
+
+    "For the public to have faith in the conclusions of scientists it is important that the methods they employ are robust and transparent.
+This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis.",
+
+    "Several researchers analyze the same research question with the same data (…) Science is credible if different researchers come up with a similar answer",
+
+    "Organized scientific knowledge production (…) should generate inter-researcher reliability, offering consumers of scientific findings assurance that they are not arbitrary flukes but that other researchers would generate similar findings given the same data.",
+
+    "crowdsourcing provides a new way to increase credibility for political and social research—in both sample populations and among the researchers themselves (…) It is hoped that these developments are tangible outcomes that increase public, private, and government views of social science.",
+
+    "the results are more credible (…) greater certainty comes from having an independent check.",
+
+    "Scientists can have comparatively more faith in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
+(…) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have no faith that the hypothesis is true",
+
+    "crowdsourced teams can conduct high-powered, precise studies and draw confident conclusions.
+(…) Crowdsourcing research is a part of a changing landscape of science that seeks to improve research reliability and advance the credibility of academic research"
+
+  )
+) %>% 
+  arrange(desc(Year))
+
+DT::datatable(t2, fillContainer = FALSE, options = list(pageLength = 2))
+```
 
 ---
+class: inverse, center, middle
+name: method
+
+# Method
+
+---
+
+## Are Crowd-Scientific Findings More Credible `r icon_style(icons::fontawesome("question-circle"), scale = 1, fill = "#035AA6")`
+
+--
+
+We run an experiment with **three conditions**:
+--
+
+`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~~$ **Single-analyst** $~~~~~~~~~~~$ a *single, aggregate parameter estimate*
+
+--
+
+`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~~$ **Multi-consistent** $~~~~~~~$ *multiple parameter estimates* with *low variance* and *high consensus*
+
+--
+
+`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~~$ **Multi-inconsistent** $~~~~$ *multiple parameter estimates* with *high variance* and *low consensus*
+
+--
+
+$~~$  
+and study the **effects on**
+
+.pull-left[
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Posterior beliefs  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceptions of credibility  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Confidence in the aggregate effect size estimate  
+]
+.pull-right[
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of bias  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of error  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of degrees of freedom  
+]
+
+---
+
 .panelset.sideways[
@@
 ]
+
+---
+class: inverse, center, middle
+name: results
+
+# Results
+
+---
+class: inverse, center, middle
+name: discussion
+
+# Discussion

### 2021-10-07 manuscript/manuscript.Rmd
changed hypothesis table in manuscript and talk

@@
 library(here)
+library(icons)
+library(rsvg)
 r_refs("r-references.bib")
@@
 ## Table 2
-```{r, echo = FALSE}
-table2 <- data.frame(
-  Measure = c("1. Final beliefs",
-              "2. Credibility", 
-              "3. Confidence",
-              "4. Bias",
-              "5. Error",
-              "6. Discretion"),
-  Multi_Consistent = c("+", "+", "-", "-", "-", "No prediction"),
-  Multi_Inconsistent = c("-", "-", "-", "+", "+", "No prediction"))
 
-knitr::kable(table2,
-             col.names = c("Measure", 
-                           "Many-analyst: Consistent", 
-                           "Many-analyst: Inconsistent"),
-             align = "lcc",
-             label = NA,
-             caption = "Predicted direction of effects for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs")
-```
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| 1. Posterior beliefs | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+|2. Credibility | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+| 3. Confidence  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | 
+| 4. Bias | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 5. Error | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 6. Discretion | No prediction | No prediction |
 *Note*.
-Table 2 indicates the predicted direction of the effect for each of the five dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+Table 2 indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction).
 For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

### 2021-10-07 talk/index.Rmd
talk: hypotheses
added artwork
changed hypothesis table in manuscript and talk

@@
 ---
+background-image: url("https://github.com/allisonhorst/stats-illustrations/raw/master/rstats-artwork/reproducibility_court.png")
+background-position: 90% 50%
+background-size: 50%
+
 # Open Science Statement
@@
 [`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)
+
+.right[
+Artwork by [@allison_horst](https://github.com/allisonhorst/stats-illustrations)
+]
 
@@
 
-We run an experiment with **three conditions**:
+We run an experiment with **three conditions**
 --
@@
 `r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of error  
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of degrees of freedom  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of discretion  
 ]
+
+---
+.center[
+
+# Hypotheses
+
+]
+
+$~~$
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**
+
+`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+]
+
+.pull-right[
+
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+]
+
+???
+
+*Note*.
+Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+---
+.center[
+
+# Hypotheses
+
+]
+
+$~~$
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**
+
+`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+]
+
+.pull-right[
+
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+]
+
+???
+
+*Note*.
+Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+---
+.center[
+
+# Hypotheses
+
+]
+
+$~~$
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**
+
+`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+]
+
+.pull-right[
+
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
+]
+
+???
+
+*Note*.
+Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+---
+.center[
+
+# Hypotheses
+
+]
+
+$~~$
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**
+
+`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+]
+
+.pull-right[
+
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
+| Bias | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
+]
+
+???
+
+*Note*.
+Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+---
+.center[
+
+# Hypotheses
+
+]
+
+$~~$
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**
+
+`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+]
+
+.pull-right[
+
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
+| Bias | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
+| Error | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
+]
+
+???
+
+*Note*.
+Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+---
+.center[
+
+# Hypotheses
+
+]
+
+$~~$
+
+.pull-left[
+
+`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**
+
+`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+]
+
+.pull-right[
+
+| Measure | Multi-consistent | Multi-inconsistent |
+| ------------- |  ------------- | ------------- | 
+| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
+| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
+| Bias | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
+| Error | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
+| Discretion | .center[No prediction] | .center[No prediction] |
+]
+
+???
+
+*Note*.
+Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+---
+class: inverse, center, middle
+name: lay
+
+# Survey Materials
 

### 2021-10-07 talk/index.Rmd
added prereg to hypotheses

@@
 
+???
+
+Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions – compared to a single research team that comes to a single, joint conclusion – to be more swayed by the findings, as it seems to reflect consensus between various approaches.
+After all, it’s a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence, and to provide a “sensitivity analysis” or “robustness checks” to examine whether and how the findings change as a result of alternative analytic specifications.
+As argued in Aczel et al., “The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher’s idiosyncratic choice (…) when reasonable alternatives exist.” The same argument has been made for triangulation, which, according to Jick, “allows researchers to be more confident of their results.”
+We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
+Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
+Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
+However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
+
 ---
@@
 
+`r icon_style(icons::academicons("preregistered"), scale = 1.5, fill = "#035AA6")` $~~~$ [**Preregistration at osf.io/rpu98**](https://osf.io/rpu98)
+
 ]
@@
 For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions – compared to a single research team that comes to a single, joint conclusion – to be more swayed by the findings, as it seems to reflect consensus between various approaches.
+After all, it’s a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence, and to provide a “sensitivity analysis” or “robustness checks” to examine whether and how the findings change as a result of alternative analytic specifications.
+As argued in Aczel et al., “The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher’s idiosyncratic choice (…) when reasonable alternatives exist.” The same argument has been made for triangulation, which, according to Jick, “allows researchers to be more confident of their results.”
+We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
+Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
+Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
+However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
 
@@
 For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+
+Our pre-registered hypotheses can be found in the table: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
+For the multi-inconsistent condition, we hypothesized that lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
+In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both multi-analyst conditions.
 
@@
 `r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**
+
+`r icon_style(icons::academicons("preregistered"), scale = 1.5, fill = "#035AA6")` $~~~$ [**Preregistration at osf.io/rpu98**](https://osf.io/rpu98)
 

### 2021-10-08 talk/index.Rmd
first draft experimental design diagram

@@
 library(icons)
+library(widgetframe)
+library(DiagrammeR)
 
@@
 ---
+class: center
+
+# Experimental Design
+
+```{r, fig.align='right', fig.retina=3, echo = FALSE}
+my_design <- DiagrammeR::mermaid("
+graph TD
+
+classDef classOne fill:#c8e2fa,stroke:#333,stroke-width:4px
+classDef classTwo fill:#e8e9eb,stroke:#333,stroke-width:4px
+
+A[<center>Introduction to research question <br> Do religious people report higher well-being?</center>] 
+A ==>B[<center>Report prior beliefs <br> How likely do you think it is that people who are more religious generally report higher well-being?</center>]
+B ==>C[<center>Single-analyst condition</center>]
+B ==>D[<center>Multi-consistent condition</center>]
+B ==>E[<center>Multi-inconsistent condition</center>]
+F[<center>Report dependent variables <br> Posterior beliefs, credibility of the results, confidence in the effect size estimate, bias, error, and discretion</center>]
+C ==>F
+D ==>F
+E ==>F
+
+class A classOne
+class B classTwo
+class C classOne
+class D classTwo
+class E classOne
+class F classTwo
+
+                           ")
+widgetframe::frameWidget(my_design)
+```
+
+---
 .center[

### 2021-10-08 talk/index.Rmd
resorted to live editor mermaid for experimental design diagram

--- 2021-10-07 talk/index.Rmd
@@
 ---
+class: left
+
+# Experimental design
+
+--
+
+```{r, echo=FALSE, fig.align='center', out.width='80%', fig.retina=3}
+knitr::include_graphics("images/mermaid.png")
+```
+
+---
 .center[
@@
 ]
-
 .panel[.panel-name[Prior Beliefs]

### 2021-10-08 talk/index.Rmd
changed font mermaid diagram
changed size mermaid diagram
added participant flow chart (and changed experimental design diagram once again)

@@
 
-```{r, echo=FALSE, fig.align='center', out.width='80%', fig.retina=3}
+```{r, echo=FALSE, fig.align='center', out.width='95%', fig.retina=3}
 knitr::include_graphics("images/mermaid.png")
@@
 ---
+
 .center[
@@
 ---
+class: left
+
+# Participants
+
+--
+
+```{r, echo = FALSE, fig.retina=3, fig.align='center', out.width='110%'}
+knitr::include_graphics("images/participants.png")
+```
+
+---
 class: inverse, center, middle

### 2021-10-08 talk/index.Rmd
Added results to talk

@@
 class: inverse, center, middle
+
+# Main results
+
+---
+background-image: url("images/Figure1.jpg")
+background-position: 50% 50%
+background-size: 78%
+
+???
+
+Our main findings are displayed in Figure 1.
+Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, b=-5.71, and the multi-inconsistent condition, b=-22.80; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, b=-6.54, while they were not significantly different in the multi-consistent condition, b=1.24 (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, b=-9.09, while it was not significantly different in the multi-consistent condition, b=0.49; (4) ratings of bias were significantly greater in the multi-inconsistent condition, b=6.68, while they were not significantly different in the multi-consistent condition, b=2.13; and (5) ratings of error were significantly greater in both the multi-consistent condition, b=3.59, and the multi-inconsistent condition, b=5.89.
+For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, b=5.14, and the multi-inconsistent condition, b=9.22.
+
+---
+.center[
+
+# Results: Multi-inconsistent
+
+]
+
+**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error  
+--
+
+$~~$  
+For the additional **exploratory measure**, lay consumers of multi-analyst studies with **inconsistent** results
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom
+
+???
+
+In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
+Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
+---
+.center[
+
+# Results: Multi-consistent
+
+]
+
+**Contrary to our hypotheses**, lay consumers of multi-analyst studies with **consistent** results  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error  
+--
+
+$~~$  
+We found **no significant effects** on  
+--
+
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Credibility of the results  
+--
+
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the effect size estimate  
+--
+
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Ratings of bias  
+--
+
+$~~$  
+For the additional **exploratory measure**, lay consumers of multi-analyst studies with **consistent** results
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom
+
+???
+
+In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
+Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
+
+---
+
+class: inverse, center, middle
 name: discussion

### 2021-10-08 talk/index.Rmd
talk: more results, added discussion slide

@@
 
+???
+
+In all three conditions the estimates average to 5%
+
 ---
@@
 
+???
+
+500 in the multi-consistent condition, 499 in the single-analyst and the multi-inconsistent condition
+
 ---
@@
 ---
+background-image: url("images/Figure2.jpg")
+background-position: 50% 50%
+background-size: 78%
+
+???
+
+Note.
+Prior beliefs are displayed in blue; posterior beliefs are displayed in orange.
+The respective boxes display the lower quartiles, medians, and upper quartiles of prior and posterior beliefs by condition.
+
+It is worth noting on the basis of Figure 2 and a post-hoc, paired t-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs within the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, M_d=4.75, p<.001.
+This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms — however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.
+
+---
 
@@
 # Discussion
+
+---
+
+# Conclusion
+
+`r icon_style(icons::fontawesome("bullseye"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
+--
+
+`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ However, scientific reform may have **unintended consequences**   
+--
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Do lay consumers respond negatively to **variability** and  **lack of consensus**?   
+--
+
+## Future directions
+`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
+--
+
+`r icon_style(icons::fontawesome("lightbulb"), scale = 1.5, fill = "#035AA6")` $~~~$ Other **suggestions**?
+
+???
+
+From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
+The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
+However, as with any real-world intervention, scientific reform can have unintended consequences.
+Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
+While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
+To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.
+
+---
+class: inverse, center, middle
+
+# Thank you!

### 2021-10-09 talk/index.Rmd
boldened important elements in datatable with html

@@
   Quote = c(
-    "When the results of independent data analyses converge, more confidence in the conclusions is warranted.
+    "When the results of independent data analyses converge, <b>more confidence in the conclusions</b> is warranted.
 When the results diverge, confidence appropriately falters, and scientists can examine the reasons for these discrepancies.",
 
-    "For the public to have faith in the conclusions of scientists it is important that the methods they employ are robust and transparent.
+    "<b>For the public to have faith in the conclusions of scientists</b> it is important that the methods they employ are robust and transparent.
 This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis.",
 
-    "Several researchers analyze the same research question with the same data (…) Science is credible if different researchers come up with a similar answer",
+    "Several researchers analyze the same research question with the same data (…) <b>Science is credible</b> if different researchers come up with a similar answer",
 
-    "Organized scientific knowledge production (…) should generate inter-researcher reliability, offering consumers of scientific findings assurance that they are not arbitrary flukes but that other researchers would generate similar findings given the same data.",
+    "Organized scientific knowledge production (…) should generate inter-researcher reliability, <b>offering consumers of scientific findings assurance</b> that they are not arbitrary flukes but that other researchers would generate similar findings given the same data.",
 
-    "crowdsourcing provides a new way to increase credibility for political and social research—in both sample populations and among the researchers themselves (…) It is hoped that these developments are tangible outcomes that increase public, private, and government views of social science.",
+    "crowdsourcing provides a new way to <b>increase credibility</b> for political and social research—in both sample populations and among the researchers themselves (…) It is hoped that these developments are tangible outcomes that <b>increase public, private, and government views of social science</b>.",
 
-    "the results are more credible (…) greater certainty comes from having an independent check.",
+    "the results are <b>more credible</b> (…) <b>greater certainty</b> comes from having an independent check.",
 
-    "Scientists can have comparatively more faith in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
-(…) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have no faith that the hypothesis is true",
+    "Scientists can have comparatively <b>more faith</b> in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
+(…) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have <b>no faith</b> that the hypothesis is true",
 
-    "crowdsourced teams can conduct high-powered, precise studies and draw confident conclusions.
-(…) Crowdsourcing research is a part of a changing landscape of science that seeks to improve research reliability and advance the credibility of academic research"
+    "crowdsourced teams can conduct high-powered, precise studies and draw <b>confident conclusions</b>.
+(…) Crowdsourcing research is a part of a changing landscape of science that seeks to <b>improve research reliability</b> and <b>advance the credibility</b> of academic research"
 
@@
 
-DT::datatable(t2, fillContainer = FALSE, options = list(pageLength = 2))
+DT::datatable(t2, 
+              fillContainer = FALSE, 
+              options = list(pageLength = 2),
+              escape = FALSE)
 ```
@@
 class: inverse, center, middle
-name: lay
 

### 2021-10-09 talk/index.Rmd
talk: added bullet to discussion

@@
 
-`r icon_style(icons::fontawesome("bullseye"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
+`r icon_style(icons::fontawesome("route"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
 --
@@
 `r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
+--
+
+`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~$ Importance of **science communication** and **communicating uncertainty**  
 --

### 2021-10-10 manuscript/manuscript.Rmd
poster: first draft, manuscript+talk: improved figures (greater fonts, color for results), small changes in text

@@
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to answer a research question and/or estimate a parameter of interest.
-We compare the effects of providing (a) a single, aggregate parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that (b) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (c) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) vs.
+multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
 In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
@@
 a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing (a) a single, aggregate parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that (b) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (c) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) vs.
+multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
 According to previous work, crowdsourced data analysis should increase the credibility of scientific findings; Table 1 provides an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
@@
 ## Table 2
+*Predicted direction of effects compared to the single-analyst condition*
 
@@
 Table 2 indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction).
-For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the multi-consistent condition and lower in the multi-inconsistent condition.
+
 \newpage
@@
 ## Figure 1
-*Ratings of Bias, Confidence, Credibility, Discretion, Error, and Posterior Beliefs*
+*Estimates and 95% Confidence Intervals for all outcomes*
 \noindent
@@
                                      "Error",
-                                     "Discretion")))
+                                     "Discretion"))) %>% 
+  mutate(Conclusion = case_when(
+    conf.low < 0 & conf.high < 0 ~ "Negative",
+    conf.low < 0 & conf.high > 0 ~ "Inconclusive",
+    conf.low > 0 & conf.high > 0 ~ "Positive"
+  ))
 
@@
 
-p1 <- ggplot(mapping = aes(x = term, y = estimate), 
+p1 <- ggplot(mapping = aes(x = term, 
+                           y = estimate,
+                           color = Conclusion), 
              data = tidy_results) +
@@
   theme(strip.background = element_rect(fill = "white"),
-        legend.position = "") +
+        legend.position = "",
+        text = element_text(size = 16)) +
   labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
-   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))
+   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))  +
+  scale_color_discrete(type = c("darkgrey", "red", "green4"))
 
@@
 *Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of posterior beliefs, credibility, confidence, bias, error, and discretion in the two multi-analyst conditions, compared to the single-analyst condition (and controlling for prior beliefs).
+Green/red/gray error bars indicate positive/negative/insignificant findings, respectively.
 
@@
 
-colors <- rep(c("dodgerblue", "darkorange"), 3) #choose colors
+colors <- rep(c("#2142d9", "darkorange"), 3) #choose colors
 
@@
   size = 1,
-  alpha = .6,
+  alpha = .7,
   ort = "h") + #set to v for vertical plot
@@
   annotate(geom = "text", 
-           label = "Single-Analyst", 
-           x = 3.9, y = 13, hjust = 1) + 
+           label = "Single-analyst", 
+           x = 3.8, y = 12, size = 6) + 
   annotate(geom = "text", 
-           label = "Multi-Analyst: Consistent", 
-           x = 2.7, y = 11) + 
+           label = "Multi-consistent", 
+           x = 2.7, y = 14, size = 6) + 
   annotate(geom = "text", 
-           label = "Multi-Analyst: Inconsistent",
-           x = 1.75, y = 12) + 
+           label = "Multi-inconsistent",
+           x = 1.75, y = 16, size = 6) + 
   annotate(geom = "text", 
            label = "Prior Beliefs", 
-           x = 4.2, y = 37, size = 5, 
-           color = "dodgerblue") + 
+           x = 4.2, y = 20, size = 10, 
+           color = "#2142d9") + 
   annotate(geom = "text", 
            label = "vs.", 
-           x = 4.2, y = 50, size = 5) + 
+           x = 4.2, y = 45, size = 10) + 
   annotate(geom = "text", 
            label = "Posterior Beliefs", 
-           x = 4.2, y = 66, size = 5, 
+           x = 4.2, y = 75, size = 10, 
            color = "darkorange") +
@@
   theme(axis.ticks.y = element_blank(),
-        axis.text = element_text(size = 9),
-        axis.title.y = element_blank())
+        #axis.text = element_text(size = 9),
+        axis.title.y = element_blank(),
+        text = element_text(size = 20))
 

### 2021-10-10 poster/GSPA_Poster.Rmd
poster: first draft, manuscript+talk: improved figures (greater fonts, color for results), small changes in text

---
title: |
  | Lay Perceptions of Scientific Findings:
  | The Risks of Variability and Lack of Consensus
author:
  - name: Insert first author name here 
    affil: 1
    orcid: ''
  - name: Insert second author name here
    affil: 1
affiliation:
  - num: 1
    address: Insert affiliation here
column_numbers: 3
#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    css: style.css
knit: pagedown::chrome_print
font_family: 'Cabin'
titletext_fontfamily: 'Cabin'
primary_colour: "#035AA6"
accent_colour: "#035AA6"
sectitle2_textcol: "#035AA6"
header-includes:
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(icons)
library(rsvg)
```

# Introduction

The **credibility of scientific research** is in doubt, among lay consumer (Hornsey & Fielding, 2017) and scientist (Pashler & Wagenmakers, 2021) alike. Several tools have been proposed to combat this "crisis of confidence" (Ibid., p. 528). One such tool is the **crowd science** approach: "the organization of scientific research in open and collaborative projects" (Franzoni & Sauermann, 2014, p. 1). We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.  
 $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019). Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve the credibility of scientific research?**

**Objectives**

We explore **the effects of scientific findings emerging from a crowd of researchers** (vs. a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.  
 $~~~~~$ We compare the effects of providing a single, aggregate parameter estimate (the **single-analyst** condition) vs. multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition). In all three conditions, the given estimates average to 5%.

**Preregistered Hypotheses**

**Table 1**: *Predicted direction of effects*

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| 1. Posterior beliefs | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
|2. Credibility | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
| 3. Confidence  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | 
| 4. Bias | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 5. Error | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 6. Discretion | No prediction | No prediction |
*Note*. Table 1 indicates the predicted direction of effects for all outcomes, **compared to the single-analyst condition** and **controlling for prior beliefs** (a green plus/red minus indicates a positive/negative prediction, respectively). For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the multi-consistent condition and lower in the multi-inconsistent condition.

# Methods

We run an experiment (*N* = 1,498) with **three conditions**  
`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single-analyst**  
A single, aggregate parameter estimate  
`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-consistent**  
Multiple parameter estimates with low variance and high consensus  
`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-inconsistent**  
Multiple parameter estimates with high variance and low consensus

**Experimental Design**

```{r, echo = FALSE, out.width='101%', fig.retina=3, fig.align='left'}
knitr::include_graphics("mermaid.png")
```

# Results

**Figure 1**: *Estimates (and 95% CIs) for all outcomes*

```{r, echo = FALSE, out.width='90%', fig.retina=3, fig.align='left'}
knitr::include_graphics("Figure1.jpg")
```

**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error

**Contrary to our hypotheses**, lay consumers of multi-analyst studies with **consistent** results  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error

We found **no significant effects** on  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Credibility of the results  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the effect size estimate  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Ratings of bias

**Exploratory results**

For the additional **exploratory measure**, lay consumers of multi-analyst studies (both with **consistent** and **inconsistent** results)  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Perceive greater researcher degrees of freedom

**Figure 2**: *Distribution of prior and posterior beliefs by condition*  
```{r, echo = FALSE, out.width='92%', fig.retina=3, fig.align='center'}
knitr::include_graphics("Figure2.jpg")
```

# Discussion  
**Conclusions**  
`r icon_style(icons::fontawesome("sitemap"), scale = 1.4, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.4, fill = "#035AA6")` $~~$ **Variability** and  **lack of consensus** may evoke negative responses

**Future Directions**  
`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~~$ Perceptions of **scientists**?  
`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**  
`r icon_style(icons::fontawesome("lightbulb"), scale = 1.5, fill = "#035AA6")` $~~~~$ Other **suggestions**?

**Open Science Statement**  
The preregistration, survey materials, data, and code that support the findings of this study are openly available on GitHub and the OSF.  
`r icon_style(icons::fontawesome("github"), scale = 1.5, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
`r icon_style(icons::academicons("osf"), scale = 1.5, fill = "#035AA6")` $~~$ [Insert OSF link here]

### 2021-10-10 manuscript/manuscript.Rmd
improvements figures (fonts, sizes), small edits talk+poster

@@
         legend.position = "",
-        text = element_text(size = 16)) +
+        text = element_text(size = 16, 
+                            family = "serif")) +
   labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
@@
 ggsave("Figure1.jpg", p1, 
-       width = 7, height = 5, units = "in")
+       width = 7, height = 5, units = "in") #save to manuscript folder
+
+ggsave(paste0(here(), "/talk/images/Figure1.jpg"), p1, 
+       width = 7, height = 5, units = "in") #save to talk folder
+
+ggsave(paste0(here(), "/poster/Figure1.jpg"), p1, 
+       width = 7, height = 5, units = "in") #save to poster folder
 
@@
 
-colors <- rep(c("#2142d9", "darkorange"), 3) #choose colors
+colors <- rep(c("#035AA6", "darkorange"), 3) #choose colors
 
@@
            label = "Single-analyst", 
-           x = 3.8, y = 12, size = 6) + 
+           x = 3.8, y = 13, size = 6,
+           family = "serif") + 
   annotate(geom = "text", 
            label = "Multi-consistent", 
-           x = 2.7, y = 14, size = 6) + 
+           x = 2.73, y = 14, size = 6,
+           family = "serif") + 
   annotate(geom = "text", 
            label = "Multi-inconsistent",
-           x = 1.75, y = 16, size = 6) + 
+           x = 1.78, y = 16, size = 6,
+           family = "serif") + 
   annotate(geom = "text", 
            label = "Prior Beliefs", 
-           x = 4.2, y = 20, size = 10, 
-           color = "#2142d9") + 
+           fontface = "bold",
+           x = 4.2, y = 26, size = 8, 
+           color = "#035AA6",
+           family = "serif") + 
   annotate(geom = "text", 
            label = "vs.", 
-           x = 4.2, y = 45, size = 10) + 
+           x = 4.2, y = 45, size = 8,
+           family = "serif") + 
   annotate(geom = "text", 
            label = "Posterior Beliefs", 
-           x = 4.2, y = 75, size = 10, 
-           color = "darkorange") +
+           fontface = "bold",
+           x = 4.2, y = 68, size = 8, 
+           color = "darkorange",
+           family = "serif") +
 
@@
         axis.title.y = element_blank(),
-        text = element_text(size = 20))
+        text = element_text(size = 16, family = "serif"))
 
 ggsave("Figure2.jpg", p2, 
-       width = 7, height = 5, units = "in")
+       width = 7, height = 5, units = "in") #save to manuscript folder
+
+ggsave(paste0(here(), "/talk/images/Figure2.jpg"), p2, 
+       width = 7, height = 5, units = "in") #save to talk folder
+
+ggsave(paste0(here(), "/poster/Figure2.jpg"), p2, 
+       width = 7, height = 5, units = "in") #save to poster folder
 

### 2021-10-10 poster/GSPA_Poster.Rmd
improvements figures (fonts, sizes), small edits talk+poster

@@
 sectitle2_textcol: "#035AA6"
-header-includes:
-  - \setlength{\parindent}{4em}
-  - \setlength{\parskip}{0em}
 ---
@@
 
-```{r, echo = FALSE, out.width='101%', fig.retina=3, fig.align='left'}
+```{r, echo = FALSE, out.width='100%', fig.retina=3, fig.align='left'}
 knitr::include_graphics("mermaid.png")
@@
 **Figure 1**: *Estimates (and 95% CIs) for all outcomes*
-
-```{r, echo = FALSE, out.width='90%', fig.retina=3, fig.align='left'}
+```{r, echo = FALSE, out.width='95%', fig.retina=3, fig.align='left'}
 knitr::include_graphics("Figure1.jpg")
 ```
-
 **In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
@@
 # Discussion  
-**Conclusions**  
+**Conclusion**  
 `r icon_style(icons::fontawesome("sitemap"), scale = 1.4, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    

### 2021-10-10 talk/index.Rmd
poster: first draft, manuscript+talk: improved figures (greater fonts, color for results), small changes in text
improvements figures (fonts, sizes), small edits talk+poster

@@
   theme(legend.position = c(0.35, 0.8),
-        text = element_text(size = 19))
+        text = element_text(size = 20, family = "serif"))
 
@@
 $~~$  
-and study the **effects on**
+In all three conditions, the given estimates average to 5%. We study the **effects on**
 
@@
 
-`r icon_style(icons::fontawesome("route"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
+`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**  
 --
@@
 
-`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Do lay consumers respond negatively to **variability** and  **lack of consensus**?   
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**   
 --

### 2021-10-11 manuscript/manuscript.Rmd
first draft GSPA abstract

@@
 a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) vs.
+We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single-analyst condition) vs.
 multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
@@
 In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% (SD = 2); and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% (SD = 8.25).
-Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) experimenter degrees of freedom.
+Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) researcher degrees of freedom.
 All questions were answered on a slider from 0% (not likely/credible/confident at all) to 100% (extremely likely/credible/confident).
@@
 An overview of our preregistered, directional hypotheses can be found in Table 2.
-We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of experimenter degrees of freedom are exploratory, and should be treated as such.
+We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of researcher degrees of freedom are exploratory, and should be treated as such.
 Because we test five separate hypotheses using two comparisons each (one comparison of the single-analyst vs.
@@
 Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`.
-For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
+For our exploratory measure of discretion, we found that ratings of researcher degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
 **[Insert Figure 1 here]**  
@@
 From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
+The multi-analyst approach has many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
 However, as with any real-world intervention, scientific reform can have unintended consequences.
@@
 While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
-To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.
+To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
 

### 2021-10-11 poster/GSPA_Abstract.Rmd
first draft GSPA abstract

---
title: |
  | Lay Perceptions of Scientific Findings:
  | The Risks of Variability and Lack of Consensus
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Word count: `r as.integer(sub("(\\d+).+$", "\\1", system(sprintf("wc -w %s", knitr::current_input()), intern = TRUE))) - 60`

# Introduction and Research Question

A recent movement towards crowd science -- the organization of scientific research in open and collaborative projects (Franzoni & Sauermann, 2014, p. 1) -- has emerged in the behavioral sciences (e.g., Schweinsberg et al., 2018; Silberzahn et al., 2018). One of the aims of crowd science is to increase the credibility of scientific research. The extent to which this goal is reached, however, remains untested: does crowd science improve lay perceptions of scientific findings?

# Objectives

We focus on crowdsourced data analysis, also known as the 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to estimate a parameter of interest. We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single-analyst condition) vs. multiple parameter estimates that show (a) low variance and high consensus (the "multi-consistent" condition) or (b) high variance and low consensus (the "multi-inconsistent" condition).

# Hypotheses

Table 1 reports our pre-registered hypotheses, which compare the two multi-analyst conditions to the single-analyst condition (while controlling for prior beliefs). Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings. Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings: in the multi-consistent condition, we except that lay consumers have higher posterior beliefs, find the results more credible, and are less likely to believe the results stem from bias or error.  
 $~~~~~~$ However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect a decrease in the sway of scientific findings. That is, when results across many analysts vary widely and lack consensus, we except that lay consumers have lower posterior beliefs, find the results less credible, and are more likely to believe the results stem from bias or error. In addition, we expect that the act of providing multiple (slightly to widely varying) parameter estimates decreases confidence in the aggregate parameter estimate in both multi-analyst conditions.

# Methods

After reporting their prior beliefs about a research question ("Do religious people report higher well-being?"), participants are randomly allocated to one of three experimental conditions in which they learn about the approach and findings of a scientific study. In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% and have low variance ($\sigma^2$ = 4); and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% and have high variance ($\sigma^2$ = 68).  
 $~~~~~$ Afterwards, participants rate their posterior beliefs, the credibility of the results, their confidence in the effect size estimate, and how likely it is that the estimate was influenced by bias, error, and researcher degrees of freedom. All questions were answered on a slider from 0% to 100%. For all measures, we run linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate. All hypotheses, statistical models, and code were preregistered.

# Results

We sampled 1,498 participants from the Prolific participant pool. We included participants from the United States or the United Kingdom who were over 18 years old and spoke English as a first language. Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs. For the multi-consistent condition, we found significantly lower posterior beliefs, ratings of credibility, and confidence in the effect size estimate (standardized effect size estimates *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and significantly higher ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001). For the multi-inconsistent condition, we found significantly lower posterior beliefs (*b* = -5.71, *p* < .001), significantly higher ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001), and no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the effect size estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).     
 $~~~~~~$ In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, multi-analyst studies with consistent results perform worse or no better *relative* to single-analyst studies: lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) report significantly lower posterior beliefs and are more likely to believe the results stem from error. However, it is worth noting (on the basis of Figure 2, which displays the distribution of prior and posterior beliefs across conditions) that, there is a significant, positive *absolute* effect on posterior beliefs within the multi-consistent condition ($M_d$ = 4.75, *p* < .001). This finding clarifies that multi-analyst studies can potentially be convincing in their own right -- however, when comparing to conventional, single-analyst research, crowdsourced data analysis does not seem to improve lay perceptions of scientific findings.

# Discussion and Impact

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. However, as with any real-world intervention, scientific reform can have unintended consequences and impose high costs. While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom. Given the resource-intensity of crowdsourced data analysis, our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.

### 2021-10-11 poster/GSPA_Poster.Rmd
first draft GSPA abstract

@@
  $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019).
-Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve the credibility of scientific research?**
+Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve lay perceptions of scientific findings?**
 
@@
 a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.
- $~~~~~$ We compare the effects of providing a single, aggregate parameter estimate (the **single-analyst** condition) vs.
+ $~~~~~$ We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the **single-analyst** condition) vs.
 multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition).

### 2021-10-11 index.Rmd
restructured repo (index.Rmd in root, to build a site for the slides)

--- 2021-10-10 talk/index.Rmd
@@
 
-ggsave("title_plot.jpg", title_plot, 
+ggsave("talk/title_plot.jpg", title_plot, 
        width = 7, height = 5, units = "in")
@@
 .pull-left[
-![](title_plot.jpg)
+![](talk/title_plot.jpg)
 ]
@@
 ---
-background-image: url("images/meteor.jpeg")
+background-image: url("talk/meteor.jpeg")
 background-position: 90% 73%
@@
 ```{r, echo=FALSE, fig.align='center', out.width='95%', fig.retina=3}
-knitr::include_graphics("images/mermaid.png")
+knitr::include_graphics("talk/mermaid.png")
 ```
@@
 ```{r, echo = FALSE, out.width='90%'}
-knitr::include_graphics("images/introduction.png")
+knitr::include_graphics("talk/introduction.png")
 ```
@@
 
-![](images/prior_beliefs.png)
+![](talk/prior_beliefs.png)
 ]
@@
 
-![](images/thanks.png)
+![](talk/thanks.png)
 ]
@@
 ```{r, echo = FALSE, out.width='93%'}
-knitr::include_graphics("images/design_single.png")
+knitr::include_graphics("talk/design_single.png")
 ```
@@
 ```{r, echo = FALSE, out.width='91%'}
-knitr::include_graphics("images/design_multi.png")
+knitr::include_graphics("talk/design_multi.png")
 ```
@@
 ```{r, echo = FALSE, out.width='80%'}
-knitr::include_graphics("images/results_single.png")
+knitr::include_graphics("talk/results_single.png")
 ```
@@
 ```{r, echo = FALSE, out.width='80%'}
-knitr::include_graphics("images/results_multi-consistent.png")
+knitr::include_graphics("talk/results_multi-consistent.png")
 ```
@@
 ```{r, echo = FALSE, out.width='80%'}
-knitr::include_graphics("images/results_multi-inconsistent.png")
+knitr::include_graphics("talk/results_multi-inconsistent.png")
 ```
@@
 ```{r, echo = FALSE, out.width='100%'}
-knitr::include_graphics("images/posterior_beliefs.png")
+knitr::include_graphics("talk/posterior_beliefs.png")
 ```
@@
 ```{r, echo = FALSE, out.width='100%'}
-knitr::include_graphics("images/credibility.png")
+knitr::include_graphics("talk/credibility.png")
 ```
@@
 ```{r, echo = FALSE, out.width='100%'}
-knitr::include_graphics("images/confidence.png")
+knitr::include_graphics("talk/confidence.png")
 ```
@@
 ```{r, echo = FALSE, out.width='100%'}
-knitr::include_graphics("images/bias.png")
+knitr::include_graphics("talk/bias.png")
 ```
@@
 ```{r, echo = FALSE, out.width='100%'}
-knitr::include_graphics("images/attention.png")
+knitr::include_graphics("talk/attention.png")
 ```
@@
 ```{r, echo = FALSE, fig.retina=3, fig.align='center', out.width='110%'}
-knitr::include_graphics("images/participants.png")
+knitr::include_graphics("talk/participants.png")
 ```
@@
 ---
-background-image: url("images/Figure1.jpg")
+background-image: url("talk/Figure1.jpg")
 background-position: 50% 50%
@@
 ---
-background-image: url("images/Figure2.jpg")
+background-image: url("talk/Figure2.jpg")
 background-position: 50% 50%

### 2021-10-11 manuscript/manuscript.Rmd
restructured repo (index.Rmd in root, to build a site for the slides)

@@
 
-ggsave(paste0(here(), "/talk/images/Figure1.jpg"), p1, 
+ggsave(paste0(here(), "/talk/Figure1.jpg"), p1, 
        width = 7, height = 5, units = "in") #save to talk folder
@@
 
-ggsave(paste0(here(), "/talk/images/Figure2.jpg"), p2, 
+ggsave(paste0(here(), "/talk/Figure2.jpg"), p2, 
        width = 7, height = 5, units = "in") #save to talk folder

### 2021-10-11 poster/GSPA_Abstract.Rmd
restructured repo (index.Rmd in root, to build a site for the slides)

@@
 To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
-Given the resource-intensity of crowdsourced data analysis, our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.
+Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.

### 2021-10-11 index.Rmd
added link to slides

@@
 --
-[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~$ Preregistration](https://osf.io/rpu98)
-
---
-
-[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~$ Open materials](https://osf.io/6vze3)
-
---
-
-[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~$ Open data](https://osf.io/b527v/)
-
---
-
-[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)
-
---
-
-[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~$ osf.io/vedb4](https://osf.io/vedb4)
-
---
-
-[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)
+[`r icon_style(icons::academicons("preregistered"), scale = 2, fill = "#035AA6")` $~~~$ Preregistration](https://osf.io/rpu98)
+
+--
+
+[`r icon_style(icons::academicons("open-materials"), scale = 2, fill = "#035AA6")` $~~~$ Open materials](https://osf.io/6vze3)
+
+--
+
+[`r icon_style(icons::academicons("open-data"), scale = 2, fill = "#035AA6")` $~~~$ Open data](https://osf.io/b527v/)
+
+--
+
+[`r icon_style(icons::fontawesome("r-project"), scale = 2, fill = "#035AA6")` $~~$ Reproducible manuscript](https://github.com/shilaan/Many-Analysts/tree/main/manuscript)
+
+--
+
+[`r icon_style(icons::academicons("osf"), scale = 2, fill = "#035AA6")` $~~~$ osf.io/vedb4](https://osf.io/vedb4)
+
+--
+
+[`r icon_style(icons::fontawesome("github"), scale = 2, fill = "#035AA6")` $~~~$ github.com/shilaan/many-analysts](https://github.com/shilaan/many-analysts)
+
+--
+
+[`r icon_style(icons::fontawesome("tv"), scale = 1.7, fill = "#035AA6")` $~~$ Slides at bit.ly/many-analysts](https://bit.ly/many-analysts)
 

### 2021-10-11 index.Rmd
fixed typo in table, added some speaker notes

@@
 
+???
+
+First, I'll share a brief open science statement and links to all the available materials. Then, I'll define crowd science.s
 ---
@@
     2020,
-    2018,
+    2021,
     2018
@@
 ```
+
+???
+3 papers published in 2021, one looking at variability in the analysis of replications, another one at opinions about different social policies, and one OBHDP looking at the effects of scientists’ gender and professional status on verbosity during group meetings.
+Two papers in 2020, one looking at variability in the analysis of fmri (neuroimaging datasets), another in applied microeconomics.
+One paper from 2019 that evaluated the extent to which clinical psychologists analyzing the same experience sampling data come to different conclusions about symptoms to target for treatment.
+And one really famous study in 2018, that looked at discrimination against darker skin toned soccer players, and arguably started the recent crowd science movement in behavioral science.
 

### 2021-10-11 index.Rmd
repositioned the speaker note
fixed mistake notes

@@
 
+???
+
+First, I'll share a brief open science statement and links to all the available materials. Then, I'll define crowd science.
+
 --
@@
 
-???
-
-First, I'll share a brief open science statement and links to all the available materials. Then, I'll define crowd science.s
 ---
@@
 This led to a detailed documentation of the great meteor shower and the birth of the citizen-science movement (highly inclusive, used for data collection.
+In terms of the two dimensions we just discussed, this project can be categorized as highly inclusive - because it sourced citizens - and as used in the stage of data collection.
 ---
@@
 ???
+
 3 papers published in 2021, one looking at variability in the analysis of replications, another one at opinions about different social policies, and one OBHDP looking at the effects of scientists’ gender and professional status on verbosity during group meetings.

### 2021-10-11 index.Rmd
add slide w question before methods
added speaker note
added Figure 1 to background of results slides

@@
 class: inverse, center, middle
+
+# Does Crowdsourcing Data Analysis Improve the Credibility of Scientific Findings `r icon_style(icons::fontawesome("question-circle"), scale = 1, fill = "white")`
+
+???
+
+Lofty statements and worthy goals - empirical claim, but no evidence yet. that's what we'll be looking at today.
+---
+class: inverse, center, middle
 name: method
@@
 ---
+background-image: url("talk/Figure1.jpg")
+background-position: 90% 60%
+background-size: 40%
+
 .center[
@@
 $~~$  
+$~~$
+
 For the additional **exploratory measure**, lay consumers of multi-analyst studies with **inconsistent** results

### 2021-10-11 index.Rmd
moved note

@@
 `r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**
---
-
-`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ However, scientific reform may have **unintended consequences**   
---
-
-`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**   
---
-
-## Future directions
-`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
---
-
-`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~$ Importance of **science communication** and **communicating uncertainty**  
---
-
-`r icon_style(icons::fontawesome("lightbulb"), scale = 1.5, fill = "#035AA6")` $~~~$ Other **suggestions**?
 
@@
 To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.
+Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.
+--
+
+`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ However, scientific reform may have **unintended consequences**   
+--
+
+`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**   
+--
+
+## Future directions
+`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
+--
+
+`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~$ Importance of **science communication** and **communicating uncertainty**  
+--
+
+`r icon_style(icons::fontawesome("lightbulb"), scale = 1.5, fill = "#035AA6")` $~~~$ Other **suggestions**?
 

### 2021-10-12 manuscript/manuscript.Rmd
restructured/shortened results section, centered hypotheses icons, changed title Fig 1 to clarify reference cat

@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "3,710"
+wordcount         : "3,692"
 
@@
          paste(apa_results$estimate$ConditionMulti_consistent,
-               apa_results$statistic$ConditionMulti_consistent,
-               sep = ", "),
+               strsplit(apa_results$statistic$ConditionMulti_consistent, ",")[[1]][2],
+               sep = ", "), #print without t-values, otherwise use apa_results$full_result
          paste(apa_results$estimate$ConditionMulti_inconsistent,
-               apa_results$statistic$ConditionMulti_inconsistent,
+               strsplit(apa_results$statistic$ConditionMulti_inconsistent, ",")[[1]][2],
                sep = ", ")
          )
+
 }
@@
 
-t_test <- t.test(df_multiconsistent$Final_beliefs, df_multiconsistent$Prior_beliefs, paired = TRUE)
-t_apa <- apa_print(t_test)
+t_test <- apa_print(t.test(df_multiconsistent$Final_beliefs, df_multiconsistent$Prior_beliefs, paired = TRUE))
+
+t_apa <- paste(t_test$estimate, 
+               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
+               sep = ", ")
 ```
@@
 This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).
-Our main findings are displayed in Figure 1.
-Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`.
-For our exploratory measure of discretion, we found that ratings of researcher degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.
+Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs.
+For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Confidence, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
+For the multi-consistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher (b) ratings of error, `r results(Error)`; and (c) discretion, `r results(Discretion)`, and no significant effects on (d) ratings of credibility, `r results(Credibility)`, (e) confidence in the effect size estimate, `r results(Confidence)`, or (f) ratings of bias, `r results(Bias)`.
 **[Insert Figure 1 here]**  
@@
 **[Insert Figure 2 here]**  
-It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa$full_result`.
+It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa`.
 This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.
@@
 | ------------- |  ------------- | ------------- | 
-| 1. Posterior beliefs | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-|2. Credibility | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 3. Confidence  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | 
-| 4. Bias | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 5. Error | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Discretion | No prediction | No prediction |
+| 1.
+Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+|2.
+Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+| 3.
+Confidence in precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+| 4.
+Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 5.
+Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
 *Note*.
@@
 ## Figure 1
-*Estimates and 95% Confidence Intervals for all outcomes*
+*Estimates relative to the single-analyst condition*
 \noindent

### 2021-10-12 poster/GSPA_Abstract.Rmd
restructured/shortened results section, centered hypotheses icons, changed title Fig 1 to clarify reference cat

@@
 
-# Introduction and Research Question
+# Introduction
 
-A recent movement towards crowd science -- the organization of scientific research in open and collaborative projects (Franzoni & Sauermann, 2014, p.
-1) -- has emerged in the behavioral sciences (e.g., Schweinsberg et al., 2018; Silberzahn et al., 2018).
-One of the aims of crowd science is to increase the credibility of scientific research.
+A recent movement towards crowd science has emerged in the behavioral sciences, with the aim of increasing the credibility of scientific research.
 The extent to which this goal is reached, however, remains untested: does crowd science improve lay perceptions of scientific findings?
-
-# Objectives
-
-We focus on crowdsourced data analysis, also known as the 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to estimate a parameter of interest.
-We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single-analyst condition) vs.
+ $~~~~~$ We focus on crowdsourced data analysis, also known as the multi-analyst approach: different teams of scientists independently analyze the same dataset to estimate a parameter of interest.
+We compare the effects of providing lay consumers with a single parameter estimate (the single-analyst condition) vs.
 multiple parameter estimates that show (a) low variance and high consensus (the "multi-consistent" condition) or (b) high variance and low consensus (the "multi-inconsistent" condition).
-
-# Hypotheses
-
-Table 1 reports our pre-registered hypotheses, which compare the two multi-analyst conditions to the single-analyst condition (while controlling for prior beliefs).
-Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings.
-Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings: in the multi-consistent condition, we except that lay consumers have higher posterior beliefs, find the results more credible, and are less likely to believe the results stem from bias or error.
- $~~~~~~$ However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect a decrease in the sway of scientific findings.
-That is, when results across many analysts vary widely and lack consensus, we except that lay consumers have lower posterior beliefs, find the results less credible, and are more likely to believe the results stem from bias or error.
-In addition, we expect that the act of providing multiple (slightly to widely varying) parameter estimates decreases confidence in the aggregate parameter estimate in both multi-analyst conditions.
+ $~~~~~$ Table 1 reports our preregistered hypotheses, which compare the two multi-analyst conditions to the single-analyst condition (while controlling for prior beliefs).
+When laypeople observe several scientists independently come to consistent (inconsistent) qualitative conclusions, we expect them to have higher (lower) posterior beliefs, find the results more (less) credible, and perceive lower (higher) degrees of bias and error.
+In addition, we expect that the act of providing multiple (slightly to widely varying) parameter estimates decreases confidence in the exact, aggregate parameter estimate in both multi-analyst conditions.
 
@@
 Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs.
-For the multi-consistent condition, we found significantly lower posterior beliefs, ratings of credibility, and confidence in the effect size estimate (standardized effect size estimates *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and significantly higher ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001).
-For the multi-inconsistent condition, we found significantly lower posterior beliefs (*b* = -5.71, *p* < .001), significantly higher ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001), and no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the effect size estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).
+For the multi-inconsistent condition, we found significantly lower posterior beliefs, ratings of credibility, and confidence in the effect size estimate (standardized effect size estimates *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and significantly higher ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001).
+For the multi-consistent condition, we found significantly lower posterior beliefs (*b* = -5.71, *p* < .001), significantly higher ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001), and no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the effect size estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).
  $~~~~~~$ In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.

### 2021-10-12 poster/GSPA_Poster.Rmd
restructured/shortened results section, centered hypotheses icons, changed title Fig 1 to clarify reference cat

@@
 
-**Figure 1**: *Estimates (and 95% CIs) for all outcomes*
+**Figure 1**: *Estimates relative to the single-analyst condition*
 ```{r, echo = FALSE, out.width='95%', fig.retina=3, fig.align='left'}
@@
 `r icon_style(icons::fontawesome("sitemap"), scale = 1.4, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
+`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.4, fill = "#035AA6")` $~~$ It's highly **resource-intensive**, and...    
 `r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.4, fill = "#035AA6")` $~~$ **Variability** and  **lack of consensus** may evoke negative responses
@@
 `r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**
-`r icon_style(icons::fontawesome("lightbulb"), scale = 1.5, fill = "#035AA6")` $~~~~$ Other **suggestions**?
 

### 2021-10-12 poster/GSPA_Abstract.Rmd
GSPA abstract: cut word count

@@
 
-Word count: `r as.integer(sub("(\\d+).+$", "\\1", system(sprintf("wc -w %s", knitr::current_input()), intern = TRUE))) - 60`
+Word count: 697
 
@@
 
-A recent movement towards crowd science has emerged in the behavioral sciences, with the aim of increasing the credibility of scientific research.
-The extent to which this goal is reached, however, remains untested: does crowd science improve lay perceptions of scientific findings?
- $~~~~~$ We focus on crowdsourced data analysis, also known as the multi-analyst approach: different teams of scientists independently analyze the same dataset to estimate a parameter of interest.
-We compare the effects of providing lay consumers with a single parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that show (a) low variance and high consensus (the "multi-consistent" condition) or (b) high variance and low consensus (the "multi-inconsistent" condition).
- $~~~~~$ Table 1 reports our preregistered hypotheses, which compare the two multi-analyst conditions to the single-analyst condition (while controlling for prior beliefs).
-When laypeople observe several scientists independently come to consistent (inconsistent) qualitative conclusions, we expect them to have higher (lower) posterior beliefs, find the results more (less) credible, and perceive lower (higher) degrees of bias and error.
-In addition, we expect that the act of providing multiple (slightly to widely varying) parameter estimates decreases confidence in the exact, aggregate parameter estimate in both multi-analyst conditions.
+Crowd science is on the rise in behavioral science and aims to increase its credibility.
+Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?
+ $~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset.
+We compare the effects of providing lay consumers with a single parameter estimate vs.
+multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.
+ $~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
+In addition, we expect that the act of providing multiple estimates decreases confidence in the aggregate parameter estimate in both multi-estimate conditions.
 
@@
 
-After reporting their prior beliefs about a research question ("Do religious people report higher well-being?"), participants are randomly allocated to one of three experimental conditions in which they learn about the approach and findings of a scientific study.
-In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% and have low variance ($\sigma^2$ = 4); and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% and have high variance ($\sigma^2$ = 68).
- $~~~~~$ Afterwards, participants rate their posterior beliefs, the credibility of the results, their confidence in the effect size estimate, and how likely it is that the estimate was influenced by bias, error, and researcher degrees of freedom.
-All questions were answered on a slider from 0% to 100%.
-For all measures, we run linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate.
-All hypotheses, statistical models, and code were preregistered.
+After participants report their prior beliefs about a research question ("Do religious people report higher well-being?"), we randomly allocate them to one of three conditions.
+In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the multi-inconsistent condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
+ $~~~~~$ Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.
 
@@
 
-We sampled 1,498 participants from the Prolific participant pool.
-We included participants from the United States or the United Kingdom who were over 18 years old and spoke English as a first language.
-Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs.
-For the multi-inconsistent condition, we found significantly lower posterior beliefs, ratings of credibility, and confidence in the effect size estimate (standardized effect size estimates *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and significantly higher ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001).
-For the multi-consistent condition, we found significantly lower posterior beliefs (*b* = -5.71, *p* < .001), significantly higher ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001), and no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the effect size estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).
- $~~~~~~$ In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, multi-analyst studies with consistent results perform worse or no better *relative* to single-analyst studies: lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) report significantly lower posterior beliefs and are more likely to believe the results stem from error.
-However, it is worth noting (on the basis of Figure 2, which displays the distribution of prior and posterior beliefs across conditions) that, there is a significant, positive *absolute* effect on posterior beliefs within the multi-consistent condition ($M_d$ = 4.75, *p* < .001).
-This finding clarifies that multi-analyst studies can potentially be convincing in their own right -- however, when comparing to conventional, single-analyst research, crowdsourced data analysis does not seem to improve lay perceptions of scientific findings.
+We sampled 1,498 participants from Prolific (native English speakers from the US and UK, over 18 years old).
+As preregistered, we regressed all outcomes on prior beliefs and condition (with the single-analyst condition as the reference category).
+Figure 1 displays the main findings.
+The multi-inconsistent condition decreased posterior beliefs, ratings of credibility, and confidence in the parameter estimate (standardized effect size *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and increased ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001).
+The multi-consistent condition decreased posterior beliefs (*b* = -5.71, *p* < .001) and increased ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the parameter estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).
+ $~~~~~~$ As hypothesized, consuming multiple, inconsistent estimates decreases lay posterior beliefs, credibility of the results, confidence in the average parameter estimate, and increases ratings of bias and error.
+Unexpectedly, consuming multiple, consistent estimates lowers lay posterior beliefs and increases ratings of error.
+Although the multi-consistent condition performs worse or no better than the single-analyst condition for all outcomes, there is a significant, positive *absolute* effect on posterior beliefs within the multi-consistent condition ($M_d$ = 4.75, *p* < .001; see Figure 2).
+This finding clarifies that multi-analyst studies with consistent outcomes can potentially be convincing in their own right -- however, relative to conventional, single-analyst research, crowdsourced data analysis does not seem to improve lay perceptions of scientific findings.
 
-# Discussion and Impact
+# Discussion
 
 From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-However, as with any real-world intervention, scientific reform can have unintended consequences and impose high costs.
-While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
-To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
+However, as with any real-world intervention, scientific reform can impose high costs, lack effectiveness, or have unintended consequences.
+ $~~~~~~$ While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
+To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error or idiosyncratic choices.
 Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.

### 2021-10-12 poster/GSPA_Poster.Rmd
GSPA abstract: cut word count

@@
 **Figure 2**: *Distribution of prior and posterior beliefs by condition*  
-```{r, echo = FALSE, out.width='92%', fig.retina=3, fig.align='center'}
+```{r, echo = FALSE, out.width='90%', fig.retina=3, fig.align='center'}
 knitr::include_graphics("Figure2.jpg")
@@
 **Conclusion**  
-`r icon_style(icons::fontawesome("sitemap"), scale = 1.4, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
-`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.4, fill = "#035AA6")` $~~$ It's highly **resource-intensive**, and...    
-`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.4, fill = "#035AA6")` $~~$ **Variability** and  **lack of consensus** may evoke negative responses
+`r icon_style(icons::fontawesome("sitemap"), scale = 1.3, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
+`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.3, fill = "#035AA6")` $~~$ It's highly **resource-intensive**, and...    
+`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.3, fill = "#035AA6")` $~$ **Variability** and  **lack of consensus** may evoke negative responses
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.3, fill = "#035AA6")` $~~$ Surprisingly, **multiple, consistent estimates may backfire**
 
 **Future Directions**  
-`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~~$ Perceptions of **scientists**?  
-`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**
+`r icon_style(icons::fontawesome("flask"), scale = 1.3, fill = "#035AA6")` $~~~$ Perceptions of **scientists**?  
+`r icon_style(icons::fontawesome("comments"), scale = 1.3, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**
 
@@
 The preregistration, survey materials, data, and code that support the findings of this study are openly available on GitHub and the OSF.  
-`r icon_style(icons::fontawesome("github"), scale = 1.5, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
-`r icon_style(icons::academicons("osf"), scale = 1.5, fill = "#035AA6")` $~~$ [Insert OSF link here]
+`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
+`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert OSF link here]

### 2021-10-12 index.Rmd
incorporated Benoît's feedback on talk pt.1

@@
   Author = c(
-    "Aczel et al.",
     "Arbon et al.",
-    "Auspurg & Brüderl",
     "Breznau et al.",
-    "Breznau",
-    "Silberzahn & Uhlmann",
-    "Silberzahn et al.",
-    "Uhlmann et al."
+    "Breznau"
   ),
@@
   Year = c(
-    2021,
     2019,
     2021,
-    2021,
-    2021,
-    2015,
-    2018,
-    2019
+    2021
   ),
   Quote = c(
-    "When the results of independent data analyses converge, <b>more confidence in the conclusions</b> is warranted.
-When the results diverge, confidence appropriately falters, and scientists can examine the reasons for these discrepancies.",
-
-    "<b>For the public to have faith in the conclusions of scientists</b> it is important that the methods they employ are robust and transparent.
-This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis.",
-
-    "Several researchers analyze the same research question with the same data (…) <b>Science is credible</b> if different researchers come up with a similar answer",
-
-    "Organized scientific knowledge production (…) should generate inter-researcher reliability, <b>offering consumers of scientific findings assurance</b> that they are not arbitrary flukes but that other researchers would generate similar findings given the same data.",
-
-    "crowdsourcing provides a new way to <b>increase credibility</b> for political and social research—in both sample populations and among the researchers themselves (…) It is hoped that these developments are tangible outcomes that <b>increase public, private, and government views of social science</b>.",
-
-    "the results are <b>more credible</b> (…) <b>greater certainty</b> comes from having an independent check.",
-
-    "Scientists can have comparatively <b>more faith</b> in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
-(…) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have <b>no faith</b> that the hypothesis is true",
-
-    "crowdsourced teams can conduct high-powered, precise studies and draw <b>confident conclusions</b>.
-(…) Crowdsourcing research is a part of a changing landscape of science that seeks to <b>improve research reliability</b> and <b>advance the credibility</b> of academic research"
+
+    "\"<b>For the public to have faith in the conclusions of scientists</b> it is important that the methods they employ are robust and transparent.
+This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis.\"",
+
+    "\"Organized scientific knowledge production (…) should generate inter-researcher reliability, <b>offering consumers of scientific findings assurance</b> that they are not arbitrary flukes but that other researchers would generate similar findings given the same data.\"",
+
+    "\"crowdsourcing provides a new way to <b>increase credibility</b> for political and social research—in both sample populations and among the researchers themselves (…) It is hoped that these developments are tangible outcomes that <b>increase public, private, and government views of social science</b>.\""
 
@@
 ) %>% 
-  arrange(desc(Year))
+  arrange(Author)
 
@@
               fillContainer = FALSE, 
-              options = list(pageLength = 2),
-              escape = FALSE)
+              options = list(pageLength = 3),
+              escape = FALSE,
+              autoHideNavigation = TRUE)
 ```
@@
 We run an experiment with **three conditions**
+
+???
+
+Three scenarios
+
 --
@@
 .pull-left[
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Posterior beliefs  
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceptions of credibility  
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Confidence in the aggregate effect size estimate  
-]
-.pull-right[
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of bias  
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of error  
-`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of discretion  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` **Posterior beliefs** about the reported phenomenon  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` **Credibility** of the results  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` **Confidence** in the aggregate estimate of 5%  
+]
+.pull-right[
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceived impact of **bias** on the 5% estimate  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceived impact of **error** on the 5% estimate  
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceived impact of **discretion** on the 5% estimate   
 ]
@@
 
+???
+
+Importantly, in both the single-analyst and the multi-analyst conditions we emphasize that there are a lot of choices to be made.
+
 ---
@@
 ---
-background-image: url("talk/Figure1.jpg")
+background-image: url("talk/Figure1b.jpg")
 background-position: 50% 50%
@@
 background-image: url("talk/Figure1.jpg")
-background-position: 90% 60%
+background-position: 95% 57%
 background-size: 40%
@@
 
-`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
---
-
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
---
-
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error  
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the aggregate estimate of 5%  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the 5% estimate is more likely to stem from bias  
+--
+
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the 5% estimate is more likely to stem from error  
 --
@@
 For the additional **exploratory measure**, lay consumers of multi-analyst studies with **inconsistent** results
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the 5% estimate is more likely to stem from idiosyncratic choices
 
@@
 
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error  
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the 5% estimate is more likely to stem from error  
 --
@@
 
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the effect size estimate  
---
-
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Ratings of bias  
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the aggregate parameter estimate of 5%  
+--
+
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Perceived impact of bias on the 5% estimate  
 --
@@
 For the additional **exploratory measure**, lay consumers of multi-analyst studies with **consistent** results
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the 5% estimate is more likely to stem from idiosyncratic choices
 
@@
 From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
-However, as with any real-world intervention, scientific reform can have unintended consequences.
-Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
-To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.
+However, as with any real-world intervention, scientific reform can impose high costs, lack effectiveness, or have unintended consequences.
+While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
+To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error or idiosyncratic choices.
 Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.

### 2021-10-12 poster/GSPA_Abstract.Rmd
incorporated Benoît's feedback on talk pt.1

@@
 
-Word count: 697
+Word count: 699
 
@@
 Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?
- $~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset.
+ $~~~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset.
 We compare the effects of providing lay consumers with a single parameter estimate vs.
 multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.
- $~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
+ $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
 In addition, we expect that the act of providing multiple estimates decreases confidence in the aggregate parameter estimate in both multi-estimate conditions.
@@
 In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the multi-inconsistent condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
- $~~~~~$ Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.
+ $~~~~~~~$ Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.
 
@@
 The multi-consistent condition decreased posterior beliefs (*b* = -5.71, *p* < .001) and increased ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the parameter estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).
- $~~~~~~$ As hypothesized, consuming multiple, inconsistent estimates decreases lay posterior beliefs, credibility of the results, confidence in the average parameter estimate, and increases ratings of bias and error.
+ $~~~~~~~~$ As hypothesized, consuming multiple, inconsistent estimates decreases lay posterior beliefs, credibility of the results, confidence in the average parameter estimate, and increases ratings of bias and error.
 Unexpectedly, consuming multiple, consistent estimates lowers lay posterior beliefs and increases ratings of error.
@@
 
-# Discussion
+# Discussion and Impact
 
@@
 However, as with any real-world intervention, scientific reform can impose high costs, lack effectiveness, or have unintended consequences.
- $~~~~~~$ While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
+ $~~~~~~~~$ While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
 To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error or idiosyncratic choices.

### 2021-10-12 poster/GSPA_Poster.Rmd
incorporated Benoît's feedback on talk pt.1

@@
 | 3.
-Confidence in precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+Confidence in the precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
 | 4.
@@
 `r icon_style(icons::fontawesome("sitemap"), scale = 1.3, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
-`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.3, fill = "#035AA6")` $~~$ It's highly **resource-intensive**, and...    
+`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.3, fill = "#035AA6")` $~~$ It's highly **resource-intensive**    
 `r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.3, fill = "#035AA6")` $~$ **Variability** and  **lack of consensus** may evoke negative responses
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.3, fill = "#035AA6")` $~~$ Surprisingly, **multiple, consistent estimates may backfire**
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.3, fill = "#035AA6")` $~~$ Surprisingly, even **multiple, consistent estimates may backfire**
 

### 2021-10-13 index.Rmd
incorporated feedback Benoît pt.2 (added slide with rationale + benefits)

@@
 
-`r icon_style(icons::fontawesome("question-circle"), scale = 2, fill = "#035AA6")` $~~~$ [**Lay Perceptions: Are Crowd-Scientific Findings More Credible?**](#lay)   
+`r icon_style(icons::fontawesome("question-circle"), scale = 2, fill = "#035AA6")` $~~~$ [**Lay Perceptions of Crowd-Scientific Findings**](#lay)   
 --
@@
 ---
+# The Rationale of Crowdsourced Data Analysis
+
+???
+
+What is the rationale of crowdsourced data analysis - why should we be convinced by its findings?
+
+--
+
+### **The Wisdom of the Crowd**
+
+--
+
+`r icon_style(icons::fontawesome("volume-up"), scale = 1.5, fill = "#035AA6")` $~~~$ Individual judgments are associated with **idiosyncratic noise**  
+--
+
+`r icon_style(icons::fontawesome("microphone-alt-slash"), scale = 1.5, fill = "#035AA6")` $~~$ Averaging over many judgments can **cancel** some of that noise
+
+---
+background-image: url("talk/ox.png")
+background-position: 99% 60%
+background-size: 35%
+
+# The Rationale of Crowdsourced Data Analysis
+
+### **The Wisdom of the Crowd**
+
+`r icon_style(icons::fontawesome("volume-up"), scale = 1.5, fill = "#035AA6")` $~~~$ Individual judgments are associated with **idiosyncratic noise**
+
+`r icon_style(icons::fontawesome("microphone-alt-slash"), scale = 1.5, fill = "#035AA6")` $~~$ Averaging over many judgments can **cancel** some of that noise
+
+$~~$
+
+In 1906, 787 people guessed the weight of an ox at a farmers' fair...
+
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` $~~$ The **mean** of all guesses was exactly **equal to the true value**
+
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` $~~$ The mean **outperformed** the estimates of **experts**
+
+`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` $~~$ The mean **outperformed** the individual **best guesser**
+
+???
+
+The true weight, and the mean of all guesses was 1197 pounds.
+This may seem unsurprising now, but it wasn't back then.
+Back then, the fact that crowds were wise was a surprise.
+Crowds mostly had negative associations, were referred to as mobs, and there was heated intellectual debate about restricting the right to vote to intellectuals, rather than democratizing society.
+
+To benefit from the wisdom of crowds several conditions must be in place.
+First each individual member of the crowd must have their own independent source of information.
+Second they must make individual decisions and not be swayed by the decisions of those around them.
+And third, there must be a mechanism in place that can collate these diverse opinions.
+
+---
+# Benefits of Crowdsourced Data Analysis
+
+### **Crowdsourced data analysis can help to...**
+
+???
+
+I'll mention some benefits, most of which are intimately related with each other, some of them will overlap.
+
+--
+`r icon_style(icons::fontawesome("users"), scale = 1.5, fill = "#035AA6")` $~~$   **Diversify** contributions to research
+
+???
+
+Promote inclusivity, include researchers from underrepresented institutions. This comes with all the benefits of diversity. 
+Allows us to leverage under-used resources and skills.
+We can't all be an expert on everything.
+If we recruit a diverse sample of data analysts, some may have expertise on a certain statistical method that is most appropriate for the data at hand, whereas others do not
+
+--
+
+`r icon_style(icons::fontawesome("bezier-curve"), scale = 1.5, fill = "#035AA6")` $~~$   Expose the **inherent variability** of results
+
+???
+
+Helps to acknowledge that results are very variable, and depend on idiosyncratic choices we have to make among multiple valid approaches, sometimes even choices we make unconsciously, such as the version of statistical software we rely on or the different defaults in for instance SPSS and R: the many-analyst approach does not *create* variability in results, it simply *exposes* it.
+that should give us pause and epistemic humility when we assess conventional scientific research: the particular outcome you're looking at is one from a distribution of outcomes that could have been possible, if the analyst had made different choices
+
+--
+
+`r icon_style(icons::fontawesome("route"), scale = 1.5, fill = "#035AA6")` $~~~$ Assess the **impact of individual analytic choices** on the results
+
+???
+
+Can we explain the strength of the evidence obtained by the individual decisions researchers make?
+Does the choice to include or exclude a certain control variable, to run a certain statistical model, to exclude or include certain participants, impact the results?
+Do people who obtain positive findings use more controls or exclude more participants?
+Do people who obtain negative findings use more complex statistical models?
+
+Shows us *the garden of forking paths*
+--
+
+`r icon_style(icons::fontawesome("dumbbell"), scale = 1.4, fill = "#035AA6")` $~~$ Assess the overall **analytic robustness** of a finding
+
+???
+
+To what extent does a finding hold across many different analytic specifications? Do the results come it consistently positive, or consistently negative, across different independent analyses?
+--
+
+`r icon_style(icons::fontawesome("vials"), scale = 1.5, fill = "#035AA6")` $~~$  **Increase confidence** when independent analyses yield the same conclusion
+
+???
+
+● Converging conclusions increase confidence in the analytical robustness of a finding
+● Diverging conclusions decrease confidence in the analytical robustness of a finding and prompt an examination of the reasons for the divergence"
+
+--
+
+`r icon_style(icons::fontawesome("divide"), scale = 1.5, fill = "#035AA6")` $~~~~$  Average across idiosyncratic analytic choices to obtain **more accurate parameter estimates**
+
+--
+`r icon_style(icons::fontawesome("balance-scale"), scale = 1.5, fill = "#035AA6")` $~~$   ... and to **balance out individual biases and errors** in the aggregate
+
+---
 class: inverse, center, middle
@@
 ---
-# Credibility of Crowd-Scientific Findings
-
-According to science reformers, crowd-scientific findings should **increase the credibility of scientific research**
+# Lay Perceptions of Crowd-Scientific Findings
+
+According to its proponents, crowdsourcing data analysis should **improve lay perceptions of scientific findings**  
 --
@@
 
-## Are Crowd-Scientific Findings More Credible `r icon_style(icons::fontawesome("question-circle"), scale = 1, fill = "#035AA6")`
+# Method
 
@@
 
-`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**
+`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**, but...
 
@@
 From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-However, as with any real-world intervention, scientific reform can impose high costs, lack effectiveness, or have unintended consequences.
+The multi-analyst approach has many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
+However, as with any real-world intervention, scientific reform can have unintended consequences.
+Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
 While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
@@
 
-`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ However, scientific reform may have **unintended consequences**   
---
-
-`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**   
+`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.5, fill = "#035AA6")` $~~$ It's highly **resource-intensive**  
+--
+
+`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**     
+--
+
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.6, fill = "#035AA6")` $~~$ Surprisingly, even **multiple, consistent estimates may backfire**   
 --

### 2021-10-13 manuscript/manuscript.Rmd
incorporated Benoît's feedback on talk pt.1
incorporated feedback Benoît pt.2 (added slide with rationale + benefits)

@@
 ```{r data-cleaning, include = FALSE}
-df <- read.csv(paste0(here(), "/data/data.csv"))
+df <- read.csv(here("data/data.csv"))
 df <- df[3:nrow(df),]
@@
 
-ggsave(paste0(here(), "/talk/Figure1.jpg"), p1, 
+ggsave(here("talk/Figure1.jpg"), p1, 
        width = 7, height = 5, units = "in") #save to talk folder
 
-ggsave(paste0(here(), "/poster/Figure1.jpg"), p1, 
+ggsave(here("poster/Figure1.jpg"), p1, 
        width = 7, height = 5, units = "in") #save to poster folder
+
+p1b <- p1 + 
+  ggtitle("Differences from the single-analyst condition") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggsave(here("talk/Figure1b.jpg"), p1b, 
+       width = 7, height = 5, units = "in") #save to talk folder
 
@@
 
-ggsave(paste0(here(), "/talk/Figure2.jpg"), p2, 
+ggsave(here("talk/Figure2.jpg"), p2, 
        width = 7, height = 5, units = "in") #save to talk folder
 
-ggsave(paste0(here(), "/poster/Figure2.jpg"), p2, 
+ggsave(here("poster/Figure2.jpg"), p2, 
        width = 7, height = 5, units = "in") #save to poster folder

### 2021-10-14 manuscript/manuscript.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

@@
 ```
+
+Change to this:
+
+<!-- The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
+Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
+528).
+One such tool is the crowd science approach: "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p.
+1].
+We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
+-->
+<!-- According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
+In the preregistration of an ongoing many-analysts study, Arbon et al.
+[-@arbon2019] justify their use of the novel approach by referring to the need for "the public to have faith in the conclusions of scientists".
+In a preprint of a conducted multi-analyst study, Breznau et al.
+[-@breznau2021, p.
+3] argue that independent data analyses with converging findings should offer "consumers of scientific findings assurance that they are not arbitrary flukes".
+In a commentary on the many analysts approach, Breznau [-@breznau2021a, p.
+311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
+-->
+<!-- We explore the effects of scientific findings emerging from a crowd of researchers (vs.
+a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
+We compare the effects of providing lay consumers with a single parameter estimate (the single-analyst condition) vs.
+multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+-->
+<!-- In line with social norm theory [@miller2016], we expect an individual who observes a crowd of scientists reach the same qualitative conclusion to be more likely to conform in opinion, and be swayed by the scientific findings, than an individual who observes the conclusion of a single scientist.
+Although observing several differing estimates (rather than a single estimate) may decrease lay confidence in the precise average estimate, it should increase beliefs about the reported phenomenon and decrease perceptions of bias and error.
+However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when the results generated by independent analyses vary widely and lack consensus in their qualitative conclusions, we expect a decrease in the sway of scientific findings.
+-->
+<!-- In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, and lower (greater) ratings of bias and error.
+In addition, we expect that observing differing estimates decreases confidence in the precise average parameter estimate in both multi-estimate conditions.
+-->
 
@@
 Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs.
-For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Confidence, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
+For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Credibility, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
 For the multi-consistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher (b) ratings of error, `r results(Error)`; and (c) discretion, `r results(Discretion)`, and no significant effects on (d) ratings of credibility, `r results(Credibility)`, (e) confidence in the effect size estimate, `r results(Confidence)`, or (f) ratings of bias, `r results(Bias)`.

### 2021-10-14 poster/GSPA_Abstract.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

@@
 
-Word count: 699
+Word count: 696
 
@@
 Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?
- $~~~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset.
+ $~~~~~~~$ We focus on crowdsourced data analysis: independent scientists estimate and report a parameter from the same dataset.
 We compare the effects of providing lay consumers with a single parameter estimate vs.
 multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.
- $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
-In addition, we expect that the act of providing multiple estimates decreases confidence in the aggregate parameter estimate in both multi-estimate conditions.
+ $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, and lower (greater) ratings of bias and error.
+In addition, we expect that observing differing estimates decreases confidence in the precise average parameter estimate in both multi-estimate conditions.
 

### 2021-10-14 poster/GSPA_Poster.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

@@
 1).
-We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
+We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: a crowd of scientists independently analyzes the same dataset to answer the same research question or estimate and report a parameter of interest.
  $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019).
@@
 a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.
- $~~~~~$ We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the **single-analyst** condition) vs.
+ $~~~~~$ We compare the effects of providing lay consumers with a single parameter estimate (the **single-analyst** condition) vs.
 multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition).
-In all three conditions, the given estimates average to 5%.
+In all three conditions, we emphasize that the given estimates average to 5%.
 
@@
 `r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single-analyst**  
-A single, aggregate parameter estimate  
+A single parameter estimate  
 `r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-consistent**  
-Multiple parameter estimates with low variance and high consensus  
+Multiple crowd estimates with low variance and high consensus  
 `r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-inconsistent**  
-Multiple parameter estimates with high variance and low consensus
+Multiple crowd estimates with high variance and low consensus
 

### 2021-10-14 poster/ORAprojectsummary.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

--- 2021-10-14 manuscript/manuscript.Rmd
@@
 ---
-title             : "Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus"
-shorttitle        : "Lay Perceptions of Multi-Analyst Studies"
+title             : "Lay Perceptions of Scientific Findings: The Risks of Variability and Lack of Consensus"
+shorttitle        : "Lay Perceptions of Scientific Findings"
 
 author:
-  - name          : "Shilaan Alzahawi"
+  - name          : "Insert first author name here"
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "655 Knight Way, Stanford, CA 94305"
-    email         : "shilaan@stanford.edu"
-  - name          : "Benoît Monin"
+    corresponding : no    # Define only one corresponding author
+    address       : ""
+    email         : ""
+  - name          : "Insert second author name here"
     affiliation   : "1"
@@
   - id            : "1"
-    institution   : "Stanford University, Graduate School of Business"
+    institution   : "Insert affiliation here"
 
 abstract: |
-  A recent movement towards crowd science has emerged in the behavioral sciences.
-One of the aims of crowd science is to increase the credibility of scientific research.
-Does it meet this promise in reality?
-We run an experiment to study the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs and ratings of credibility, confidence in an aggregate effect size estimate, bias, and error.
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to answer a research question and/or estimate a parameter of interest.
-We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
-In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific findings to lay consumers: instead, to our surprise, they lead to lower posterior beliefs and higher ratings of error.
+  Crowd science is on the rise in behavioral science and aims to increase the credibility of scientific research.
+Whether it does, however, remains untested.
+We run an experiment to study whether crowd science improves lay perceptions of scientific findings.
+We focus on crowdsourced data analysis: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
+  We compare the effects of providing lay consumers (*N* = 1,498) with a single non-crowdsourced parameter estimate (the single-analyst condition) vs.
+multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+In the single-analyst condition, a single team of six researchers reports a 5% estimate; in the multi-consistent condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the multi-inconsistent condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
+  According to our preregistered hypotheses and in line with social norm theory, when laypeople observe multiple consistent (inconsistent) estimates from independent scientists rather than a single estimate, we expect an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
+In addition, we expect that observing differing estimates decreases confidence in the precise average estimate in both multi-estimate conditions.
+`r knitr::load_cache("results")`
+  In line with our hypotheses, we find that lay consumers of multiple, inconsistent (high variance, low consensus) crowdsourced estimates have lower posterior beliefs, `r final_inconsistent`; find the results less credible, `r credibility_inconsistent`; have less confidence in the average effect size estimate, `r confidence_inconsistent`; and believe the results are more likely to stem from bias, `r bias_inconsistent`, and error, `r error_inconsistent`, than consumers of a single, non-crowdsourced estimate.
+Contrary to our hypotheses, we do not find that consuming multiple, consistent (low variance, high consensus) crowdsourced estimates improves lay perceptions of scientific findings: instead, to our surprise, it leads to lower posterior beliefs, `r final`, and higher ratings of error, `r error`, than a single, non-crowdsourced estimate.
 
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "3,692"
+wordcount         : "Abstract: 383, Project summary: x"
 
@@
 
-Change to this:
-
-<!-- The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
+The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
 Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
@@
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
--->
-<!-- According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
+According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
 In the preregistration of an ongoing many-analysts study, Arbon et al.
@@
 311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
--->
-<!-- We explore the effects of scientific findings emerging from a crowd of researchers (vs.
+We explore the effects of scientific findings emerging from a crowd of researchers (vs.
 a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
@@
 multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
--->
-<!-- In line with social norm theory [@miller2016], we expect an individual who observes a crowd of scientists reach the same qualitative conclusion to be more likely to conform in opinion, and be swayed by the scientific findings, than an individual who observes the conclusion of a single scientist.
-Although observing several differing estimates (rather than a single estimate) may decrease lay confidence in the precise average estimate, it should increase beliefs about the reported phenomenon and decrease perceptions of bias and error.
-However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when the results generated by independent analyses vary widely and lack consensus in their qualitative conclusions, we expect a decrease in the sway of scientific findings.
--->
-<!-- In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, and lower (greater) ratings of bias and error.
-In addition, we expect that observing differing estimates decreases confidence in the precise average parameter estimate in both multi-estimate conditions.
--->
-
-The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
-Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
-528).
-One such tool is the crowd science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
-Crowd science is defined as "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p.
-1].
-Crowd-scientific projects vary in their degree of selectivity: some are open to the general public (such projects are often referred to as "citizen science"), while others require the expertise of specialists [e.g., scientists\; @uhlmann2019, p.
-714].
-Here, we focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
-We explore the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
-According to previous work, crowdsourced data analysis should increase the credibility of scientific findings; Table 1 provides an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
-Does crowd science meet its promise -- to improve the credibility of scientific research -- in reality?
-Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings, as it seems to reflect consensus between various approaches.
-After all, it's a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence [@jick1979; @turner2017], and to provide a "sensitivity analysis" or "robustness checks" to examine whether and how the findings change as a result of alternative analytic specifications [@munoz2018; @steegen2016].
-As argued in Aczel et al.
-[-@aczel2020, p.
-562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher's idiosyncratic choice (…) when reasonable alternatives exist." The same argument has been made for triangulation, which, according to Jick [-@jick1979, p.
-608], "allows researchers to be more confident of their results."
-We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
-Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
-Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
-However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
-**[Insert Table 1 here]**  
-Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 2: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
-For the multi-inconsistent condition, we hypothesized that lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
-In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both multi-analyst conditions.
-**[Insert Table 2 here]**
-
-<!-- "Following the logic of the wisdom of the crowds, in which aggregating estimates reduces individual level biases (Galton, 1907; Lorge, Fox, Davitz, & Brenner, 1958; Surowiecki, 2004), the central tendency of the effect size estimates calculated by many different analysts may provide a less subjective and error-prone estimate of the effect."  (Schweinsberg et al., 2021: p.
-246-7) -->
+In line with social norm theory [@miller2016], we expect an individual who observes a crowd of scientists reach identical (differing) qualitative conclusions to be more (less) likely to conform in opinion, and be more (less) swayed by the scientific findings, than an individual who observes the conclusion of a single scientist.
+However, regardless of the presence or absence of consensus in conclusions, we expect that observing (slightly to widely) varying estimates decreases lay confidence in the precise average estimate.
+In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, lower (lower) confidence in the precise average parameter estimate, and lower (greater) ratings of bias and error.
 
 # Methods
-The preregistration of our experiment can be found in the Open Science Foundation (OSF) Registries at https://osf.io/rpu98.
-All data and code needed to reproduce this article can be found on GitHub at https://github.com/shilaan/many-analysts and the OSF at https://osf.io/vedb4/.
+All relevant materials -- including the preregistration, survey materials, data, and code -- are openly available on the OSF at [insert link].
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-## Participants
-We sampled participants from the Prolific participant pool.
-We included participants from the United States or the United Kingdom who were at least 18 years old and spoke English as a first language.
-We excluded participants who failed the attention check or attempted to take the survey more than once.
+We sampled UK- and US-based participants from the Prolific participant pool (native English speakers, over 18 years old).
+We excluded participants who failed an attention check or attempted to take the survey more than once.
 Our target sample size was 1,500 participants after exclusions.
-We aimed to keep sampling until reaching the desired number of valid participants or until 2 weeks passed (whichever came first).
-We expected relatively small effect sizes and decided on an upper limit on the number of participants based on monetary constraints.
-
-## Procedure and materials
-All survey materials can be found on the OSF at https://osf.io/md9z5/.
 After a brief introduction to a research question ("Do religious people report higher well-being?"), participants were asked to report their prior beliefs ("How likely do you think it is that people who are more religious generally report higher well-being?") on a slider from 0% (not likely at all) to 100% (extremely likely).
@@
 For all six measures, we run linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate.
-All hypotheses, statistical models, and code were preregistered at https://osf.io/rpu98.
-An overview of our preregistered, directional hypotheses can be found in Table 2.
+All hypotheses, statistical models, and code were preregistered.
 We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of researcher degrees of freedom are exploratory, and should be treated as such.
@@
 
-```{r data-cleaning, include = FALSE}
+```{r results, include = FALSE, cache = TRUE}
 df <- read.csv(here("data/data.csv"))
@@
 
+# Cache results in objects for abstract
+final <- results(Final_beliefs)
+final_inconsistent <- results(Final_beliefs, "Inconsistent")
+credibility <- results(Credibility)
+credibility_inconsistent <- results(Credibility, "Inconsistent")
+confidence <- results(Confidence)
+confidence_inconsistent <- results(Confidence, "Inconsistent")
+bias <- results(Bias)
+bias_inconsistent <- results(Bias, "Inconsistent")
+error <- results(Error)
+error_inconsistent <- results(Error, "Inconsistent")
+discretion <- results(Discretion)
+discretion_inconsistent <- results(Discretion, "Inconsistent")
+
 # Post-hoc t-test
@@
 Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
+While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
 To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
-
-## Acknowledgements
-We thank Nicole Clare Kolmstetter for valuable assistance in the data collection. This manuscript was created using `r cite_r("r-references.bib")`.
-
-## Disclosure statement
-There are no relevant financial or non-financial competing interests to report.
-
-## Data availability statement
-The data that support the findings of this study are openly available on GitHub at https://github.com/shilaan/many-analysts and the OSF at https://osf.io/vedb4/.
 
@@
 
-# Tables
-
-## Table 1
-## *Proposed credibility- and confidence-related benefits of crowdsourced data analysis*
-
-| Citation | Description of credibility- or confidence-related benefits | 
-| ------------- | ------------- | 
-| [@aczel2021, pp.
-3-4] | "When the results of independent data analyses converge, more confidence in the conclusions is warranted.
-When the results diverge, confidence appropriately falters, and scientists can examine the reasons for these discrepancies."|
-|[@arbon2019] | "For the public to have faith in the conclusions of scientists it is important that the methods they employ are robust and transparent.
-This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis." |
-| [@auspurg2021, pp. 1, 10]  | "Several researchers analyze the same research question with the same data (...) Science is credible if different researchers come up with a similar answer"  | 
-| [@breznau2021, p.
-3] | "Organized scientific knowledge production (...) should generate inter-researcher reliability, offering consumers of scientific findings assurance that they are not arbitrary flukes but that other researchers would generate similar findings given the same data." |
-| [@breznau2021a, p.
-311] | "crowdsourcing provides a new way to increase credibility for political and social research---in both sample populations and among the researchers themselves (...) It is hoped that these developments are tangible outcomes that increase public, private, and government views of social science." |
-|[@silberzahn2015, pp. 190-1]|"the results are more credible (...) greater certainty comes from having an independent check."|
-|[@silberzahn2018, p.
-352]|"Scientists can have comparatively more faith in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
-(...) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have no faith that the hypothesis is true"|
-|[@uhlmann2019, p.
-713]|"crowdsourced teams can conduct high-powered, precise studies and draw confident conclusions.
-(...) Crowdsourcing research is a part of a changing landscape of science that seeks to improve research reliability and advance the credibility of academic research"|
-
-\newpage
-
-## Table 2
-*Predicted direction of effects compared to the single-analyst condition*
-
-| Measure | Multi-consistent | Multi-inconsistent |
-| ------------- |  ------------- | ------------- | 
-| 1.
-Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-|2.
-Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 3.
-Confidence in precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 4.
-Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 5.
-Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
-*Note*.
-Table 2 indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction).
-For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the multi-consistent condition and lower in the multi-inconsistent condition.
-
-\newpage
-
 # Figures
@@
 ```{r fig-1, echo=FALSE}
-tidy_df <- function(Predictor) {
-  linear_mod <- lm(
-    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
-
-  tidy_lm <- tidy(linear_mod, conf.int = TRUE) %>% 
-    mutate(Measure = glue("{Predictor}")) %>% 
-    filter(term != "Prior_beliefs" & term != "(Intercept)")
-  tidy_lm
-}
-
-Predictors <- list("Final_beliefs", 
-                  "Credibility", 
-                  "Confidence", 
-                  "Bias", 
-                  "Error", 
-                  "Discretion")
-
-tidy_results <- Predictors %>% 
-  map(~ tidy_df(.x)) %>% 
-  bind_rows() %>% 
-  mutate(term = gsub("Condition", "", term),
-         Measure = factor(Measure,
-                          levels = c("Final_beliefs",
-                                     "Credibility",
-                                     "Confidence",
-                                     "Bias",
-                                     "Error",
-                                     "Discretion"))) %>% 
-  mutate(Conclusion = case_when(
-    conf.low < 0 & conf.high < 0 ~ "Negative",
-    conf.low < 0 & conf.high > 0 ~ "Inconclusive",
-    conf.low > 0 & conf.high > 0 ~ "Positive"
-  ))
-
-Measure.label = c("Posterior beliefs", Predictors %>% unlist() %>% tail(5))
-names(Measure.label) <- Predictors %>% unlist()
-
-p1 <- ggplot(mapping = aes(x = term, 
-                           y = estimate,
-                           color = Conclusion), 
-             data = tidy_results) +
-  geom_point(size = 2) +
-  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), 
-                size = 0.8, width = 0.2) +
-  geom_hline(yintercept = 0, linetype = "dashed", color = "gray34", alpha = 0.7) +
-  facet_wrap(~ Measure, 
-             labeller = labeller(Measure = Measure.label)) + 
-  theme_bw() + 
-  theme(strip.background = element_rect(fill = "white"),
-        legend.position = "",
-        text = element_text(size = 16, 
-                            family = "serif")) +
-  labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
-   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))  +
-  scale_color_discrete(type = c("darkgrey", "red", "green4"))
-
-ggsave("Figure1.jpg", p1, 
-       width = 7, height = 5, units = "in") #save to manuscript folder
-
-ggsave(here("talk/Figure1.jpg"), p1, 
-       width = 7, height = 5, units = "in") #save to talk folder
-
-ggsave(here("poster/Figure1.jpg"), p1, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
-p1b <- p1 + 
-  ggtitle("Differences from the single-analyst condition") +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggsave(here("talk/Figure1b.jpg"), p1b, 
-       width = 7, height = 5, units = "in") #save to talk folder
-
 knitr::include_graphics("Figure1.jpg", dpi = 1200)
@@
 ```{r raincloud, echo=FALSE}
-set.seed(341990)
-
-df <- df %>% 
-  group_by(Condition) %>% 
-  slice_sample(n = 499)
-
-df_2x3 <- data_2x2(
-  array_1 = df %>% filter(Condition == "Multi-inconsistent") %>% pull(Prior_beliefs),
-  array_2 = df %>% filter(Condition == "Multi-inconsistent") %>% pull(Final_beliefs),
-  array_3 = df %>% filter(Condition == "Multi-consistent") %>% pull(Prior_beliefs),
-  array_4 = df %>% filter(Condition == "Multi-consistent") %>% pull(Final_beliefs),
-  array_5 = df %>% filter(Condition == "Single") %>% pull(Prior_beliefs),
-  array_6 = df %>% filter(Condition == "Single") %>% pull(Final_beliefs),
-  labels = (c('Prior Beliefs','Final Beliefs')),
-  jit_distance = .09,
-  jit_seed = 321)
-
-colors <- rep(c("#035AA6", "darkorange"), 3) #choose colors
-
-p2 <- raincloud_2x3_repmes(
-  data = df_2x3,
-  colors = colors,
-  fills = colors,
-  size = 1,
-  alpha = .7,
-  ort = "h") + #set to v for vertical plot
-
-  scale_x_continuous(
-    breaks = c(1,2,3), 
-    limits = c(0.8, 4.3), 
-    labels = rep("", 3)) +
-  ylab("Rated Beliefs") +
-
-  annotate(geom = "text", 
-           label = "Single-analyst", 
-           x = 3.8, y = 13, size = 6,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "Multi-consistent", 
-           x = 2.73, y = 14, size = 6,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "Multi-inconsistent",
-           x = 1.78, y = 16, size = 6,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "Prior Beliefs", 
-           fontface = "bold",
-           x = 4.2, y = 26, size = 8, 
-           color = "#035AA6",
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "vs.", 
-           x = 4.2, y = 45, size = 8,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "Posterior Beliefs", 
-           fontface = "bold",
-           x = 4.2, y = 68, size = 8, 
-           color = "darkorange",
-           family = "serif") +
-
-  theme_classic() +
-  theme(axis.ticks.y = element_blank(),
-        #axis.text = element_text(size = 9),
-        axis.title.y = element_blank(),
-        text = element_text(size = 16, family = "serif"))
-
-ggsave("Figure2.jpg", p2, 
-       width = 7, height = 5, units = "in") #save to manuscript folder
-
-ggsave(here("talk/Figure2.jpg"), p2, 
-       width = 7, height = 5, units = "in") #save to talk folder
-
-ggsave(here("poster/Figure2.jpg"), p2, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
 knitr::include_graphics("Figure2.jpg", dpi = 1200)

### 2021-10-14 poster/ORAprojectsummary.Rmd
took out r-references ORA

@@
 
-bibliography      : ["r-references.bib", "references.bib"]
+bibliography      : ["references.bib"]
 
@@
 library(rsvg)
-r_refs("r-references.bib")
 ```

### 2021-10-15 manuscript/manuscript.Rmd
GSPA poster+abstract: incorporated feedback B, massive overhaul.

@@
 
+get_d <- function(Predictor, Multi_Condition = "Consistent") {
+  linear_mod <- lm(
+    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
+
+  apa_results <- apa_print(linear_mod)
+
+  ifelse(Multi_Condition == "Consistent",
+         parse_number(apa_results$table$statistic[2])/sqrt(499),
+         parse_number(apa_results$table$statistic[3])/sqrt(500)) 
+}
+
 # Post-hoc t-test
@@
 
-t_test <- apa_print(t.test(df_multiconsistent$Final_beliefs, df_multiconsistent$Prior_beliefs, paired = TRUE))
+t_test <- apa_print(t.test(df_multiconsistent$Final_beliefs,
+                           df_multiconsistent$Prior_beliefs, 
+                           paired = TRUE))
+
+cohens_d <- parse_number(gsub(".*=", "", t_test$statistic)) / sqrt(499)
+
+t_apa <- paste(t_test$estimate, 
+               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
+               sep = ", ")
+
+# Post-hoc t-test
+df_multi_inconsistent <- df %>% 
+  filter(Condition == "Multi-inconsistent")
+
+t_test <- apa_print(t.test(df_multi_inconsistent$Final_beliefs,
+                           df_multi_inconsistent$Prior_beliefs, 
+                           paired = TRUE))
+
+t_apa <- paste(t_test$estimate, 
+               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
+               sep = ", ")
+
+# Post-hoc t-test
+df_single <- df %>% 
+  filter(Condition == "Single")
+
+t_test <- apa_print(t.test(df_single$Final_beliefs,
+                           df_single$Prior_beliefs, 
+                           paired = TRUE))
 
@@
 
-p2 <- raincloud_2x3_repmes(
+raincloud <- function(label_c1, label_c2, label_c3){
+  raincloud_2x3_repmes(
   data = df_2x3,
@@
   annotate(geom = "text", 
-           label = "Single-analyst", 
+           label = label_c1, 
            x = 3.8, y = 13, size = 6,
@@
   annotate(geom = "text", 
-           label = "Multi-consistent", 
+           label = label_c2, 
            x = 2.73, y = 14, size = 6,
@@
   annotate(geom = "text", 
-           label = "Multi-inconsistent",
+           label = label_c3,
            x = 1.78, y = 16, size = 6,
@@
         text = element_text(size = 16, family = "serif"))
+}
+
+p2 <- raincloud("Single-analyst", "Multi-consistent", "Multi-inconsistent")
 
@@
 ggsave(here("poster/Figure2.jpg"), p2, 
+       width = 7, height = 5, units = "in") #save to poster folder
+
+p3 <- raincloud("Single estimate", "Consistent crowd", "Inconsistent crowd")
+
+ggsave(here("poster/Figure2b.jpg"), p3, 
        width = 7, height = 5, units = "in") #save to poster folder

### 2021-10-15 poster/GSPA_Abstract.Rmd
GSPA poster+abstract: incorporated feedback B, massive overhaul.

--- 2021-10-12 poster/GSPA_Abstract.Rmd
@@
 ---
-title: |
-  | Lay Perceptions of Scientific Findings:
-  | The Risks of Variability and Lack of Consensus
-output: pdf_document
+title: "Lay Perceptions of Scientific Findings: Swayed by the Crowd?"
+shorttitle        : "Lay Perceptions of Scientific Findings"
+
+author:
+  - name          : "First author name here"
+    affiliation   : "1"
+    corresponding : no    # Define only one corresponding author
+    address       : ""
+    email         : ""
+  - name          : "Second author name here"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Insert affiliation here"
+
+abstract: |
+
+keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
+wordcount         : "700"
+
+bibliography      : ["references.bib"]
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_word
 ---
@@
 
-Word count: 699
-
-# Introduction
-
 Crowd science is on the rise in behavioral science and aims to increase its credibility.
 Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?
- $~~~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset.
-We compare the effects of providing lay consumers with a single parameter estimate vs.
-multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.
- $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
-In addition, we expect that the act of providing multiple estimates decreases confidence in the aggregate parameter estimate in both multi-estimate conditions.
+We draw from theories on social norms and numerical cognition to hypothesize that consistent (inconsistent) crowd estimates will lead to higher (lower) posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower (higher) ratings of bias and error, than a single estimate.
 
@@
 After participants report their prior beliefs about a research question ("Do religious people report higher well-being?"), we randomly allocate them to one of three conditions.
-In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the multi-inconsistent condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
- $~~~~~~~$ Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.
+In the single estimate condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the consistent crowd condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the inconsistent crowd condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
+Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.
 
@@
 We sampled 1,498 participants from Prolific (native English speakers from the US and UK, over 18 years old).
-As preregistered, we regressed all outcomes on prior beliefs and condition (with the single-analyst condition as the reference category).
-Figure 1 displays the main findings.
-The multi-inconsistent condition decreased posterior beliefs, ratings of credibility, and confidence in the parameter estimate (standardized effect size *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and increased ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001).
-The multi-consistent condition decreased posterior beliefs (*b* = -5.71, *p* < .001) and increased ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the parameter estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).
- $~~~~~~~~$ As hypothesized, consuming multiple, inconsistent estimates decreases lay posterior beliefs, credibility of the results, confidence in the average parameter estimate, and increases ratings of bias and error.
-Unexpectedly, consuming multiple, consistent estimates lowers lay posterior beliefs and increases ratings of error.
-Although the multi-consistent condition performs worse or no better than the single-analyst condition for all outcomes, there is a significant, positive *absolute* effect on posterior beliefs within the multi-consistent condition ($M_d$ = 4.75, *p* < .001; see Figure 2).
-This finding clarifies that multi-analyst studies with consistent outcomes can potentially be convincing in their own right -- however, relative to conventional, single-analyst research, crowdsourced data analysis does not seem to improve lay perceptions of scientific findings.
+As preregistered, we regressed all outcomes on prior beliefs and condition (with the single estimate condition as the reference category).
+Compared to the single estimate condition, inconsistent crowd estimates decreased posterior beliefs (*b* = -22.80, *p* < .001, Cohen's *d* = -0.72), ratings of credibility (*b* = -6.54, *p* < .001, *d* = -0.21), and confidence in the parameter estimate (*b* = -9.09, *p* < .001, *d* = -0.26), and increased ratings of bias (*b* = 6.68, *p* < .001, *d* = 0.18), error (*b* = 5.89, *p* < .001, *d* = 0.18), and discretion (*b* = 9.22, *p* < .001, *d* = 0.29).
+Compared to the single estimate condition, consistent crowd estimates decreased posterior beliefs (*b* = -5.71, *p* < .001, *d* = -0.18) and increased ratings of error (*b* = 3.59, *p* = .016, *d* = 0.11) and discretion (*b* = 5.14, *p* < .001, *d* = 0.16); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380, *d* = 0.04), confidence in the average parameter estimate (*b* = 0.49, *p* = .749, *d* = 0.01), or ratings of bias (*b* = 2.13, *p* = .192, *d* = 0.06).
+As hypothesized, inconsistent crowd estimates lead to lower posterior beliefs, credibility of the results, and confidence in the average parameter estimate, and higher ratings of bias and error, than a single estimate.
+Unexpectedly, consistent crowd estimates lead to lower posterior beliefs and higher ratings of error than a single estimate.
+On all outcomes, consuming consistent crowd estimates performs worse or no better than consuming a single estimate.
+However, it is worth noting that there is a positive difference between prior and posterior beliefs within the consistent crowd condition ($M_d$ = 4.75, *d* = 0.19, *p* < .001; see Figure 2).
+This finding clarifies that a consistent crowd may sway observers --- however, relative to the conventional reporting of non-crowdsourced estimates, crowd estimates do not seem to improve lay perceptions of scientific findings.
 
@@
 From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-However, as with any real-world intervention, scientific reform can impose high costs, lack effectiveness, or have unintended consequences.
- $~~~~~~~~$ While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research.
-To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error or idiosyncratic choices.
-Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.
+However, as with any real-world intervention, scientific reform can have unintended consequences.
+While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of crowd science.
+To our surprise, even when the results generated by an independent crowd are largely consistent and lead to the same qualitative conclusion, lay consumers seem to respond negatively to observing multiple, variable estimates.
+In the future, it is important for crowd scientists to consider how -- e.g., by drawing from research on science communication -- to effectively communicate variable estimates while preserving or perhaps even improving the credibility of scientific research.

### 2021-10-15 poster/GSPA_Poster.Rmd
GSPA poster+abstract: incorporated feedback B, massive overhaul.

@@
   | Lay Perceptions of Scientific Findings:
-  | The Risks of Variability and Lack of Consensus
+  | Swayed by the Crowd?
 author:
@@
 
-The **credibility of scientific research** is in doubt, among lay consumer (Hornsey & Fielding, 2017) and scientist (Pashler & Wagenmakers, 2021) alike.
-Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
-528).
-One such tool is the **crowd science** approach: "the organization of scientific research in open and collaborative projects" (Franzoni & Sauermann, 2014, p.
-1).
-We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: a crowd of scientists independently analyzes the same dataset to answer the same research question or estimate and report a parameter of interest.
- $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019).
-Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve lay perceptions of scientific findings?**
+Every day, important scientific findings are rejected at large.
+From man-made climate change to the safety and efficacy of Covid-19 vaccinations, **science skepticism** has run rampant among lay consumers in modern society (Hornsey & Fielding, 2017).
+To **increase public faith in science**, some have proposed the use of **crowd science** (Silberzahn et al., 2018; Uhlmann et al., 2019).
+ $~~~~~$ We explore whether high consensus and low variance in parameter estimates among a **crowd** (the **consistent crowd** condition) can improve **lay perceptions of scientific findings**.
+In line with **social norm theory** (Miller & Prentice, 2016), we expect that **observing consensus among a crowd** will -- compared to the conclusion of a single scientist (the **single estimate** condition) -- increase conformity in opinion.
+Drawing from work on **intuitive statistics** (Gigerenzer & Murray, 2015), we also expect laypeople to intuitively follow the logic of the **wisdom of crowds**: the ability of an **aggregate of estimates** (rather than a single estimate) to **reduce noise** stemming from individual bias or error (Schweinsberg et al., 2021).
+  $~~~~~$ In contrast, when crowd estimates show low consensus and high variance (the **inconsistent crowd** condition), we predict that observers will be less swayed and more likely to **attribute** the findings to **bias** and **error**.
+In addition, due to the difficulty of lay reasoning about variation (Ben-Zvi & Garfield, 1999), we predict an **aversion to variability**: i.e., we expect that observing variable estimates will decrease lay **confidence** in the precise average parameter estimate in both crowd conditions.
 
-**Objectives**
+# Hypotheses
+ **Table 1**: *Predicted differences with the single estimate condition*
 
-We explore **the effects of scientific findings emerging from a crowd of researchers** (vs.
-a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.
- $~~~~~$ We compare the effects of providing lay consumers with a single parameter estimate (the **single-analyst** condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition).
-In all three conditions, we emphasize that the given estimates average to 5%.
-
-**Preregistered Hypotheses**
-
-**Table 1**: *Predicted direction of effects*
-
-| Measure | Multi-consistent | Multi-inconsistent |
+| Measure | Consistent crowd | Inconsistent crowd |
 | ------------- |  ------------- | ------------- | 
 | 1.
-Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+Posterior beliefs in the phenomenon | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
 |2.
@@
 Confidence in the precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 4.
-Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 5.
-Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
-*Note*.
-Table 1 indicates the predicted direction of effects for all outcomes, **compared to the single-analyst condition** and **controlling for prior beliefs** (a green plus/red minus indicates a positive/negative prediction, respectively).
-For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the multi-consistent condition and lower in the multi-inconsistent condition.
+| 4. Bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 5. Error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 6. Discretion | $~~~$ No prediction | $~~~$ No prediction |  
+*Note.* We regress each outcome on **prior beliefs** and **condition** (with the **single estimate condition** as the **reference category**).
+When laypeople observe multiple consistent (inconsistent) estimates from a crowd, we expect -- compared to a single estimate and controlling for prior beliefs -- higher (lower) **posterior beliefs** and **credibility** of the results, lower **confidence** in the precise average parameter estimate, and lower (higher) ratings of **bias** and **error**.
+
+**Open Science:** Preregistration, survey, data, and code available at        
+`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
+`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert OSF link here]
 
@@
 
-We run an experiment (*N* = 1,498) with **three conditions**  
-`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single-analyst**  
-A single parameter estimate  
-`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-consistent**  
-Multiple crowd estimates with low variance and high consensus  
-`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-inconsistent**  
-Multiple crowd estimates with high variance and low consensus
+We ran an experiment (*N* = 1,498; UK/US Prolific) with **three conditions**  
+`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single estimate**  
+A single parameter estimate (5%)   
+`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Consistent crowd**  
+Multiple crowd estimates: low variance, high consensus (M = 5%)  
+`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Inconsistent crowd**  
+Multiple crowd estimates: high variance, low consensus (M = 5%)
 
@@
 
-**Figure 1**: *Estimates relative to the single-analyst condition*
-```{r, echo = FALSE, out.width='95%', fig.retina=3, fig.align='left'}
+**Figure 1**: *Estimates of differences with the single estimate condition*
+```{r, echo = FALSE, out.width='93%', fig.retina=3, fig.align='left'}
 knitr::include_graphics("Figure1.jpg")
 ```
-**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
-`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
-`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
-`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error
+**In line with our hypotheses**, lay consumers of **inconsistent crowd estimates** (vs. a single estimate)...  
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Have lower posterior beliefs about the reported phenomenon  
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Find the results less credible  
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Have less confidence in the average estimate of 5%  
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Are more likely to attribute the average estimate (5%) to bias   
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Are more likely to attribute the average estimate (5%) to error
 
-**Contrary to our hypotheses**, lay consumers of multi-analyst studies with **consistent** results  
-`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error
+**Contrary to our hypotheses**, lay consumers of **consistent crowd estimates** (vs. a single estimate)...  
+`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Have lower posterior beliefs about the reported phenomenon  
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Are more likely to attribute the average estimate (5%) to error
 
-We found **no significant effects** on  
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Credibility of the results  
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the effect size estimate  
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Ratings of bias
+We found **no significant effects** for lay consumers of **consistent crowd estimates** (vs. a single estimate) on...  
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~$ Credibility of the results  
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~$ Confidence in the average estimate   
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~$ Ratings of bias
 
@@
 
-For the additional **exploratory measure**, lay consumers of multi-analyst studies (both with **consistent** and **inconsistent** results)  
-`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Perceive greater researcher degrees of freedom
+For the additional **exploratory measure**, lay consumers of consistent and inconsistent **crowd estimates**...  
+`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Perceive greater discretion (i.e., idiosyncratic choices)
 
 **Figure 2**: *Distribution of prior and posterior beliefs by condition*  
-```{r, echo = FALSE, out.width='90%', fig.retina=3, fig.align='center'}
-knitr::include_graphics("Figure2.jpg")
+```{r, echo = FALSE, out.width='100%', fig.retina=3, fig.align='center'}
+knitr::include_graphics("Figure2b.jpg")
 ```
 
-# Discussion  
-**Conclusion**  
-`r icon_style(icons::fontawesome("sitemap"), scale = 1.3, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
-`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.3, fill = "#035AA6")` $~~$ It's highly **resource-intensive**    
-`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.3, fill = "#035AA6")` $~$ **Variability** and  **lack of consensus** may evoke negative responses
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.3, fill = "#035AA6")` $~~$ Surprisingly, even **multiple, consistent estimates may backfire**
+In terms of **belief updating**, Figure 2 shows a positive difference within the consistent crowd condition $($pre vs.
+post $M_d$ = 4.75 [2.55,6.95]$)$, but less so than for the single estimate condition $(M_d$ = 11.66 [9.66,13.66]$)$.
+As expected, we find negative belief updating in the inconsistent crowd condition $(M_d$ = -11.45 [-13.75,-9.16]$)$.
+
+# Conclusion 
+ $~~$ **Compared to providing a single estimate, we find no evidence that**   
+ $~~~~~~~$ **crowd estimates improve lay perceptions of scientific findings**
 
 **Future Directions**  
-`r icon_style(icons::fontawesome("flask"), scale = 1.3, fill = "#035AA6")` $~~~$ Perceptions of **scientists**?  
-`r icon_style(icons::fontawesome("comments"), scale = 1.3, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**
-
-**Open Science Statement**  
-The preregistration, survey materials, data, and code that support the findings of this study are openly available on GitHub and the OSF.  
-`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
-`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert OSF link here]
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "#035AA6")` $~~$ Does **variability aversion** explain the findings?  
+`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~~$ Perceptions of **scientists**  
+`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**

### 2021-10-16 poster/GSPA_Abstract.Rmd
last changes prior to submission GSPA + ORA

@@
 On all outcomes, consuming consistent crowd estimates performs worse or no better than consuming a single estimate.
-However, it is worth noting that there is a positive difference between prior and posterior beliefs within the consistent crowd condition ($M_d$ = 4.75, *d* = 0.19, *p* < .001; see Figure 2).
+However, it is worth noting that there is a positive difference between prior and posterior beliefs within the consistent crowd condition ($M_d$ = 4.75, *p* < .001, *d* = 0.19; see Figure 2).
 This finding clarifies that a consistent crowd may sway observers --- however, relative to the conventional reporting of non-crowdsourced estimates, crowd estimates do not seem to improve lay perceptions of scientific findings.

### 2021-10-16 poster/GSPA_Poster.Rmd
last changes prior to submission GSPA + ORA

@@
 To **increase public faith in science**, some have proposed the use of **crowd science** (Silberzahn et al., 2018; Uhlmann et al., 2019).
- $~~~~~$ We explore whether high consensus and low variance in parameter estimates among a **crowd** (the **consistent crowd** condition) can improve **lay perceptions of scientific findings**.
-In line with **social norm theory** (Miller & Prentice, 2016), we expect that **observing consensus among a crowd** will -- compared to the conclusion of a single scientist (the **single estimate** condition) -- increase conformity in opinion.
-Drawing from work on **intuitive statistics** (Gigerenzer & Murray, 2015), we also expect laypeople to intuitively follow the logic of the **wisdom of crowds**: the ability of an **aggregate of estimates** (rather than a single estimate) to **reduce noise** stemming from individual bias or error (Schweinsberg et al., 2021).
+ $~~~~~$ We explore the effects of scientific findings emerging from a **crowd** of researchers (vs.
+a typical research collaboration) on **lay perceptions of scientific findings**.
+In line with **social norm theory** (Miller & Prentice, 2016), we expect that observing **consensus** among a crowd (the **consistent crowd** condition) will -- compared to the conclusion of a single scientist (the **single estimate** condition) -- increase conformity in opinion.
+Drawing from work on **intuitive statistics** (Gigerenzer & Murray, 2015), we also expect laypeople to intuitively accord to logic of the **wisdom of crowds**: the ability of an **aggregate of multiple estimates** (rather than a single estimate) to **reduce noise** stemming from individual bias or error (Schweinsberg et al., 2021).
   $~~~~~$ In contrast, when crowd estimates show low consensus and high variance (the **inconsistent crowd** condition), we predict that observers will be less swayed and more likely to **attribute** the findings to **bias** and **error**.
@@
 ```{r, echo = FALSE, out.width='93%', fig.retina=3, fig.align='left'}
-knitr::include_graphics("Figure1.jpg")
+knitr::include_graphics("Figure1c.jpg")
 ```
@@
 
-**Future Directions**  
+**Future directions**  
 `r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "#035AA6")` $~~$ Does **variability aversion** explain the findings?  

### 2021-10-16 poster/ORAprojectsummary.Rmd
last changes prior to submission GSPA + ORA

@@
 ---
-title             : "Lay Perceptions of Scientific Findings: The Risks of Variability and Lack of Consensus"
+title             : "Lay Perceptions of Scientific Findings: Swayed by the Crowd?"
 shorttitle        : "Lay Perceptions of Scientific Findings"
@@
 author:
-  - name          : "Insert first author name here"
+  - name          : "First author name"
     affiliation   : "1"
@@
     email         : ""
-  - name          : "Insert second author name here"
+  - name          : "Second author name"
     affiliation   : "1"
@@
 We focus on crowdsourced data analysis: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
-  We compare the effects of providing lay consumers (*N* = 1,498) with a single non-crowdsourced parameter estimate (the single-analyst condition) vs.
-multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
-In the single-analyst condition, a single team of six researchers reports a 5% estimate; in the multi-consistent condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the multi-inconsistent condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
-  According to our preregistered hypotheses and in line with social norm theory, when laypeople observe multiple consistent (inconsistent) estimates from independent scientists rather than a single estimate, we expect an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error.
-In addition, we expect that observing differing estimates decreases confidence in the precise average estimate in both multi-estimate conditions.
+  We compare the effects of providing lay consumers (*N* = 1,498) with a single parameter estimate (the single estimate condition) vs.
+multiple parameter estimates from a crowd that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "consistent crowd" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "inconsistent crowd" condition).
+In the single estimate condition, a single team of six researchers reports a 5% estimate; in the consistent crowd condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the inconsistent crowd condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
+We draw from theories on social norms and numerical cognition to hypothesize that consistent (inconsistent) crowd estimates will lead to higher (lower) posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower (higher) ratings of bias and error, than a single estimate.
 `r knitr::load_cache("results")`
-  In line with our hypotheses, we find that lay consumers of multiple, inconsistent (high variance, low consensus) crowdsourced estimates have lower posterior beliefs, `r final_inconsistent`; find the results less credible, `r credibility_inconsistent`; have less confidence in the average effect size estimate, `r confidence_inconsistent`; and believe the results are more likely to stem from bias, `r bias_inconsistent`, and error, `r error_inconsistent`, than consumers of a single, non-crowdsourced estimate.
-Contrary to our hypotheses, we do not find that consuming multiple, consistent (low variance, high consensus) crowdsourced estimates improves lay perceptions of scientific findings: instead, to our surprise, it leads to lower posterior beliefs, `r final`, and higher ratings of error, `r error`, than a single, non-crowdsourced estimate.
+  In line with our preregistered hypotheses, we find that lay consumers of inconsistent (high variance, low consensus) crowd estimates have lower posterior beliefs, `r final_inconsistent`; find the results less credible, `r credibility_inconsistent`; have less confidence in the average effect size estimate, `r confidence_inconsistent`; and believe the results are more likely to stem from bias, `r bias_inconsistent`, and error, `r error_inconsistent`, than consumers of a single estimate.
+Contrary to our hypotheses, we do not find that consuming consistent (low variance, high consensus) crowd estimates improves lay perceptions of scientific findings: instead, to our surprise, it leads to lower posterior beliefs, `r final`, and higher ratings of error, `r error`, than a single estimate.
+In the future, it is important for crowd scientists to consider how -- e.g., by drawing from research on science communication -- to tackle science skepticism and effectively communicate variable crowd estimates to lay consumers.
 
-keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "Abstract: 383, Project summary: x"
+keywords          : "Crowd science, Science skepticism, Variability, Numerical cognition"
+wordcount         : "Abstract: 400, Project summary: 965"
 
@@
 
-The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
-Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
-528).
-One such tool is the crowd science approach: "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p.
-1].
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
-According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
-In the preregistration of an ongoing many-analysts study, Arbon et al.
-[-@arbon2019] justify their use of the novel approach by referring to the need for "the public to have faith in the conclusions of scientists".
-In a preprint of a conducted multi-analyst study, Breznau et al.
-[-@breznau2021, p.
-3] argue that independent data analyses with converging findings should offer "consumers of scientific findings assurance that they are not arbitrary flukes".
-In a commentary on the many analysts approach, Breznau [-@breznau2021a, p.
-311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
+Every day, important scientific findings are rejected at large.
+From man-made climate change to the safety and efficacy of Covid-19 vaccinations, science skepticism has run rampant among lay consumers in modern society [@hornsey2017].
+To increase public faith in science, some have proposed the use of crowd science [@silberzahn2018; @uhlmann2019].
 We explore the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing lay consumers with a single parameter estimate (the single-analyst condition) vs.
-multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
-In line with social norm theory [@miller2016], we expect an individual who observes a crowd of scientists reach identical (differing) qualitative conclusions to be more (less) likely to conform in opinion, and be more (less) swayed by the scientific findings, than an individual who observes the conclusion of a single scientist.
-However, regardless of the presence or absence of consensus in conclusions, we expect that observing (slightly to widely) varying estimates decreases lay confidence in the precise average estimate.
-In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, lower (lower) confidence in the precise average parameter estimate, and lower (greater) ratings of bias and error.
+a typical research collaboration) on lay perceptions of scientific findings.
+In line with social norms theory [@miller2016], we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
+Drawing from work on intuitive statistics [@gigerenzer2015a], we also expect laypeople to intuitively accord to the logic of "the wisdom of crowds": the ability of an aggregate of estimates (rather than a single estimate) to reduce noise stemming from individual bias or error [@schweinsberg2021].
+In contrast, when crowd estimates show low consensus and high variance (the inconsistent crowd condition), we predict that observers will be less swayed and more likely to attribute the findings to bias and error.
+In addition, due to the difficulty of lay reasoning about variation [@garfield2004], we predict an aversion to variability: i.e., we expect that observing variable estimates will decrease lay confidence in the precise average parameter estimate in both crowd conditions.
+In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- higher (lower) posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower (greater) ratings of bias and error.
 
 # Methods
-All relevant materials -- including the preregistration, survey materials, data, and code -- are openly available on the OSF at [insert link].
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures.
 We sampled UK- and US-based participants from the Prolific participant pool (native English speakers, over 18 years old).
-We excluded participants who failed an attention check or attempted to take the survey more than once.
-Our target sample size was 1,500 participants after exclusions.
-After a brief introduction to a research question ("Do religious people report higher well-being?"), participants were asked to report their prior beliefs ("How likely do you think it is that people who are more religious generally report higher well-being?") on a slider from 0% (not likely at all) to 100% (extremely likely).
-After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a scientific study.
-In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% (SD = 2); and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% (SD = 8.25).
-Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) researcher degrees of freedom.
-All questions were answered on a slider from 0% (not likely/credible/confident at all) to 100% (extremely likely/credible/confident).
-
-## Data analysis
-For all six measures, we run linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate.
-All hypotheses, statistical models, and code were preregistered.
-We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of researcher degrees of freedom are exploratory, and should be treated as such.
-Because we test five separate hypotheses using two comparisons each (one comparison of the single-analyst vs.
-the multi-consistent condition, and one comparison of the single-analyst vs.
-the multi-inconsistent condition), we use the Bonferroni method to correct for multiple comparisons.
-Thus, our preregistered threshold for statistical significance is $\displaystyle \alpha = \frac{.05}{2} = .025$.
+There was no prior work to base an excepted effect size on; due to our expectation of relatively small effect sizes and monetary constraints, we decided on an upper limit of 1,500 participants after exclusions.
+After participants report their prior beliefs about a research question ("Do religious people report higher well-being?"), we randomly allocate them to one of three conditions.
+In the single estimate condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the consistent crowd condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the inconsistent crowd condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).
+Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion (i.e., idiosyncratic choices).
+We did not preregister any hypotheses for the last measure; rated discretion is thus an exploratory measure.
 
@@
 
-After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics.
-We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check.
-This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).
-Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs.
-For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Credibility, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
-For the multi-consistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher (b) ratings of error, `r results(Error)`; and (c) discretion, `r results(Discretion)`, and no significant effects on (d) ratings of credibility, `r results(Credibility)`, (e) confidence in the effect size estimate, `r results(Confidence)`, or (f) ratings of bias, `r results(Bias)`.
-**[Insert Figure 1 here]**  
-In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
-Figure 2 further clarifies the sway of multi-analyst vs.
-single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.
-**[Insert Figure 2 here]**  
-It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa`.
-This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.
+We recorded 2,019 responses; after excluding `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check, our total sample size was 1,498 participants.
+As preregistered, we regressed all outcomes on prior beliefs and condition (with the single estimate condition as the reference category).
+Figure 1 displays the main findings.
+Compared to the single estimate condition, inconsistent crowd estimates decreased posterior beliefs (*b* = -22.80, *p* < .001, Cohen's *d* = -0.72), ratings of credibility (*b* = -6.54, *p* < .001, *d* = -0.21), and confidence in the parameter estimate (*b* = -9.09, *p* < .001, *d* = -0.26), and increased ratings of bias (*b* = 6.68, *p* < .001, *d* = 0.18), error (*b* = 5.89, *p* < .001, *d* = 0.18), and discretion (*b* = 9.22, *p* < .001, *d* = 0.29).
+Compared to the single estimate condition, consistent crowd estimates decreased posterior beliefs (*b* = -5.71, *p* < .001, *d* = -0.18) and increased ratings of error (*b* = 3.59, *p* = .016, *d* = 0.11) and discretion (*b* = 5.14, *p* < .001, *d* = 0.16); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380, *d* = 0.04), confidence in the average parameter estimate (*b* = 0.49, *p* = .749, *d* = 0.01), or ratings of bias (*b* = 2.13, *p* = .192, *d* = 0.06).
+As hypothesized, inconsistent crowd estimates lead to lower posterior beliefs, credibility of the results, and confidence in the average parameter estimate, and higher ratings of bias and error, than a single estimate.
+Unexpectedly, consistent crowd estimates lead to lower posterior beliefs and higher ratings of error than a single estimate.
+However, it is worth noting that there is a positive difference between prior and posterior beliefs within the consistent crowd condition ($M_d$ = 4.75, *p* < .001, *d* = 0.19; see Figure 2).
+This finding clarifies that a consistent crowd may sway observers --- however, compared to a conventional, non-crowdsourced estimate, crowd estimates do not seem to improve lay perceptions of scientific findings.
 
@@
 
-From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-The multi-analyst approach has many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
-However, as with any real-world intervention, scientific reform can have unintended consequences.
-Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
-To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
+Although crowd science aims to improve the credibility of scientific research, we find that lay consumers resist the variability and lack of consensus that often reflect its reality.
+To our surprise, even when results generated by a crowd are highly consistent, we find no improvement in lay perceptions.
+Further research is needed to consider the possible mechanisms behind this preliminary finding.
+In the future, it is important for crowd scientists to consider how to tackle science skepticism and effectively communicate variable estimates.
 
@@
 ## Figure 1
-*Estimates relative to the single-analyst condition*
+*Estimates of differences with the single estimate condition*
 \noindent
 ```{r fig-1, echo=FALSE}
-knitr::include_graphics("Figure1.jpg", dpi = 1200)
+knitr::include_graphics("Figure1c.jpg", dpi = 1200)
 ```
-*Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of posterior beliefs, credibility, confidence, bias, error, and discretion in the two multi-analyst conditions, compared to the single-analyst condition (and controlling for prior beliefs).
+*Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of posterior beliefs, credibility, confidence, bias, error, and discretion in the two crowd conditions, compared to the single estimate condition (and controlling for prior beliefs).
 Green/red/gray error bars indicate positive/negative/insignificant findings, respectively.
@@
 
-*Individual data points, quartiles, and distributions of prior and posterior beliefs in the single-analyst, multi-consistent, and multi-inconsistent conditions*  
+*Distribution of prior and posterior beliefs by condition*  
 \noindent
 ```{r raincloud, echo=FALSE}
-knitr::include_graphics("Figure2.jpg", dpi = 1200)
+knitr::include_graphics("Figure2b.jpg", dpi = 1200)
 ```

### 2021-10-26 index.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract
changes discussion slide

@@
 library(widgetframe)
-library(DiagrammeR)
 
@@
 
-$~~$
-
 ```{r, echo = FALSE}
@@
 
-# Conclusion
-
-`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**, but...
+$~~$
+
+.center[
+### **Compared to a single estimate, we find no evidence that crowd estimates improve lay perceptions of scientific findings**
+]
+
+$~~$
 
@@
 
-`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.5, fill = "#035AA6")` $~~$ It's highly **resource-intensive**  
---
-
-`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**     
---
-
-`r icon_style(icons::fontawesome("question-circle"), scale = 1.6, fill = "#035AA6")` $~~$ Surprisingly, even **multiple, consistent estimates may backfire**   
---
-
 ## Future directions
+`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "#035AA6")` $~~$ Does **variability aversion** explain the findings?
+
+???
+
+We conclude that, compared to a single estimate, we do not find evidence that crowd estimates improve lay perceptions of scientific findings.
+In the future, we are curious to explore whether it might be aversion to variability that explains these findings, and what the perceptions of scientists are.
+We also believe that in the future it is important for crowd scientists to consider how -- for example, by drawing from research on science communication -- to tackle science skepticism and effectively communicate variable crowd estimates to lay consumers.
+--
+
 `r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  

### 2021-10-28 index.Rmd
added speaker notes for PSA talk today

@@
 ]
+
+???
+
+Hi, thank you for being here. Today  I'll present some recent findings on crowdsourcing data analysis that I've been working on in collaboration with my co-author Professor Benoit Monin.
+
 ---
@@
 `r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~$ [**Crowdsourcing Science**](#crowdscience)
+
+???
+
+Then, I'll define crowd science and crowdsourced data analysis and introduce our question of interest, which is "does crowdsourcing data analysis improve lay perceptions of scientific findings?".
 --
@@
 `r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~$ [**Results**](#results)
+
+???
+
+Afterwards we'll briefly talk about the methods and results of an experiment, and hopefully we'll have some time at the end for some discussion.
+
 --
@@
 `r icon_style(icons::fontawesome("comment"), scale = 2, fill = "#035AA6")` $~~~$ [**Discussion**](#discussion)
+
+???
+
+If you have any questions, thoughts, comments, please feel free to raise your hand or unmute yourself and jump in.
+We have quite some time today for this session, so I'd be happy to make this as interactive as you'd like it to be.
 
@@
 
+???
+
+???
+
+In terms of the materials, these are all available online, including a preregistration, the survey, data and code, and a fully reproducible manuscript.
+You can find all these materials on the OSF and on Github, and you can also find these slides online if you want to have them in front of you at bit.ly/many-analysts.
+
 ---
@@
 
+???
+
+You may have already heard of crowdfunding, which uses the crowd for funding, but you can also use a crowd of individuals for generating research ideas, designing studies, collecting data, and analyzing data, which is what I'll be talking about today.
 --
@@
 ]
+
+???
+
+Involves giving different teams of scientists the same dataset, who independently analyze it to answer the same research question or estimate and report on a parameter of interest.
 
@@
 
-3 papers published in 2021, one looking at variability in the analysis of replications, another one at opinions about different social policies, and one OBHDP looking at the effects of scientists’ gender and professional status on verbosity during group meetings.
-Two papers in 2020, one looking at variability in the analysis of fmri (neuroimaging datasets), another in applied microeconomics.
-One paper from 2019 that evaluated the extent to which clinical psychologists analyzing the same experience sampling data come to different conclusions about symptoms to target for treatment.
-And one really famous study in 2018, that looked at discrimination against darker skin toned soccer players, and arguably started the recent crowd science movement in behavioral science.
+I'm including an interactive table with 7 papers that have recently been published in the social and behavioral science that use the many-analyst approach.
+They include interesting topics such as variability in replications, opinions about different social policies, the effects of the gender and professional status of scientists on their verbosity during group meetings, variability in the analysis of fmri (so neuroimaging datasets), and we can scroll back all the way to 2018, to a quite well-known study that looked at discrimination against darker skin toned soccer players, and arguably started the recent crowd science movement in behavioral science.
 
@@
 
-What is the rationale of crowdsourced data analysis - why should we be convinced by its findings?
+What is the rationale of crowdsourced data analysis - why should we be convinced by its findings? The phenomenon that underlies crowd science in general is known as the wisdom of the crowd.
 
@@
 
-The true weight, and the mean of all guesses was 1197 pounds.
+???
+
+Perhaps the first documented case of the wisdom of the crowd was back in 1906, when... 1197 pounds, cattle experts, individual best guesser who took home the grand prize that day.
+
 This may seem unsurprising now, but it wasn't back then.
@@
 
-I'll mention some benefits, most of which are intimately related with each other, some of them will overlap.
+I'll mention some benefits, some of which will overlap, and most of them are intimately related with each other.
 
@@
 
-Promote inclusivity, include researchers from underrepresented institutions. This comes with all the benefits of diversity. 
-Allows us to leverage under-used resources and skills.
-We can't all be an expert on everything.
-If we recruit a diverse sample of data analysts, some may have expertise on a certain statistical method that is most appropriate for the data at hand, whereas others do not
+First, crowdsourced data analysis can help to diversify contributions to research.
+I will say that this benefit is not specific to crowdsourcing data analysis, but a property of crowd science and big team science in general.
+A goal of crowd science and big team science is to promote inclusivity and include researchers from underrepresented institutions.
+This comes with all the benefits of diversity.
+It allows us to leverage under-used resources and skills.
+We of course can't all be an expert on everything.
+If we recruit a diverse sample of data analysts, some may have expertise, for example, on a certain statistical method that is most appropriate for the data at hand, or they'll have some other expertise that may benefit the data analysis.
 
@@
 
-Helps to acknowledge that results are very variable, and depend on idiosyncratic choices we have to make among multiple valid approaches, sometimes even choices we make unconsciously, such as the version of statistical software we rely on or the different defaults in for instance SPSS and R: the many-analyst approach does not *create* variability in results, it simply *exposes* it.
-that should give us pause and epistemic humility when we assess conventional scientific research: the particular outcome you're looking at is one from a distribution of outcomes that could have been possible, if the analyst had made different choices
+Second, the many-analyst approach helps to acknowledge that results in social science tend to be very variable, and can depend on idiosyncratic choices we have to make among multiple valid approaches, sometimes even choices we make unconsciously, such as the version of statistical software we rely on or the different defaults in for instance SPSS and R: it is important to note that the many-analyst approach does not *create* this variability in results, it simply *exposes* it.
+that should give us pause and epistemic humility when we assess conventional scientific research, which is often done by a single analyst or a single team: the particular outcome you're looking at is one from a distribution of outcomes that could have been possible, if the analyst had made different choices.
 
@@
 
-Can we explain the strength of the evidence obtained by the individual decisions researchers make?
-Does the choice to include or exclude a certain control variable, to run a certain statistical model, to exclude or include certain participants, impact the results?
-Do people who obtain positive findings use more controls or exclude more participants?
-Do people who obtain negative findings use more complex statistical models?
-
-Shows us *the garden of forking paths*
+Third, we can assess the impact of individual analytic choices on the results.
+Here, we can ask if we can explain the strength of the evidence obtained by the specific individual decisions that researchers make.
+For instance, we can asses the impact of including or excluding certain control variables, the impact of running a certain statistical model such as a t-test or a mixed effects model, or the impact of excluding or including certain participants or outliers.
+We could ask, for example, if people who obtain stronger evidence are more likely to do one or the other, and vice versa.
+
 --
@@
 
-To what extent does a finding hold across many different analytic specifications? Do the results come it consistently positive, or consistently negative, across different independent analyses?
+Fourth, the many-analyst approach can help us assess the overall analytic robustness of a finding.
+We can assess to what extent a finding holds across many different analytic specification.
+We can ask: do the results come out consistently positive, or consistently negative, across different independent analyses?
 --
@@
 
-● Converging conclusions increase confidence in the analytical robustness of a finding
-● Diverging conclusions decrease confidence in the analytical robustness of a finding and prompt an examination of the reasons for the divergence"
+And when we do find that the result come out consistently positive or negative, then this can increase our confidence in the specific conclusion we're drawing.
 
@@
 
+???
+
+And going back to the wisdom of the crowd phenomenon that we discussed, another benefit is that we can average across all these idiosyncratic analytic choices to obtain more accurate parameter estimates and to balance out individual biases and errors in the aggregate
 --
@@
 
+???
+
+Now I'd like to move on to talking about lay perceptions.
+One of the reasons crowdsourced data analysis was proposed, was to increase the credibility of scientific research.
+Now, we know there's quite a great deal of science skepticism in some public circles, so we want scientific research to become more credible not just to ourselves as academics, but to lay people as well.
 ---
@@
 
-Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions – compared to a single research team that comes to a single, joint conclusion – to be more swayed by the findings, as it seems to reflect consensus between various approaches.
-After all, it’s a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence, and to provide a “sensitivity analysis” or “robustness checks” to examine whether and how the findings change as a result of alternative analytic specifications.
-As argued in Aczel et al., “The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher’s idiosyncratic choice (…) when reasonable alternatives exist.” The same argument has been made for triangulation, which, according to Jick, “allows researchers to be more confident of their results.”
-We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
-Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
-Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
-However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
+I'm including here another table with three quotes.
+The first one is from a preregistration, in which the authors justify their use of the many-analyst approach by referring to the public needing to have faith in the conclusions of scientists.
+The second one is from a commentary on the many-analyst approach, in which the author provides the hopeful view that crowdsourcing provides a new way to increase credibility for social research, not just among researchers themselves, but in sample populations as well; and that it's hoped that the many-analyst approach will increase public views of social science.
+The third one is from a preprint relying on the many-analyst approach, in which the authors argue that many-analyst studies that generate consistent results across independent analysis should offer consumers of scientific findings assurance that they are not arbitrary flukes.
 
@@
 
-Lofty statements and worthy goals - empirical claim, but no evidence yet. that's what we'll be looking at today.
+Now, these quotes describe a worthy goal: improving the credibility of scientific findings through crowdsourcing data analysis.
+However, this is also an empirical claim, and as far as we know there is no evidence yet that crowdsourcing data analysis can indeed achieve this goal.
+So that's what we'll be looking at today: does crowdsourcing data analysis improve lay perceptions of scientific findings?
 ---
@@
 
-Three scenarios
+Three scenarios.
+The first condition is a conventional, single-analyst condition where a single team of six scientists analyzes the same dataset and reports a single, aggregrate parameter estimate of 5% for the relationship between two variables that I'll introduce shortly.
 
@@
 
+???
+
+We contrast this condition with two multi-analyst conditions.
+In the multi-consistent conditon, six independent teams of scientists report six independent estimates that show low variance and high consensus: they all agree in their conclusion, and the spread in their effect size estimate is small.
 --
@@
 `r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~~$ **Multi-consistent** $~~~~~~~$ *multiple parameter estimates* with *low variance* and *high consensus*
+
+???
+
+In the multi-consistent condition, six independent teams of scientists report six independent estimates that show high variance and low consensus.
+There is a large spread between the estimates, and the qualitative conclusions differ: two of the scientists find a negative relationship, and four of the scientists find a positive relationship.
 
@@
 
+???
+
+In terms of the experimental design, participants are first introduced to a research question - do religious people report higher well-being - and then report their prior beliefs about this research question.
+They are then allocated to one of the three conditions, and afterwards report the outcomes that I just described.
+---
+
+.center[
+
+# Hypotheses
+
+]
+
+### **Social norms theory**
+Observing consensus among a crowd increases **conformity** in opinion
+
+???
+
+We based our hypotheses on three lines of thought.
+First, in line with social norms theory, we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
+
+--
+
+### **Intuitive statistics **
+Observers intuitively accord to the logic of **the wisdom of crowds**:  
+The ability of an aggregate of estimates to reduce noise stemming from individual bias or error
+
+???
+
+We based our hypotheses on three lines of thought.
+First, in line with social norms theory, we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
+
+Second, Drawing from work on intuitive statistics, we also expect laypeople to intuitively accord to the logic of "the wisdom of crowds": the ability of an aggregate of estimates (rather than a single estimate) to reduce noise stemming from individual bias or error.
+
+In contrast, when crowd estimates show low consensus and high variance (the inconsistent crowd condition), we predict that observers will be less swayed and more likely to attribute the findings to bias and error.
+
+--
+
+### **Aversion to variability**
+Observing **variable estimates** decreases confidence in the overall estimate
+
+???
+
+We based our hypotheses on three lines of thought.
+First, in line with social norms theory, we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
+
+Second, Drawing from work on intuitive statistics, we also expect laypeople to intuitively accord to the logic of "the wisdom of crowds": the ability of an aggregate of estimates (rather than a single estimate) to reduce noise stemming from individual bias or error.
+
+In contrast, when crowd estimates show low consensus and high variance (the inconsistent crowd condition), we predict that observers will be less swayed and more likely to attribute the findings to bias and error.
+
+Third, due to the difficulty of lay reasoning about variation, we predict an aversion to variability: i.e., we expect that observing variable estimates will decrease lay confidence in the precise average parameter estimate in both crowd conditions.
+This is based on the idea that it may be completely foreign to lay consumers that analyzing the dataset can lead to different estimates in the first place.
+If we report one estimate, this is taken to be the "one true" estimate -- if we report several variable estimates, the consumer in question may no longer be so certain that any of the estimates, or the overall average estimate, is precisely correct.
+
+In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- higher posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower ratings of bias and error.
+When laypeople observe multiple inconsistent estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- lower posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and greater ratings of bias and error.
+
 ---
@@
 
-Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions – compared to a single research team that comes to a single, joint conclusion – to be more swayed by the findings, as it seems to reflect consensus between various approaches.
-After all, it’s a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence, and to provide a “sensitivity analysis” or “robustness checks” to examine whether and how the findings change as a result of alternative analytic specifications.
-As argued in Aczel et al., “The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher’s idiosyncratic choice (…) when reasonable alternatives exist.” The same argument has been made for triangulation, which, according to Jick, “allows researchers to be more confident of their results.”
-We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
-Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
-Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
-However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
+???
+
+We based our hypotheses on three lines of thought.
+First, in line with social norms theory, we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
+
+Second, Drawing from work on intuitive statistics, we also expect laypeople to intuitively accord to the logic of "the wisdom of crowds": the ability of an aggregate of estimates (rather than a single estimate) to reduce noise stemming from individual bias or error.
+
+In contrast, when crowd estimates show low consensus and high variance (the inconsistent crowd condition), we predict that observers will be less swayed and more likely to attribute the findings to bias and error.
+
+Third, due to the difficulty of lay reasoning about variation, we predict an aversion to variability: i.e., we expect that observing variable estimates will decrease lay confidence in the precise average parameter estimate in both crowd conditions.
+In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- higher posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower ratings of bias and error.
+When laypeople observe multiple inconsistent estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- lower posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and greater ratings of bias and error.
 
@@
 
-???
-
-Participants had to wait 30 seconds before proceeding to the next slide. 
 ---
@@
 
-Importantly, in both the single-analyst and the multi-analyst conditions we emphasize that there are a lot of choices to be made.
+Participants are first introduced to the research question and research approach.
+In the single-analyst condition, a single team of six researchers analyzes the same dataset, and in the two multi-analyst conditions, six independent researchers analyze the same dataset.
+Importantly, in all conditions we emphasize in the last paragraph that there are a lot of choices to be made.
+Participants had to wait 30 seconds before proceeding to the next slide.
 
@@
 
+???
+
+Here are the results we show participants.
+In the single-analyst condition, the team of six researchers concludes that religious people do indeed report higher well-being, and they find a 5% increase in well-being for every one point increase in religiosity.
+In the multi-consistent condition, the six independent researchers show consensus in that they all report a positive relationship, and the spread in their estimates is quite small; they range from 2% to 8%.
+In the multi-inconsistent condition, the six independent researchers do not show consensus, in that two of the scientists conclude that the relationship is negative, and four of the scientists conclude that the relationship is positive, and we can see that the spread in their estimates is quite large, ranging from -6% to 16%.
+
 ---
@@
 ???
-
-Our main findings are displayed in Figure 1.
-Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, b=-5.71, and the multi-inconsistent condition, b=-22.80; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, b=-6.54, while they were not significantly different in the multi-consistent condition, b=1.24 (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, b=-9.09, while it was not significantly different in the multi-consistent condition, b=0.49; (4) ratings of bias were significantly greater in the multi-inconsistent condition, b=6.68, while they were not significantly different in the multi-consistent condition, b=2.13; and (5) ratings of error were significantly greater in both the multi-consistent condition, b=3.59, and the multi-inconsistent condition, b=5.89.
-For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, b=5.14, and the multi-inconsistent condition, b=9.22.
+For the results, we regressed all outcomes on prior beliefs and condition, with the single-analyst condition as the reference category.
+So all results that I will show you control for prior beliefs and show the results for the two multi-analyst conditions compared to the single-analyst condition.
+I will now walk you through each individual aspect of this Figure.
 
@@
 
-In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
+???
+
+In line with out hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results have lower posterior beliefs (you can see this estimate here), find the results less credible, have less confidence in the aggregate estimate of 5%, and believe this estimate is more likely to stem from bias, error, and discretion (which we define as idiosyncratic choices among multiple valid approaches, or what we researchers often refer to as researcher degrees of freedom).
+
 ---
@@
 
-In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
+Contrary to our hypotheses, we find that lay consumers of multi-analyst studies with consistent results also have lower beliefs and believe the 5% estimate is more likely to stem from error or from idiosyncratic choices.
+We found no significant effects on the credibility of the results, confidence in the aggregate parameter estimate of 5%,  and the perceived impact of bias on the estimate.
 
@@
 ???
+
+We conclude that, compared to a single estimate, we do not find evidence that crowd estimates improve lay perceptions of scientific findings.
+In the future, we are curious to explore whether it might be aversion to variability that explains these findings, and what the perceptions of scientists are.
+We also believe that in the future it is important for crowd scientists to consider how -- for example, by drawing from research on science communication -- to tackle science skepticism and effectively communicate variable crowd estimates to lay consumers.
 
@@
 To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error or idiosyncratic choices.
-Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.
 --

### 2021-11-02 manuscript/manuscript.Rmd
last changes prior to submission GSPA + ORA
edits to manuscript based on SPSP submissions: rewrote discussion, rewording of title/conditions

@@
 ---
-title             : "Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus"
-shorttitle        : "Lay Perceptions of Multi-Analyst Studies"
+title             : "Lay Perceptions of Scientific Findings: Swayed by the Crowd?"
+shorttitle        : "The Sway of Crowd Science"
 
@@
 a typical research collaboration) on lay consumers' posterior beliefs and ratings of credibility, confidence in an aggregate effect size estimate, bias, and error.
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to answer a research question and/or estimate a parameter of interest.
-We compare the effects of providing a single, aggregate parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
+We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to estimate and report a parameter of interest.
+We compare the effects of providing a single, aggregate parameter estimate (the single estimate condition) vs.
+multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the consistent crowd condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the inconsistent crowd condition).
 In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "3,692"
+wordcount         : "2,222"
 
@@
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
--->
-<!-- According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
-In the preregistration of an ongoing many-analysts study, Arbon et al.
-[-@arbon2019] justify their use of the novel approach by referring to the need for "the public to have faith in the conclusions of scientists".
-In a preprint of a conducted multi-analyst study, Breznau et al.
-[-@breznau2021, p.
+According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
+In the preregistration of an ongoing many-analysts study, Arbon and colleagues [-@arbon2019] justify their use of the novel approach by referring to the need for "the public to have faith in the conclusions of scientists".
+In a preprint of a conducted multi-analyst study, Breznau and colleagues [-@breznau2021, p.
 3] argue that independent data analyses with converging findings should offer "consumers of scientific findings assurance that they are not arbitrary flukes".
@@
 311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
--->
-<!-- We explore the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing lay consumers with a single parameter estimate (the single-analyst condition) vs.
-multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
--->
-<!-- In line with social norm theory [@miller2016], we expect an individual who observes a crowd of scientists reach the same qualitative conclusion to be more likely to conform in opinion, and be swayed by the scientific findings, than an individual who observes the conclusion of a single scientist.
-Although observing several differing estimates (rather than a single estimate) may decrease lay confidence in the precise average estimate, it should increase beliefs about the reported phenomenon and decrease perceptions of bias and error.
-However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when the results generated by independent analyses vary widely and lack consensus in their qualitative conclusions, we expect a decrease in the sway of scientific findings.
--->
-<!-- In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, and lower (greater) ratings of bias and error.
-In addition, we expect that observing differing estimates decreases confidence in the precise average parameter estimate in both multi-estimate conditions.
--->
-
-The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
-Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
-528).
-One such tool is the crowd science approach, which leverages a large number of individuals or teams at specific stages of the research process [@uhlmann2019].
-Crowd science is defined as "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p.
-1].
-Crowd-scientific projects vary in their degree of selectivity: some are open to the general public (such projects are often referred to as "citizen science"), while others require the expertise of specialists [e.g., scientists\; @uhlmann2019, p.
-714].
-Here, we focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.
 We explore the effects of scientific findings emerging from a crowd of researchers (vs.
 a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single-analyst condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).
-According to previous work, crowdsourced data analysis should increase the credibility of scientific findings; Table 1 provides an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
-Does crowd science meet its promise -- to improve the credibility of scientific research -- in reality?
-Normatively, we expect laypeople who observe several scientists independently come to the same qualitative conclusions -- compared to a single research team that comes to a single, joint conclusion -- to be more swayed by the findings, as it seems to reflect consensus between various approaches.
-After all, it's a hallmark of rigorous research to triangulate various methodological approaches and provide converging evidence [@jick1979; @turner2017], and to provide a "sensitivity analysis" or "robustness checks" to examine whether and how the findings change as a result of alternative analytic specifications [@munoz2018; @steegen2016].
-As argued in Aczel et al.
-[-@aczel2020, p.
-562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results: ideally, results should be reasonably unaffected by a researcher's idiosyncratic choice (…) when reasonable alternatives exist." The same argument has been made for triangulation, which, according to Jick [-@jick1979, p.
-608], "allows researchers to be more confident of their results."
-We similarly expect readers of multi-analyst reports that yield consistent findings to be more confident in the results.
-Although lay observers, in such cases, may be less certain that the precise aggregate parameter estimate is exactly correct, they should be more likely to positively update their beliefs about the reported phenomenon, and less likely to assume that the overall estimate stems from bias or error.
-Thus, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
+We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single estimate condition) vs.
+multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the consistent crowd condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the inconsistent crowd condition).
+In line with social norms theory [@miller2016], we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
+Drawing from work on intuitive statistics [@gigerenzer2015a], we also expect laypeople to intuitively accord to the logic of "the wisdom of crowds": the ability of an aggregate of estimates (rather than a single estimate) to reduce noise stemming from individual bias or error [@schweinsberg2021].
+In contrast, when crowd estimates show low consensus and high variance (the inconsistent crowd condition), we predict that observers will be less swayed and more likely to attribute the findings to bias and error.
+In addition, due to the difficulty of lay reasoning about variation [@garfield2004], we predict an aversion to variability: i.e., we expect that observing variable estimates will decrease lay confidence in the precise average parameter estimate in both crowd conditions.
+In sum, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
 However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
 **[Insert Table 1 here]**  
-Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 2: we hypothesized that in the multi-consistent condition (compared to the single-analyst condition), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
-For the multi-inconsistent condition, we hypothesized that lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
-In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both multi-analyst conditions.
-**[Insert Table 2 here]**
-
-<!-- "Following the logic of the wisdom of the crowds, in which aggregating estimates reduces individual level biases (Galton, 1907; Lorge, Fox, Davitz, & Brenner, 1958; Surowiecki, 2004), the central tendency of the effect size estimates calculated by many different analysts may provide a less subjective and error-prone estimate of the effect."  (Schweinsberg et al., 2021: p.
-246-7) -->
+Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 1: we hypothesized that in the consistent crowd condition (compared to the single estimate condition, and controlling for prior beliefs), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
+For the inconsistent crowd condition, we hypothesized that (compared to the single estimate condition, and controlling for prior beliefs) lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
+In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both crowd conditions.
+In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- higher (lower) posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower (greater) ratings of bias and error.
 
@@
 After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a scientific study.
-In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% (SD = 2); and in the multi-inconsistent condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% (SD = 8.25).
+In the single estimate condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the consistent crowd condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% ($\sigma$ = 2%); and in the inconsistent crowd condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% ($\sigma$ = 8.25%).
 Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) researcher degrees of freedom.
@@
 ## Data analysis
-For all six measures, we run linear regression models with condition as the independent variable (with the single-analyst condition as the reference category) and prior beliefs as a covariate.
+For all six measures, we run linear regression models with condition as the independent variable (with the single estimate condition as the reference category) and prior beliefs as a covariate.
 All hypotheses, statistical models, and code were preregistered at https://osf.io/rpu98.
-An overview of our preregistered, directional hypotheses can be found in Table 2.
+An overview of our preregistered, directional hypotheses can be found in Table 1.
 We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of researcher degrees of freedom are exploratory, and should be treated as such.
-Because we test five separate hypotheses using two comparisons each (one comparison of the single-analyst vs.
-the multi-consistent condition, and one comparison of the single-analyst vs.
-the multi-inconsistent condition), we use the Bonferroni method to correct for multiple comparisons.
+Because we test five separate hypotheses using two comparisons each (one comparison of the single estimate vs.
+the consistent crowd condition, and one comparison of the single estimate vs.
+the inconsistent crowd condition), we use the Bonferroni method to correct for multiple comparisons.
 Thus, our preregistered threshold for statistical significance is $\displaystyle \alpha = \frac{.05}{2} = .025$.
@@
 ```{r data-cleaning, include = FALSE}
-df <- read.csv(here("data/data.csv"))
-df <- df[3:nrow(df),]
-n_recorded <- nrow(df)
+df <- read.csv(here("data/data.csv")) #read data
+df <- df[3:nrow(df),] #take out header rows
+n_recorded <- nrow(df) #save number of recorded responses
 
@@
 We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check.
-This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).
-Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs.
-For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Credibility, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
-For the multi-consistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher (b) ratings of error, `r results(Error)`; and (c) discretion, `r results(Discretion)`, and no significant effects on (d) ratings of credibility, `r results(Credibility)`, (e) confidence in the effect size estimate, `r results(Confidence)`, or (f) ratings of bias, `r results(Bias)`.
+This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single estimate, consistent crowd, and inconsistent crowd condition, respectively).
+Figure 1 displays the main findings of our linear regression models, which compare each condition to the single estimate condition and control for prior beliefs.
+For the inconsistent crowd condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Credibility, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher ratings of (d) bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
+For the consistent crowd condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher ratings of (b) error, `r results(Error)`; and (c) discretion, `r results(Discretion)`; and no significant effects on (d) ratings of credibility, `r results(Credibility)`; (e) confidence in the effect size estimate, `r results(Confidence)`; or (f) ratings of bias, `r results(Bias)`.
 **[Insert Figure 1 here]**  
@@
 **[Insert Figure 2 here]**  
-It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa`.
-This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.
+It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a positive difference between prior and posterior beliefs within the consistent crowd condition: i.e., beliefs in the research hypothesis are greater after consuming consistent crowd estimates, `r t_apa`.
+This finding clarifies that a consistent crowd may sway observers --- however, compared to a conventional, non-crowdsourced estimate, crowd estimates do not seem to improve lay perceptions of scientific findings.
 
@@
 
+Every day, important scientific findings are rejected at large.
+From man-made climate change to the safety and efficacy of Covid-19 vaccinations, science skepticism has run rampant among lay consumers in modern society [@hornsey2017].
+To increase public faith in science, some have proposed the use of crowd science [@silberzahn2018; @uhlmann2019].
+In Table 2, we provide an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
+The logic behind the crowd science approach accords with that of analytic practices that are considered to be hallmarks of rigorous research: e.g., to triangulate various methodological approaches and provide converging evidence [@jick1979; @turner2017], and to provide a "sensitivity analysis" or "robustness checks" to examine whether and how the findings change as a result of alternative analytic specifications [@munoz2018; @steegen2016].
+As argued in Aczel et al.
+[-@aczel2020, p.
+562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results." The same argument has been made for triangulation, which, according to Jick [-@jick1979, p.
+608], "allows researchers to be more confident of their results." Drawing from theories on social norms and numerical cognition, we similarly expected lay consumers of multi-analyst studies with consistent findings to be more confident in the results.
+**[Insert Table 2 here]**  
 From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-The multi-analyst approach has many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates.
 However, as with any real-world intervention, scientific reform can have unintended consequences.
 Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
-To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
+While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
+To our surprise, even when results generated by independent analysts are highly consistent and lead to the same qualitative conclusion, we find no improvement in lay perceptions of scientific findings.
+Instead, consumers of consistent, slightly variable, crowd estimates are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
+In the future, it is important for crowd scientists to consider how to tackle science skepticism and effectively communicate variable estimates.
 
@@
 ## Table 1
+*Predicted direction of effects compared to the single estimate condition*
+
+| Measure | Consistent crowd | Inconsistent crowd |
+| ------------- |  ------------- | ------------- | 
+| 1.
+Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+|2.
+Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+| 3.
+Confidence in precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
+| 4.
+Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 5.
+Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
+*Note*.
+Table 1 indicates the predicted direction of the effect for all dependent variables, compared to the single estimate condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction).
+For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the consistent crowd condition and lower in the inconsistent crowd condition.
+
+\newpage
+
+## Table 2
 ## *Proposed credibility- and confidence-related benefits of crowdsourced data analysis*
@@
 
-## Table 2
-*Predicted direction of effects compared to the single-analyst condition*
-
-| Measure | Multi-consistent | Multi-inconsistent |
-| ------------- |  ------------- | ------------- | 
-| 1.
-Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-|2.
-Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 3.
-Confidence in precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 4.
-Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 5.
-Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
-*Note*.
-Table 2 indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction).
-For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the multi-consistent condition and lower in the multi-inconsistent condition.
-
-\newpage
-
 # Figures
@@
 ## Figure 1
-*Estimates relative to the single-analyst condition*
+*Estimates of differences with the single estimate condition*
 \noindent
@@
 p1b <- p1 + 
-  ggtitle("Differences from the single-analyst condition") +
+  ggtitle("Differences from the single estimate condition") +
   theme(plot.title = element_text(hjust = 0.5))
@@
 
-knitr::include_graphics("Figure1.jpg", dpi = 1200)
+p1c <- p1 + 
+  scale_x_discrete(labels = c("Consistent\ncrowd", "Inconsistent\ncrowd"))
+
+ggsave(here("poster/Figure1c.jpg"), p1c, 
+       width = 7, height = 5, units = "in") #save to poster folder
+
+knitr::include_graphics(here("poster/Figure1c.jpg"), dpi = 1200)
 ```
@@
 
-*Individual data points, quartiles, and distributions of prior and posterior beliefs in the single-analyst, multi-consistent, and multi-inconsistent conditions*  
+*Individual data points, quartiles, and distributions of prior and posterior beliefs in the single estimate, consistent crowd, and inconsistent crowd conditions*  
 \noindent
@@
            label = label_c3,
-           x = 1.78, y = 16, size = 6,
+           x = 1.78, y = 15, size = 6,
            family = "serif") + 
@@
 
-knitr::include_graphics("Figure2.jpg", dpi = 1200)
+knitr::include_graphics(here("poster/Figure2b.jpg"), dpi = 1200)
 ```

### 2021-11-02 manuscript/manuscript.Rmd
caught mistake in reported post-hoc t-test

@@
 
-get_d <- function(Predictor, Multi_Condition = "Consistent") {
-  linear_mod <- lm(
-    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
-
-  apa_results <- apa_print(linear_mod)
-
-  ifelse(Multi_Condition == "Consistent",
-         parse_number(apa_results$table$statistic[2])/sqrt(499),
-         parse_number(apa_results$table$statistic[3])/sqrt(500)) 
-}
-
 # Post-hoc t-test
@@
 
-t_test <- apa_print(t.test(df_multiconsistent$Final_beliefs,
+t_test <- apa_print(
+  t.test(
+    df_multiconsistent$Final_beliefs,
     df_multiconsistent$Prior_beliefs, 
-                           paired = TRUE))
-
-cohens_d <- parse_number(gsub(".*=", "", t_test$statistic)) / sqrt(499)
-
-t_apa <- paste(t_test$estimate, 
-               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
-               sep = ", ")
-
-# Post-hoc t-test
-df_multi_inconsistent <- df %>% 
-  filter(Condition == "Multi-inconsistent")
-
-t_test <- apa_print(t.test(df_multi_inconsistent$Final_beliefs,
-                           df_multi_inconsistent$Prior_beliefs, 
-                           paired = TRUE))
-
-t_apa <- paste(t_test$estimate, 
-               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
-               sep = ", ")
-
-# Post-hoc t-test
-df_single <- df %>% 
-  filter(Condition == "Single")
-
-t_test <- apa_print(t.test(df_single$Final_beliefs,
-                           df_single$Prior_beliefs, 
     paired = TRUE))
@@
 In the future, it is important for crowd scientists to consider how to tackle science skepticism and effectively communicate variable estimates.
+
+\newpage
 

### 2021-11-09 manuscript/manuscript.Rmd
added abstract for SPSP JDM preconference

@@
 We run an experiment to study the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs and ratings of credibility, confidence in an aggregate effect size estimate, bias, and error.
+a typical research collaboration) on lay consumers' posterior beliefs, confidence in an aggregate effect size estimate, and ratings of credibility, bias, and error.
 We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to estimate and report a parameter of interest.
@@
 
+p1d <- p1c + 
+  ggtitle("Differences from the single estimate condition") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggsave(here("poster/Figure1d.jpg"), p1d, 
+       width = 7, height = 5, units = "in") #save to poster folder
+
 knitr::include_graphics(here("poster/Figure1c.jpg"), dpi = 1200)
 ```
-*Note.* Figure 1 displays coefficient estimates (and 95% confidence intervals) of posterior beliefs, credibility, confidence, bias, error, and discretion in the two multi-analyst conditions, compared to the single-analyst condition (and controlling for prior beliefs).
+*Note.* We regressed all outcomes on prior beliefs and condition (with the single estimate condition as the reference category).
+Figure 1 displays coefficient estimates (and 95% confidence intervals) of posterior beliefs, credibility, confidence, bias, error, and discretion in the two crowd conditions – the consistent crowd and the inconsistent crowd – compared to the single-analyst condition and controlling for prior beliefs.
 Green/red/gray error bars indicate positive/negative/insignificant findings, respectively.

### 2021-11-09 poster/SPSP_Abstract.Rmd
added abstract for SPSP JDM preconference

--- 2021-11-09 manuscript/manuscript.Rmd
@@
 abstract: |
-  A recent movement towards crowd science has emerged in the behavioral sciences.
-One of the aims of crowd science is to increase the credibility of scientific research.
-Does it meet this promise in reality?
-We run an experiment to study the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs, confidence in an aggregate effect size estimate, and ratings of credibility, bias, and error.
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: giving the same dataset to different teams of scientists, who independently analyze the data to estimate and report a parameter of interest.
-We compare the effects of providing a single, aggregate parameter estimate (the single estimate condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the consistent crowd condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the inconsistent crowd condition).
-In line with our hypotheses, we find that lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that multi-analyst studies with consistent results (compared to single-analyst studies) increase the sway and credibility of scientific findings to lay consumers: instead, to our surprise, they lead to lower posterior beliefs and higher ratings of error.
+  Every day, important scientific findings are rejected at large.
+To increase public faith in science, some have proposed the use of crowd science.
+Drawing from theories on social norms and numerical cognition, we test whether crowd science improves lay perceptions of scientific findings.
+We run an experiment (N = 2,019; preregistration, data, code, and materials at [osf.io/vedb4](osf.io/vedb4)) to study the effects of scientific findings emerging from a crowd of researchers (vs.
+a typical research collaboration) on lay consumers’ posterior beliefs, confidence in an aggregate effect size estimate, and ratings of credibility, bias, and error.
+We focus on crowdsourced data analysis: a crowd of scientists who independently analyze the same data to estimate and report a parameter of interest.
+Contrary to our hypotheses, we do not find that consistent crowd estimates increase the sway and credibility of scientific findings to lay consumers: instead, to our surprise, they lead to lower posterior beliefs and higher ratings of error.
+In the future, it is important for crowd scientists to consider how to tackle science skepticism and effectively communicate variable crowd estimates to lay consumers.
 
-keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "2,222"
+keywords          : "Crowd science, Variability aversion, Science skepticism"
+wordcount         : "181"
 
@@
 
-The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike.
-Several tools have been proposed to combat this "crisis of confidence" (Ibid., p.
-528).
-One such tool is the crowd science approach: "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p.
-1].
-We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.
-According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers.
-In the preregistration of an ongoing many-analysts study, Arbon and colleagues [-@arbon2019] justify their use of the novel approach by referring to the need for "the public to have faith in the conclusions of scientists".
-In a preprint of a conducted multi-analyst study, Breznau and colleagues [-@breznau2021, p.
-3] argue that independent data analyses with converging findings should offer "consumers of scientific findings assurance that they are not arbitrary flukes".
-In a commentary on the many analysts approach, Breznau [-@breznau2021a, p.
-311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
-We explore the effects of scientific findings emerging from a crowd of researchers (vs.
-a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error.
-We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the single estimate condition) vs.
-multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the consistent crowd condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the inconsistent crowd condition).
-In line with social norms theory [@miller2016], we expect that observing consensus among a crowd (the consistent crowd condition) will -- compared to the conclusion of a single scientist (the single estimate condition) -- increase conformity in opinion.
-Drawing from work on intuitive statistics [@gigerenzer2015a], we also expect laypeople to intuitively accord to the logic of "the wisdom of crowds": the ability of an aggregate of estimates (rather than a single estimate) to reduce noise stemming from individual bias or error [@schweinsberg2021].
-In contrast, when crowd estimates show low consensus and high variance (the inconsistent crowd condition), we predict that observers will be less swayed and more likely to attribute the findings to bias and error.
-In addition, due to the difficulty of lay reasoning about variation [@garfield2004], we predict an aversion to variability: i.e., we expect that observing variable estimates will decrease lay confidence in the precise average parameter estimate in both crowd conditions.
-In sum, when the results generated by independent analysts are largely consistent, we expect an increase in the sway of scientific findings.
-However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when results across many analysts vary widely and lack consensus in their qualitative conclusions (which, arguably, often reflects the reality of large-scale science collaborations), we expect a decrease in the sway of scientific findings.
-**[Insert Table 1 here]**  
-Our pre-registered hypotheses (https://osf.io/rpu98) can be found in Table 1: we hypothesized that in the consistent crowd condition (compared to the single estimate condition, and controlling for prior beliefs), lay consumers would have higher posterior beliefs, would find the results more credible, and would be less likely to believe the results stem from bias or error.
-For the inconsistent crowd condition, we hypothesized that (compared to the single estimate condition, and controlling for prior beliefs) lay consumers would have lower posterior beliefs, would find the results less credible, and would be more likely to believe the results stem from bias or error.
-In addition, we expected that the act of providing multiple (slightly to widely varying) parameter estimates would decrease confidence in the aggregate parameter estimate in both crowd conditions.
-In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single estimate and controlling for prior beliefs -- higher (lower) posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower (greater) ratings of bias and error.
-
-# Methods
-The preregistration of our experiment can be found in the Open Science Foundation (OSF) Registries at https://osf.io/rpu98.
-All data and code needed to reproduce this article can be found on GitHub at https://github.com/shilaan/many-analysts and the OSF at https://osf.io/vedb4/.
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-## Participants
-We sampled participants from the Prolific participant pool.
-We included participants from the United States or the United Kingdom who were at least 18 years old and spoke English as a first language.
-We excluded participants who failed the attention check or attempted to take the survey more than once.
-Our target sample size was 1,500 participants after exclusions.
-We aimed to keep sampling until reaching the desired number of valid participants or until 2 weeks passed (whichever came first).
-We expected relatively small effect sizes and decided on an upper limit on the number of participants based on monetary constraints.
-
-## Procedure and materials
-All survey materials can be found on the OSF at https://osf.io/md9z5/.
-After a brief introduction to a research question ("Do religious people report higher well-being?"), participants were asked to report their prior beliefs ("How likely do you think it is that people who are more religious generally report higher well-being?") on a slider from 0% (not likely at all) to 100% (extremely likely).
-After reporting their prior beliefs, participants were randomly allocated to one of three experimental conditions in which they learned about the approach and findings of a scientific study.
-In the single estimate condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the consistent crowd condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% ($\sigma$ = 2%); and in the inconsistent crowd condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% ($\sigma$ = 8.25%).
-Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) researcher degrees of freedom.
-All questions were answered on a slider from 0% (not likely/credible/confident at all) to 100% (extremely likely/credible/confident).
-
-## Data analysis
-For all six measures, we run linear regression models with condition as the independent variable (with the single estimate condition as the reference category) and prior beliefs as a covariate.
-All hypotheses, statistical models, and code were preregistered at https://osf.io/rpu98.
-An overview of our preregistered, directional hypotheses can be found in Table 1.
-We did not preregister any hypotheses for the last measure; the findings concerning the impact of experimental condition on ratings of researcher degrees of freedom are exploratory, and should be treated as such.
-Because we test five separate hypotheses using two comparisons each (one comparison of the single estimate vs.
-the consistent crowd condition, and one comparison of the single estimate vs.
-the inconsistent crowd condition), we use the Bonferroni method to correct for multiple comparisons.
-Thus, our preregistered threshold for statistical significance is $\displaystyle \alpha = \frac{.05}{2} = .025$.
-
-# Results
-
-```{r data-cleaning, include = FALSE}
-df <- read.csv(here("data/data.csv")) #read data
-df <- df[3:nrow(df),] #take out header rows
-n_recorded <- nrow(df) #save number of recorded responses
-
-df <- df %>% #take out participants who attempted to take the survey more than once
-  filter(!PROLIFIC_PID %in% df$PROLIFIC_PID[duplicated(df$PROLIFIC_PID)])
-n_more_than_once <- n_recorded - nrow(df)
-
-df <- df %>% #take out participants who were screened out or did not consent
-  filter(Consent == "I agree to participate in this research project")
-n_screened_out <- n_recorded - n_more_than_once - nrow(df)
-
-df <- df %>% #take out participants who failed or did not complete the attention check
-  filter(Condition == Attention_check & Attention_check != "") 
-n_failed_attention <- n_recorded - n_more_than_once - n_screened_out - nrow(df)
-ns_bycondition <- table(df$Condition)
-
-df <- df %>% 
-  mutate(
-    ID = 1:nrow(df),
-    Condition = factor(Condition, #set reference category
-                       levels = c("Single",           
-                                  "Multi-consistent", 
-                                  "Multi-inconsistent"))
-  ) %>% 
-  rename(
-    Prior_beliefs = Prior.beliefs_1,
-    Final_beliefs = Final.beliefs_1,
-    Credibility = Credibility_1,
-    Confidence = Confidence_1,
-    Bias = Sources.Variability_1,
-    Error = Sources.Variability_4,
-    Discretion = Sources.Variability_5
-  ) %>% 
-  select(ID, Condition, Attention_check, Prior_beliefs:Discretion)
-
-df[,4:ncol(df)] <- sapply(df[,4:ncol(df)], as.numeric) #recode variables to numeric
-
-# Function to show inline results
-results <- function(Predictor, Multi_Condition = "Consistent") {
-  linear_mod <- lm(
-    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
-
-  apa_results <- apa_print(linear_mod)
-
-  ifelse(Multi_Condition == "Consistent",
-         paste(apa_results$estimate$ConditionMulti_consistent,
-               strsplit(apa_results$statistic$ConditionMulti_consistent, ",")[[1]][2],
-               sep = ", "), #print without t-values, otherwise use apa_results$full_result
-         paste(apa_results$estimate$ConditionMulti_inconsistent,
-               strsplit(apa_results$statistic$ConditionMulti_inconsistent, ",")[[1]][2],
-               sep = ", ")
-         )
-
-}
-
-# Post-hoc t-test
-df_multiconsistent <- df %>% 
-  filter(Condition == "Multi-consistent")
-
-t_test <- apa_print(
-  t.test(
-    df_multiconsistent$Final_beliefs,
-    df_multiconsistent$Prior_beliefs, 
-    paired = TRUE))
-
-t_apa <- paste(t_test$estimate, 
-               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
-               sep = ", ")
-```
-
-After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics.
-We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check.
-This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single estimate, consistent crowd, and inconsistent crowd condition, respectively).
-Figure 1 displays the main findings of our linear regression models, which compare each condition to the single estimate condition and control for prior beliefs.
-For the inconsistent crowd condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Credibility, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher ratings of (d) bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.
-For the consistent crowd condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher ratings of (b) error, `r results(Error)`; and (c) discretion, `r results(Discretion)`; and no significant effects on (d) ratings of credibility, `r results(Credibility)`; (e) confidence in the effect size estimate, `r results(Confidence)`; or (f) ratings of bias, `r results(Bias)`.
-**[Insert Figure 1 here]**  
-In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error.
-Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).
-Figure 2 further clarifies the sway of multi-analyst vs.
-single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.
-**[Insert Figure 2 here]**  
-It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a positive difference between prior and posterior beliefs within the consistent crowd condition: i.e., beliefs in the research hypothesis are greater after consuming consistent crowd estimates, `r t_apa`.
-This finding clarifies that a consistent crowd may sway observers --- however, compared to a conventional, non-crowdsourced estimate, crowd estimates do not seem to improve lay perceptions of scientific findings.
-
-# Discussion
-
-Every day, important scientific findings are rejected at large.
-From man-made climate change to the safety and efficacy of Covid-19 vaccinations, science skepticism has run rampant among lay consumers in modern society [@hornsey2017].
-To increase public faith in science, some have proposed the use of crowd science [@silberzahn2018; @uhlmann2019].
-In Table 2, we provide an overview of the proposed confidence- and credibility-related benefits of the multi-analyst approach.
-The logic behind the crowd science approach accords with that of analytic practices that are considered to be hallmarks of rigorous research: e.g., to triangulate various methodological approaches and provide converging evidence [@jick1979; @turner2017], and to provide a "sensitivity analysis" or "robustness checks" to examine whether and how the findings change as a result of alternative analytic specifications [@munoz2018; @steegen2016].
-As argued in Aczel et al.
-[-@aczel2020, p.
-562], "The main argument for the importance of performing robustness checks over reasonable variations in modelling choices is to increase confidence in the obtained results." The same argument has been made for triangulation, which, according to Jick [-@jick1979, p.
-608], "allows researchers to be more confident of their results." Drawing from theories on social norms and numerical cognition, we similarly expected lay consumers of multi-analyst studies with consistent findings to be more confident in the results.
-**[Insert Table 2 here]**  
-From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research.
-However, as with any real-world intervention, scientific reform can have unintended consequences.
-Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
-While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research.
-To our surprise, even when results generated by independent analysts are highly consistent and lead to the same qualitative conclusion, we find no improvement in lay perceptions of scientific findings.
-Instead, consumers of consistent, slightly variable, crowd estimates are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom.
-In the future, it is important for crowd scientists to consider how to tackle science skepticism and effectively communicate variable estimates.
-
-\newpage
-
-## Acknowledgements
-We thank Nicole Clare Kolmstetter for valuable assistance in the data collection. This manuscript was created using `r cite_r("r-references.bib")`.
-
-## Disclosure statement
-There are no relevant financial or non-financial competing interests to report.
-
-## Data availability statement
-The data that support the findings of this study are openly available on GitHub at https://github.com/shilaan/many-analysts and the OSF at https://osf.io/vedb4/.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-
-# Tables
-
-## Table 1
-*Predicted direction of effects compared to the single estimate condition*
-
-| Measure | Consistent crowd | Inconsistent crowd |
-| ------------- |  ------------- | ------------- | 
-| 1.
-Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-|2.
-Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 3.
-Confidence in precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 4.
-Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 5.
-Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
-*Note*.
-Table 1 indicates the predicted direction of the effect for all dependent variables, compared to the single estimate condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction).
-For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the consistent crowd condition and lower in the inconsistent crowd condition.
-
-\newpage
-
-## Table 2
-## *Proposed credibility- and confidence-related benefits of crowdsourced data analysis*
-
-| Citation | Description of credibility- or confidence-related benefits | 
-| ------------- | ------------- | 
-| [@aczel2021, pp.
-3-4] | "When the results of independent data analyses converge, more confidence in the conclusions is warranted.
-When the results diverge, confidence appropriately falters, and scientists can examine the reasons for these discrepancies."|
-|[@arbon2019] | "For the public to have faith in the conclusions of scientists it is important that the methods they employ are robust and transparent.
-This study will examine robustness by recruiting teams of independent data analysts and looking at how they answer a controversial research question using the same data, effectively ‘crowd-sourcing’ the data analysis." |
-| [@auspurg2021, pp. 1, 10]  | "Several researchers analyze the same research question with the same data (...) Science is credible if different researchers come up with a similar answer"  | 
-| [@breznau2021, p.
-3] | "Organized scientific knowledge production (...) should generate inter-researcher reliability, offering consumers of scientific findings assurance that they are not arbitrary flukes but that other researchers would generate similar findings given the same data." |
-| [@breznau2021a, p.
-311] | "crowdsourcing provides a new way to increase credibility for political and social research---in both sample populations and among the researchers themselves (...) It is hoped that these developments are tangible outcomes that increase public, private, and government views of social science." |
-|[@silberzahn2015, pp. 190-1]|"the results are more credible (...) greater certainty comes from having an independent check."|
-|[@silberzahn2018, p.
-352]|"Scientists can have comparatively more faith in a finding when there is less variability in analytic approaches taken to investigating the targeted phenomenon and in results obtained using different methods.
-(...) In such extreme cases of little to no convergence in results, the crowdsourcing process suggests that the scientific community should have no faith that the hypothesis is true"|
-|[@uhlmann2019, p.
-713]|"crowdsourced teams can conduct high-powered, precise studies and draw confident conclusions.
-(...) Crowdsourcing research is a part of a changing landscape of science that seeks to improve research reliability and advance the credibility of academic research"|
-
-\newpage
-
-# Figures
-
 ## Figure 1
@@
 ```{r fig-1, echo=FALSE}
-tidy_df <- function(Predictor) {
-  linear_mod <- lm(
-    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)
-
-  tidy_lm <- tidy(linear_mod, conf.int = TRUE) %>% 
-    mutate(Measure = glue("{Predictor}")) %>% 
-    filter(term != "Prior_beliefs" & term != "(Intercept)")
-  tidy_lm
-}
-
-Predictors <- list("Final_beliefs", 
-                  "Credibility", 
-                  "Confidence", 
-                  "Bias", 
-                  "Error", 
-                  "Discretion")
-
-tidy_results <- Predictors %>% 
-  map(~ tidy_df(.x)) %>% 
-  bind_rows() %>% 
-  mutate(term = gsub("Condition", "", term),
-         Measure = factor(Measure,
-                          levels = c("Final_beliefs",
-                                     "Credibility",
-                                     "Confidence",
-                                     "Bias",
-                                     "Error",
-                                     "Discretion"))) %>% 
-  mutate(Conclusion = case_when(
-    conf.low < 0 & conf.high < 0 ~ "Negative",
-    conf.low < 0 & conf.high > 0 ~ "Inconclusive",
-    conf.low > 0 & conf.high > 0 ~ "Positive"
-  ))
-
-Measure.label = c("Posterior beliefs", Predictors %>% unlist() %>% tail(5))
-names(Measure.label) <- Predictors %>% unlist()
-
-p1 <- ggplot(mapping = aes(x = term, 
-                           y = estimate,
-                           color = Conclusion), 
-             data = tidy_results) +
-  geom_point(size = 2) +
-  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), 
-                size = 0.8, width = 0.2) +
-  geom_hline(yintercept = 0, linetype = "dashed", color = "gray34", alpha = 0.7) +
-  facet_wrap(~ Measure, 
-             labeller = labeller(Measure = Measure.label)) + 
-  theme_bw() + 
-  theme(strip.background = element_rect(fill = "white"),
-        legend.position = "",
-        text = element_text(size = 16, 
-                            family = "serif")) +
-  labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
-   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))  +
-  scale_color_discrete(type = c("darkgrey", "red", "green4"))
-
-ggsave("Figure1.jpg", p1, 
-       width = 7, height = 5, units = "in") #save to manuscript folder
-
-ggsave(here("talk/Figure1.jpg"), p1, 
-       width = 7, height = 5, units = "in") #save to talk folder
-
-ggsave(here("poster/Figure1.jpg"), p1, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
-p1b <- p1 + 
-  ggtitle("Differences from the single estimate condition") +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggsave(here("talk/Figure1b.jpg"), p1b, 
-       width = 7, height = 5, units = "in") #save to talk folder
-
-p1c <- p1 + 
-  scale_x_discrete(labels = c("Consistent\ncrowd", "Inconsistent\ncrowd"))
-
-ggsave(here("poster/Figure1c.jpg"), p1c, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
-p1d <- p1c + 
-  ggtitle("Differences from the single estimate condition") +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggsave(here("poster/Figure1d.jpg"), p1d, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
 knitr::include_graphics(here("poster/Figure1c.jpg"), dpi = 1200)
@@
 Green/red/gray error bars indicate positive/negative/insignificant findings, respectively.
-
-\newpage
-
-## Figure 2
-
-*Individual data points, quartiles, and distributions of prior and posterior beliefs in the single estimate, consistent crowd, and inconsistent crowd conditions*  
-\noindent
-```{r raincloud, echo=FALSE}
-set.seed(341990)
-
-df <- df %>% 
-  group_by(Condition) %>% 
-  slice_sample(n = 499)
-
-df_2x3 <- data_2x2(
-  array_1 = df %>% filter(Condition == "Multi-inconsistent") %>% pull(Prior_beliefs),
-  array_2 = df %>% filter(Condition == "Multi-inconsistent") %>% pull(Final_beliefs),
-  array_3 = df %>% filter(Condition == "Multi-consistent") %>% pull(Prior_beliefs),
-  array_4 = df %>% filter(Condition == "Multi-consistent") %>% pull(Final_beliefs),
-  array_5 = df %>% filter(Condition == "Single") %>% pull(Prior_beliefs),
-  array_6 = df %>% filter(Condition == "Single") %>% pull(Final_beliefs),
-  labels = (c('Prior Beliefs','Final Beliefs')),
-  jit_distance = .09,
-  jit_seed = 321)
-
-colors <- rep(c("#035AA6", "darkorange"), 3) #choose colors
-
-raincloud <- function(label_c1, label_c2, label_c3){
-  raincloud_2x3_repmes(
-  data = df_2x3,
-  colors = colors,
-  fills = colors,
-  size = 1,
-  alpha = .7,
-  ort = "h") + #set to v for vertical plot
-
-  scale_x_continuous(
-    breaks = c(1,2,3), 
-    limits = c(0.8, 4.3), 
-    labels = rep("", 3)) +
-  ylab("Rated Beliefs") +
-
-  annotate(geom = "text", 
-           label = label_c1, 
-           x = 3.8, y = 13, size = 6,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = label_c2, 
-           x = 2.73, y = 14, size = 6,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = label_c3,
-           x = 1.78, y = 15, size = 6,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "Prior Beliefs", 
-           fontface = "bold",
-           x = 4.2, y = 26, size = 8, 
-           color = "#035AA6",
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "vs.", 
-           x = 4.2, y = 45, size = 8,
-           family = "serif") + 
-  annotate(geom = "text", 
-           label = "Posterior Beliefs", 
-           fontface = "bold",
-           x = 4.2, y = 68, size = 8, 
-           color = "darkorange",
-           family = "serif") +
-
-  theme_classic() +
-  theme(axis.ticks.y = element_blank(),
-        #axis.text = element_text(size = 9),
-        axis.title.y = element_blank(),
-        text = element_text(size = 16, family = "serif"))
-}
-
-p2 <- raincloud("Single-analyst", "Multi-consistent", "Multi-inconsistent")
-
-ggsave("Figure2.jpg", p2, 
-       width = 7, height = 5, units = "in") #save to manuscript folder
-
-ggsave(here("talk/Figure2.jpg"), p2, 
-       width = 7, height = 5, units = "in") #save to talk folder
-
-ggsave(here("poster/Figure2.jpg"), p2, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
-p3 <- raincloud("Single estimate", "Consistent crowd", "Inconsistent crowd")
-
-ggsave(here("poster/Figure2b.jpg"), p3, 
-       width = 7, height = 5, units = "in") #save to poster folder
-
-knitr::include_graphics(here("poster/Figure2b.jpg"), dpi = 1200)
-```
-*Note.
-* Prior beliefs are displayed in blue; posterior beliefs are displayed in orange.
-The respective boxes display the lower quartiles, medians, and upper quartiles of prior and posterior beliefs by condition.
-
-<!-- Given the existing huge inefficiencies, substantial improvements are almost certainly feasible...but neither presence nor absence of revolutionary intent should be taken as a reliable surrogate for actual impact…  -->
-
-<!-- Interventions to change the current system should not be accepted without proper scrutiny, even when they are reasonable and well-intended.” -->
-
-<!-- John Ioannidis -->

### 2021-12-01 index.Rmd
added note for PSA
turned off incremental slides count

@@
       ratio: 16:9
-      countIncrementalSlides: true
+      countIncrementalSlides: false
 ---
@@
 
+Like Nicholas said in his opening talk, approaches like this allow us to explore the size of the multiverse.
+
 --

### 2021-12-08 manuscript/manuscript.Rmd
changed poster in prep for round 2 GSPA (removed anonymity)

@@
   theme_bw() + 
-  theme(strip.background = element_rect(fill = "white"),
+  theme(
+    strip.background = element_rect(fill = "white"),
     legend.position = "",
-        text = element_text(size = 16, 
-                            family = "serif")) +
+    text = element_text(size = 16, family = "serif")
+    ) +
   labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
@@
 p1c <- p1 + 
-  scale_x_discrete(labels = c("Consistent\ncrowd", "Inconsistent\ncrowd"))
+  scale_x_discrete(labels = c("Consistent\ncrowd", "Inconsistent\ncrowd")) +
+  theme(
+    strip.text = element_text(face="bold")
+  )
 

### 2021-12-08 poster/GSPA_Poster.Rmd
changed poster in prep for round 2 GSPA (removed anonymity)

@@
 author:
-  - name: Insert first author name here 
+  - name: Shilaan Alzahawi
     affil: 1
     orcid: ''
-  - name: Insert second author name here
+  - name: Benoît Monin
     affil: 1
@@
   - num: 1
-    address: Insert affiliation here
+    address: Stanford University, Graduate School of Business
 column_numbers: 3
@@
 In line with **social norm theory** (Miller & Prentice, 2016), we expect that observing **consensus** among a crowd (the **consistent crowd** condition) will -- compared to the conclusion of a single scientist (the **single estimate** condition) -- increase conformity in opinion.
-Drawing from work on **intuitive statistics** (Gigerenzer & Murray, 2015), we also expect laypeople to intuitively accord to logic of the **wisdom of crowds**: the ability of an **aggregate of multiple estimates** (rather than a single estimate) to **reduce noise** stemming from individual bias or error (Schweinsberg et al., 2021).
+Drawing from work on **intuitive statistics** (Gigerenzer & Murray, 2015), we also expect laypeople to intuitively accord to the logic of the **wisdom of crowds**: the ability of an **aggregate of multiple estimates** (rather than a single estimate) to **reduce noise** stemming from individual bias or error (Schweinsberg et al., 2021).
   $~~~~~$ In contrast, when crowd estimates show low consensus and high variance (the **inconsistent crowd** condition), we predict that observers will be less swayed and more likely to **attribute** the findings to **bias** and **error**.
@@
 Confidence in the precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
-| 4. Bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 5. Error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Discretion | $~~~$ No prediction | $~~~$ No prediction |  
+| 4.
+Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 5.
+Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |  
 *Note.* We regress each outcome on **prior beliefs** and **condition** (with the **single estimate condition** as the **reference category**).
@@
 **Open Science:** Preregistration, survey, data, and code available at        
-`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
-`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert OSF link here]
+`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [**github.com/shilaan/many-analysts**](http://github.com/shilaan/many-analysts)   
+`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [**osf.io/vedb4**](https://osf.io/vedb4)
 
@@
 `r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Consistent crowd**  
-Multiple crowd estimates: low variance, high consensus (M = 5%)  
+Multiple crowd estimates: low variance, high consensus (*M* = 5%)  
 `r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Inconsistent crowd**  
-Multiple crowd estimates: high variance, low consensus (M = 5%)
+Multiple crowd estimates: high variance, low consensus (*M* = 5%)
 

### 2021-12-08 poster/GSPA_Poster.Rmd
minor edit poster

@@
 | 4.
-Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+Scientific bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
 | 5.
-Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
-| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |  
+Scientific error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
+| 6. Scientific discretion | $~~~$ No prediction | $~~~$ No prediction |  
 *Note.* We regress each outcome on **prior beliefs** and **condition** (with the **single estimate condition** as the **reference category**).

### 2022-02-23 manuscript/manuscript.Rmd
minor edits prior to paper swap

@@
 keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
-wordcount         : "2,222"
+wordcount         : "2,249"
 
@@
 In a commentary on the many analysts approach, Breznau [-@breznau2021a, p.
-311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
+311] offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?
 We explore the effects of scientific findings emerging from a crowd of researchers (vs.
@@
 In the single estimate condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the consistent crowd condition, six independent researchers report six  consistent estimates (2%, 4%, 5%, 5%, 6%, and 8%, respectively) that average to 5% ($\sigma$ = 2%); and in the inconsistent crowd condition, six independent researchers report six inconsistent estimates (-6%, -2%, 5%, 5%, 12%, and 16%, respectively) that average to 5% ($\sigma$ = 8.25%).
-Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) bias, (5) error, and (6) researcher degrees of freedom.
+Afterwards, participants rated (1) their posterior beliefs, (2) the credibility of the results, (3) their confidence in the effect size estimate, and how likely it is that the estimate was influenced by (4) researcher bias, (5) researcher error, and (6) researcher degrees of freedom.
 All questions were answered on a slider from 0% (not likely/credible/confident at all) to 100% (extremely likely/credible/confident).
@@
 However, as with any real-world intervention, scientific reform can have unintended consequences.
+Thus, "interventions to change the current system should not be accepted without proper scrutiny, even when they are reasonable and well intended" [@ioannidis2014: p.5].
 Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
@@
   bind_rows() %>% 
-  mutate(term = gsub("Condition", "", term),
-         Measure = factor(Measure,
-                          levels = c("Final_beliefs",
+  mutate(
+    term = gsub("Condition", "", term),
+    Measure = factor(
+      Measure,
+      levels = c(
+        "Final_beliefs",
         "Credibility",
@@
         "Error",
-                                     "Discretion"))) %>% 
+        "Discretion"
+        )
+      )
+    ) %>% 
   mutate(Conclusion = case_when(
